### 2023-06-19 paper/report.tex
initial commit for paper

% This report template is adapted from the IEEE style.
% https://www.ieee.org/conferences/publishing/templates.html

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{float}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\title{Towards Language Model-based Identification of Market Segments and Fostering of Business Clusters}

\author{\IEEEauthorblockN{1\textsuperscript{th} Müller Nicola}
\IEEEauthorblockA{s8namuel@stud.uni-saarland.de \\ 2578753}
\and
\IEEEauthorblockN{2\textsuperscript{st} Leist Robert}
\IEEEauthorblockA{s8roleis@stud.uni-saarland.de \\ 2580448}
\and
\IEEEauthorblockN{3\textsuperscript{nd} Eichler Paul}
\IEEEauthorblockA{s8pleich@stud.uni-saarland.de \\ 2578569}
\and
\IEEEauthorblockN{4\textsuperscript{rd} Recktenwald Tobias}
\IEEEauthorblockA{s8tsreck@stud.uni-saarland.de \\ 2577468}
\and
\IEEEauthorblockN{5\textsuperscript{th} Nazari Hameed}
\IEEEauthorblockA{Email Address \\ Matriculation No.}
}

\maketitle

\begin{abstract}
With this guide, we give an example of what a write-up for the mini-project report could look like. We provide a \LaTeX template that you 
can use in your own write-up, if you want to. We explain some important points regarding specific types of sections that need to be included in the report.
\end{abstract}

\section{Introduction}
\color{red} 
I need the business guys to check the following paragraph!
\color{black}

Identifying market segments in regional economies is crucial for effective marketing strategies and making well-informed business decisions. Further, combining geographical data of companies' locations with information on their corresponding market segments allows for detecting business clusters, which are local concentrations of businesses, manufacturers, suppliers, and institutions from the same field. This geographic proximity of related businesses enables efficient cooperation and knowledge transfer, which has been shown to significantly increase the productivity of all businesses within the cluster (citation). Thus, establishing or further developing business clusters is of high interest to companies and local governments.

However, the identification of market segments, and moreover that of business clusters, is complicated by the fact that data on regional companies is often unavailable or difficult to analyze due to non-numerical, irrelevant, or missing features.

This work demonstrates how to identify market segments and develop business clusters by introducing an automatic clustering pipeline and location recommendation system for economic data from the German federal state Saarland.

Our clustering pipeline can be divided into $4$ distinct steps: $1)$ gathering data from the websites of companies in Saarland, $2)$ computing embeddings of the data, $3)$ reducing the embeddings' dimensionality, and $4)$ applying clustering algorithms.

$1)$ To construct data points for companies in Saarland, we rely on publicly available descriptions from their websites, allowing us to circumvent the challenges of gathering economic data. Since these descriptions are intended to attract customers and investors, they contain all relevant information for characterizing the companies.

$2)$ Given the company descriptions, we utilize state-of-the-art language models to compute embeddings of the text data, corresponding to low-dimensional vectors encompassing the data's essential information.

$3)$ We further reduce the dimensionality of the embeddings using non-linear dimensionality reduction techniques, which enables us to preserve the non-linear relationships between the embedded text data while avoiding the curse of dimensionality.

$4)$ Lastly, we apply well-established clustering algorithms in the low-dimensional feature space to assign each company to a cluster corresponding to a potential market segment.

Our location recommendation system builds upon the clustering pipeline by computing an embedding of a novel company's description, assigning it to a cluster, and then identifying the most similar companies within the cluster. The system then recommends that the novel company locate its site near an established company acting in the same market segment, which fosters business cluster development in Saarland.

We provide a graphical user interface for our methods, which visualizes the clustering of companies in Saarland and their locations in an interactive manner, allowing end-users to analyze the various market segments. Further, the interface supports making location recommendations for new company sites using text inputs.

In summary, our main contributions are:
\begin{itemize}
    \item We circumvent the challenges of traditional economic data collection by relying solely on publicly available company descriptions.
    \item We leverage state-of-the-art language models to apply clustering algorithms to the high-dimensional text data.
    \item We demonstrate our approach's feasibility using Saarland's economy.
    \item We provide a user-friendly graphical interface for our methods, allowing for analyzing market segments and location recommendations for establishing business clusters.
\end{itemize}

The remaining parts of this paper are structured as follows: In section \MakeUppercase{\romannumeral 2}, we first examine the economy in Saarland and the theory behind business clusters. Then we look upon existing work on using clustering for economic analysis, and lastly, we investigate work on language models for extracting information from text. Next, in section \MakeUppercase{\romannumeral 3}, we present our methods in more detail, discussing each step of our clustering pipeline and location recommendation system, and in \MakeUppercase{\romannumeral 4}, we present how we apply our methods to the economy of Saarland. Lastly, we examine our results in section \MakeUppercase{\romannumeral 5} and conclude this work in section \MakeUppercase{\romannumeral 6}.

\section{Related Work}
\color{red}
\begin{itemize}
    \item General stuff about Saarland's economy and its market segments?
    \item How market segments are normally identified?
    \item Theory behind business clusters and maybe related work?
    \item Related Work on clustering in economy?
    \item Mention that we collected traditional economic data?
\end{itemize}
\color{black}

In natural language processing (NLP), translating text data to machine-processable representations is a fundamental challenge for numerous tasks, such as machine translation~\cite{qi2018and}, sentiment analysis~\cite{rezaeinia2019sentiment}, and information retrieval~\cite{ye2016word}, due to the complexity and variability of natural language. A popular approach for representing text data is the utilization of so-called \emph{embeddings}: vectorized representations of text with the property that vectors of text data with similar semantic and syntactic properties will have a smaller distance to vectors of text data with different properties. Thus, embeddings enable quantifying semantic and syntactic similarity in terms of distances in a low-dimensional, dense vector space, making them ideal for applying clustering to our sparse dataset of high-dimensional company descriptions.

In general, embeddings are learned by training a neural network to perform a task requiring understanding semantic and syntactic information, such as predicting words given their surrounding contexts or predicting subsequent words in sentences. In this process, the network learns a mapping from its text input to low-dimensional representations, containing the information needed to generate correct outputs. Hence, the outputs of this mapping encode all relevant semantic and syntactic information in the text inputs, meaning that, after training, the network's corresponding layers can be reused to compute embeddings for other downstream tasks.

Mikolov et al~\cite{mikolov2013efficient}. popularized learning word embeddings from raw text data in $2013$ by introducing their Word2Vec model. GloVe, developed by Pennington et al.~\cite{pennington2014glove}, improved upon Word2Vec by effectively encoding both local context information and global statistical information into the embeddings, thereby offering more detailed semantic capture. More recently, transformer-based models like BERT, developed by Devlin et al.~\cite{devlin2018bert}, and GPT models by OpenAI~\cite{radford2018improving} have leveraged context-dependent word embeddings by encoding the words themselves and the context in which they are used. So-called sentence transformers extended these approaches by computing embeddings for entire sentences to capture more contextual information than individual word embeddings. Reimers and Gurevych~\cite{reimers2019sentence} introduced the Sentence-BERT model consisting of two Siamese BERT-networks, i.e., two BERT-networks with tied weights, which compute sentence embeddings by embedding each word individually and then applying a pooling layer calculating the maximum or mean over all word embeddings. Starting with pre-trained BERT-networks, Sentence-BERT is fine-tuned using text classification or cosine-similarity tasks, yielding a model capable of generating high-quality sentence embeddings using only a fraction of the original BERT model's computational effort.

\section{Procedure}
\input{figure}

Our goal is to collect data points on companies in Saarland and cluster them to identify market segments and recommend locations for companies who plan to establish new sites, such that it supports the development of business clusters. We will present our clustering pipeline and then examine how we can use the results to provide location recommendations.

\subsection{Identifying Market Segments through Clustering}
Figure \hyperref{fig:pipeline}{$1$} shows a graphical representation of our clustering pipeline, consisting of $4$ steps: $1)$ Collection of descriptions from company websites, $2)$ converting the descriptions to embeddings, $3)$ reducing the dimensionality of the embeddings, and $4)$ applying a clustering algorithm. In the following, we will examine each of these steps in detail.

\textit{$1)$ Collect Descriptions:} Given that high-quality economic data is highly valuable, there are no freely available data sets we could rely on for our purposes, meaning we need to build our dataset from scratch. The traditional approach for building such a dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in Saarland and then store each in a fixed-size vector. However, this approach has several drawbacks: It is not straightforward to encode non-numerical attributes, like products and customer base, such that clustering algorithms can parse them without introducing an unwanted ordering of the attributes' values. Further, some attributes may be unavailable for some companies, meaning we would need to discard them because we require fixed-size vectors, or we would need to insert dummy values, which could lead to unwanted effects. Lastly, representing a company using a small number of publicly available attributes might be insufficient for capturing all relevant characteristics. For instance, consider the smartphone manufacturers Apple and Samsung: Both companies build smartphones, have over $100.000$ employees, have revenues of over $200$ billion dollars, and have production and sales sites worldwide. Given these attributes, one could argue that Apple and Samsung are very similar companies. Yet, it is commonly known that Apple, with its minimalist design, high-end smartphones targeted toward customers looking to differentiate themselves from other people, and Samsung, with its more utilitarian smartphones targeted toward a broad customer base, are companies with fundamentally different characters.
To address these challenges to dataset construction, we propose representing companies by the description on their websites instead of numerical attributes. Since companies want to present themselves publicly in a way that attracts customers and investors, these descriptions contain the information needed to represent them accurately.

\textit{$2)$ Compute Description Embeddings:} To achieve the fixed-size inputs required by clustering algorithms, we map each company description to an embedding that describes the data in a low-dimensional space. We rely on a sentence transformer neural network architecture to compute embeddings for each sentence in a company's description. We propose two approaches to get a single embedding for each description: we repeatedly concatenate individual sentence embeddings until a fixed size is achieved, or we take the maximum over each feature dimension. The first approach, which we will call padding, preserves each sentence embedding's information but may introduce bias and high dimensionality, whereas the second approach, which we will call max pooling, achieves a lower dimensionality but may discard relevant information by only keeping the largest features.

\textit{$3)$ Projection into 2D Space:} Although the embeddings are of much lower dimensionality than the original text data, the number of features might still be too large relative to the size of our dataset. This might invoke the curse of dimensionality, meaning that the few data points are so distant from each other in the high-dimensional space that it is impossible to derive meaningful clusters. Further, clustering data in high-dimensional space prevents the visualization of clustered data points. To avoid the course of dimensionality and to enable user-friendly visualization of our results, we will project the embeddings to 2D space using two dimensionality reduction techniques.
\emph{Kernel Principal Components Analysis} (KPCA) is a dimensionality reduction technique that computes a linear transformation that projects the data in the kernel space onto the dimensions with the highest variance, such that a non-linear transformation in the original feature space is attained. Hence, by projecting the data on the dimensions with the highest variance, KPCA preserves the most relevant information.
The \emph{t-distributed stochastic neighbor embedding} (t-SNE) technique computes a probability distribution representing the pairwise similarity between data points in the feature space and then projects the data points to a low-dimensional space according to a second probability distribution that minimizes the Kullback-Leibler divergence to the first distribution. This enables t-SNE to preserve local structures in the data accurately.
The crucial difference between KPCA and t-SNE is that KPCA computes a deterministic projection that can be applied to novel data points, whereas t-SNE does not. However, the preservation of local structures by t-SNE might be more suitable for identifying clusters.

\textit{$4)$ Clustering:} We will now present two clustering approaches that depend on the choice of dimensionality reduction technique.
If KPCA is used, we cluster the data using the $K$-Means algorithm, which, starting from $K$ randomly initialized cluster centers, assigns each data point to the nearest cluster, updates the values of the cluster centers as the mean of each data point in the cluster, and then repeats until the cluster assignments do not change anymore. We combine $K$-Means with KPCA since it returns a set of cluster centers that can be used to classify novel data points. 
If t-SNE is used, we cluster the data using Agglomerative clustering, which initially assigns each data point to a separate cluster and then iteratively merges close clusters until all data points are in the same cluster. The intermediate clustering that achieves the largest overall separation between data points can then be chosen as the final clustering. The advantage of Agglomerative clustering over $K$-Means is that it does not require a pre-specified number of clusters and can compute hierarchically structured clusters.
Once the clustering algorithm converges, we receive cluster labels for each company in our dataset, corresponding to the predicted market segments.

\subsection{Fostering Business Clusters through Location Recommendations}
We utilize parts of our clustering pipeline to give location recommendations for companies seeking to establish new sites in Saarland. Given the description of the novel company, we compute an embedding using a sentence transformer and apply KPCA or t-SNE to get a low-dimensional feature vector. We then assign the feature vector to a cluster according to the $K$-Means or Agglomerative clustering algorithm and then compute which company within the cluster is most similar to the novel company. Note that when using KPCA and $K$-Means, we can assign the novel data points to a pre-computed clustering, and when using t-SNE and Agglomerative clustering, we compute a new clustering.
Thus, the second approach accounts for the possibility that introducing a novel company might change existing market segments, whereas the first approach does not. In our experiments (section \MakeUppercase{\romannumeral 4}), we will investigate which of these approaches is more suitable.
Given the cluster label of the novel company, the location recommendation is to establish the new company site nearby the most similar company within the cluster, meaning we recommend placing the novel site near the most similar company acting in the same market segment. Thus, our location recommendations support the geographical concentration of companies acting in the same market segment, which helps to foster business clusters in Saarland.

We present the results of our clustering of Saarland's economy in a user-friendly way by providing a web interface that shows our clustered data points, where we highlight the clusters by drawing the interpolated convex hull around the data points in each cluster. Further, users can see the location of each company on a map, and additional tables provide supplementary information such as industry, products, market positioning, and customer base. The interface also offers a text box where users can enter the name and description of their company to receive a location recommendation. The user then receives an output that shows all companies in the predicted cluster, ordered according to their similarity. The interface then makes a location recommendation by recommending the user locate his company near the most similar company from the same cluster. The most similar company is also highlighted on the map, so the user can visually inspect the recommended location.

\section{Experiments}

To build our dataset of company descriptions, we manually extracted the descriptions of $50$ of the largest companies in Saarland. When a description was only available in German, we translated it to English using the online translator DeepL. A list of all companies in our dataset can be found in the appendix. We conducted the data collection manually since company websites are generally structured very differently, making it complicated to extract such information automatically. Thus, building a scraping tool was out of this project's scope. To test our location recommendation feature, we created company descriptions using GPT-4.

We utilize the popular pre-trained sentence transformer "all-MiniLM-L6-v2" from the HuggingFace hub to compute sentence embeddings for each description. An embedding for the full description is then attained using our padding or max pooling approach.
Afterward, the embeddings are projected onto 2D space using either KPCA or t-SNE. We chose suitable hyperparameters for KPCA by conducting a grid search over the values $\textit{kernel} = \{\textit{radial basis function}, \textit{sigmoid}, \textit{linear}, \textit{polynomial} \}$ and $\textit{gamma} = \{0.03, 0.032, 0.034, \dots, 0.05\}$, where we found the best values to be $\textit{kernel} = \textit{polynomial}$ and $\textit{gamma} = 0.05$. For t-SNE, we manually fine-tuned the perplexity hyperparameter until we achieve a suitable separation of data points.

To choose the number of clusters for K-Means, we started with $K = \sqrt{N}$, where $N$ is the size of the dataset, and then increased $K$ until the clustering aligned with our expectations based on our supplementary economic data (section \MakeUppercase{\romannumeral 2}). For Agglomerative clustering, we chose the final number of clusters through visual inspection of the dendrogram returned by the algorithm.

Given that we have no ground truth labels, we will evaluate the results of our clustering process based on our investigation of Saarland's economy in \MakeUppercase{\romannumeral 2}.

\section{Results}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/clustering_tsne.png}
    \caption{Clustering of company descriptions using t-SNE and Agglomerative clustering.}
    \label{fig:t-sne-agglomerative}
\end{figure}

In this section, we will investigate the results of the best-performing configuration of our clustering and location recommendation system. These results were obtained using the following configuration: the description embeddings were computed using max pooling, the embeddings were projected into 2D space using t-SNE, and the clustering was achieved using Agglomerative clustering. We found that this configuration yields the most sensible predictions of market segments and location recommendations. Figure \hyperref[fig:t-sne-agglomerative]{$2$} displays the resulting clustered data points, and the plots of the other configurations can be found in the appendix.

\subsection{Clustering}
In the following, we analyze each of the found clusters and interpret them with respect to potential market segments:
\begin{itemize}
    \item \textit{Cluster 0 (dark blue)}: This cluster contains the four large food producers Karlsberg, Kunzler, Ludwig Schokolade, and Schröder. Hence, we classify it as the food market segment. It also contains Globus, a large supermarket chain that also produces its own foods. The last member of this cluster is Dillinger, which we can discard as incorrectly assigned since it is a steel manufacturer.

    \item \textit{Cluster 1 (light blue)}: We cannot infer a market segment from the members of this cluster since it contains vastly different companies, such as the pharmaceutical company URSAPHARM, the ceramics manufacturer Villeroy\&Boch, and the steel manufacturer Saarstahl. However, it contains the construction companies Peter Gross Bau and Backes AG, and the OBG Group, which is assigned to Cluster $5$, is another construction company close to the first two companies. Hence, we follow that there is a construction market segment in Saarland.

    \item \textit{Cluster 2 (dark orange)}: The data points of this cluster have the largest relative distance due to them sharing no commonalities, and thus we cannot derive a potential market segment.

    \item \textit{Cluster 3 (light orange)}: The large automotive suppliers ZF and Michelin are part of this cluster, which explains its proximity to Cluster $7$ (automotive industry market segment). However, Hörmann, which produces doors for commercial and industrial applications, and Festo, which produces industrial automation systems, are also part of this cluster. Since the only commonality between these companies is that they are large, multi-national, industrial companies, we cannot assign them to a single market segment.

    \item \textit{Cluster 4 (dark green)}: The IT / IT consulting firms eurodata, ORBIS, Scheer, and SAP are part of this cluster, so we classify it as the IT consulting market segment. The fifth member of this cluster is Iqony Energies, which is seemingly misclassified since it provides energy solutions, yet it resembles the other cluster members since it also does consulting and IT infrastructure.

    \item \textit{Cluster 5 (light green)}: This cluster contains the companies Welocalize, Unimed, and IAS Software, which provide IT services such as document translation, accounting, and data collection. Hence, we follow that this cluster is representative of the IT service market segment. Note that the remaining two cluster members can be considered incorrectly assigned. HYDAC should be added to Cluster $7$ (automotive industry market segment), and OBG Group should be in a single cluster with Peter Gross Bau and Backes AG (construction market segment).

    \item \textit{Cluster 6 (dark red)}: The only two members of this cluster are Uni Saar and CISPA, making it representative of the academia market segment.

    \item \textit{Cluster 7 (light red)}: It corresponds to the automotive industry market segment since it comprises the automotive manufacturers and suppliers Nemak, Ford, ThyssenKrupp, Schaeffler, and SaarGummi.

    \item \textit{Cluster 8 (dark purple)}: This cluster contains Bosch, VOIT, Fresenius, and Purem, which focus on electrical engineerings, such as filtration systems and powertrain components for electric cars. Thus, this cluster corresponds to the electronics industry market segment.

    \item \textit{Cluster 9 (light purple)}: The companies MAT Foundries and Meiser, which specialize in steel products, are part of this cluster, and the last cluster member is the weapons manufacturer Diehl Defence. This suggests that this cluster represents the steel industry market segment, and we note that the companies Dillinger and Saarstahl should also be contained in it.

    \item \textit{Cluster $10$ (brown)}: This cluster consists of Caritas, IKK Südwest, and CosmosDirekt, and thus we classify it as the healthcare and insurance market segment.
\end{itemize}

\subsection{Location Recommendation}
To test our location recommendation system, we generated descriptions for four fictional German companies with vastly different characteristics:
\begin{itemize}
    \item \textit{FluxAI}: A young artificial intelligence start-up with ambitious goals of revolutionizing healthcare, finance, energy, and transportation.
    \item \textit{ABC Auto}: A well-established automotive manufacturer offering a wide range of cars focusing on sustainability.
    \item \textit{Bratwurst Bliss}: A hot dog manufacturer that values traditional sausage making and locally sourced ingredients.
    \item \textit{PanzerTech}: A weapons manufacturer with a wide spectrum of products, from armored vehicles to cybersecurity solutions.
\end{itemize}

For FluxAI, our system recommends placing the new site close to CISPA, which is sensible since CISPA is a world leader in information security research, which also includes artificial intelligence, and thus knowledge transfer between both companies could be highly beneficial. It also makes sense that our system did not recommend locating FluxAI near IT companies with a more commercial focus, like SAP, since they primarily work on existing technology instead of revolutionary innovations.
For ABC Auto, the location recommendation is to establish a new site close to VOIT, which specializes in manufacturing car components with a focus on hybrid and electric cars. Thus, placing ABC Auto near VOIT would allow ABC Auto to source parts for its hybrid and electric cars from a company nearby, leading to a more robust supply chain.
For Bratwurst Bliss, the system recommends settling near the meat producer Kunzler, which could lead to knowledge transfer regarding sausage making.
Lastly, our system recommends placing PanzerTech's new site close to Diehl Defence, corresponding to the only weapons manufacturer in our dataset. Hence, this shows that our system does not need a large number of samples from each market segment to give reasonable location recommendations.

We conclude that our location recommendation system can reliably identify companies in our dataset with similar characteristics to companies seeking to establish sites in Saarland and thus can be used to foster the development of business clusters.

\subsection{Limitations}
We observed in subsection \textit{A} that we could not derive corresponding market segments for a small number of clusters because the cluster members had too different characteristics. These companies mostly belonged to sectors that are underrepresented in our dataset, such as ceramics manufacturing and pharmaceutics, so we would likely achieve more concise cluster assignments if we added more companies from these sectors to our dataset.

Another reason for invalid cluster assignments could be that our utilized sentence transformer was not fine-tuned for company descriptions, so that it could have produced inaccurate embeddings for some descriptions. Further, projecting the embeddings into 2D space could also cause inaccurate cluster assignments due to a large loss of information. Projecting the embeddings into higher dimensions might avoid this information loss, yet it would likely complicate or prevent a user-friendly visualization of the clustering results. We note that we observed no benefits from projecting the embeddings into 3D space.

\section{Conclusion}
\begin{itemize}
	\item \textbf{Recapitulate the Objectives:} Begin by restating the main project objectives or questions that guided your study. This helps to remind the reader of the purpose and scope of your research \cite{sample-article}.
	\item \textbf{Summarize the Key Findings:} Provide a brief summary of the main findings from your study. Highlight the most important results and their implications. However, avoid repeating all the details presented in the Results section. Instead, focus on the key outcomes that directly address your research objectives \cite{sample-web}.
	\item \textbf{Future Research Suggestions:} Identify potential directions for future research based on the limitations or gaps identified in your study. Discuss areas that would benefit from additional investigation or areas where more data or different methodologies could provide deeper insights.
	\item \textbf{Final remarks:} Provide a concise and thoughtful closing statement that summarizes the overall significance of your research. Reflect on the importance of your study and its potential impact on the field. Consider the broader implications of your findings and emphasize the value of your research contribution.
\end{itemize}

\bibliographystyle{IEEEtran}
\bibliography{bibliography}

\appendix
\begin{itemize}
	\item \textbf{Link to Code}: Provide the link to your code repository. You can use any service to host your code (Github, gdrive etc.). The code should be running, accessible and all of your work must be reproducible. In case your code is not accessible or not in a working state, relevant number of points will be deducted.   
	\item \textbf{Link to Overleaf}: Add a link to the Overleaf project which contains all of the LaTex related files for this report.
	\item \textbf{Additional Figures}: Add any and all additional figures produced during you work with relevant explanations in the appendix.
\end{itemize}

\end{document}

### 2023-06-19 code/clustering_kpca.py

@@ -102,8 +102,12 @@ def visualize_clustering(train_clusters, train_labels, train_projected, test_clu
 
         # compute convex hull
         try:
-            hull = ConvexHull(points)
+            hull = ConvexHull(points)  # computation might not work if data points in a cluster have a very weird position
         except:
+            # plot the label of the cluster
+            offset = (np.max(all_projected[:, 1]) - np.min(all_projected[:, 1])) * 0.025
+            ax.text(np.min(points[:, 0]), np.max(points[:, 1]) + offset, "Cluster " + str(cluster),
+                    fontsize=fontsize + 5, alpha=0.5, color=colors[cluster])
             continue
         x_hull = np.append(points[hull.vertices, 0],
                            points[hull.vertices, 0][0])

### 2023-06-19 code/clustering_tsne.py

@@ -128,7 +128,14 @@ def visualize_clustering(clusters, labels, projected, fontsize=5):
             continue
 
         # compute convex hull
-        hull = ConvexHull(points)
+        try:
+            hull = ConvexHull(points)  # computation might not work if data points in a cluster have a very weird position
+        except:
+            # plot the label of the cluster
+            offset = (np.max(projected[:, 1]) - np.min(projected[:, 1])) * 0.025
+            ax.text(np.min(points[:, 0]), np.max(points[:, 1]) + offset, "Cluster " + str(cluster),
+                    fontsize=fontsize + 5, alpha=0.5, color=colors[cluster])
+            continue
         x_hull = np.append(points[hull.vertices, 0],
                            points[hull.vertices, 0][0])
         y_hull = np.append(points[hull.vertices, 1],

### 2023-06-19 code/description_data.py

@@ -62,10 +62,12 @@ train_labels = ["ZF", "Saarstahl", "Dillinger", "Bosch", "Festo", "Ford", "Schae
                 "Ludwig Schokolade", "MAT Foundries", "Adient", "Schröder"]
 
 test_descriptions = ["FluxAI, an innovative artificial intelligence startup, is excited to announce the establishment of our global headquarters in Saarland, Germany. We are committed to integrating cutting-edge AI technology into everyday life, with solutions spanning across sectors like healthcare, finance, energy, and transportation. Our new HQ in Saarland, a hub of culture and innovation, reflects our values of creativity, collaboration, and sustainability. We're leveraging the region's strategic position in Europe's tech industry, fostering alliances with leading academic institutions, and contributing to local economic growth and STEM education. Join FluxAI in Saarland as we continue to shape the future of AI, amplifying human potential and driving global impact from the heart of Europe. Together, we're creating a smarter world.",
-                "At ABC Automobile Group, we stand as a monument to precision, innovation, and timeless German engineering. With over a century of excellence in the automotive industry, we have steadfastly shaped the future of mobility, uniting tradition and forward-thinking vision in a seamless dance of progress. Our deep roots in Germany and relentless dedication to quality have built us into a global icon. Our vehicles are renowned for their superb performance, groundbreaking technology, and unmistakable style, echoing our commitment to pushing boundaries and exceeding expectations. As we look to the future, we remain steadfastly committed to our German heritage, infusing every venture with our core values of innovation, sustainability, and craftsmanship. ABC Automobile Group is not just about manufacturing cars - we're about crafting experiences, inspiring generations, and defining mobility's future. Join us on this exhilarating journey. Together, we're not just building vehicles; we're setting benchmarks, challenging the status quo, and driving change. This is the ABC Automobile Group. Our Tradition. Our Future."
[…]

### 2023-06-19 code/embeddings.py

@@ -27,6 +27,7 @@ def get_description_embeddings(descriptions, max=True):
 
 
 def get_full_embeddings(descriptions):
+#def get_description_embeddings(descriptions):
     model = SentenceTransformer('sentence-transformers/all-MiniLM-L6-v2')
     description_embeddings = []
     min_sentences = 100

### 2023-06-19 code/predictions_kpca.py

@@ -10,7 +10,7 @@ from clustering_kpca import fit_kernel_pca, cluster_data, predict_cluster, visua
 assert len(train_labels) == len(train_descriptions), print(len(train_labels), len(train_descriptions))
 
 # Compute the clustering of the training data
-train_embeddings = get_description_embeddings(train_descriptions, max=True)
+train_embeddings = get_description_embeddings(train_descriptions)
 n_clusters = int(np.floor(np.sqrt(len(train_descriptions)))) + 4
 n_clusters = 11
 pca = fit_kernel_pca(data=train_embeddings, random_state=42)
@@ -41,7 +41,7 @@ while True:
     print("Please enter your company's description")
     test_description = input()
 
-    test_embeddings = get_description_embeddings([test_description], max=True)
+    test_embeddings = get_description_embeddings([test_description])
     test_clusters, test_projected = predict_cluster(data=test_embeddings, kpca=pca, clustering=clustering)
 
     print("\n")

### 2023-06-19 code/predictions_tsne.py

@@ -10,7 +10,7 @@ from clustering_tsne import project_tsne, predict_clusters, visualize_clustering
 assert len(train_labels) == len(train_descriptions), print(len(train_labels), len(train_descriptions))
 
 # Compute the clustering of the training data
-train_embeddings = get_description_embeddings(train_descriptions, max=True)
+train_embeddings = get_description_embeddings(train_descriptions)
 n_clusters = int(np.floor(np.sqrt(len(train_descriptions)))) + 5
 n_clusters = 11
 projected_train_embeddings = project_tsne(data=train_embeddings, dimensions=2, perplexity=np.sqrt(len(train_embeddings)),
@@ -31,7 +31,7 @@ while True:
     print("Please enter your company's description")
     new_description = input()
 
-    new_embedding = get_description_embeddings([new_description], max=True)
+    new_embedding = get_description_embeddings([new_description])
     all_embeddings = train_embeddings + new_embedding
     all_labels = train_labels + [new_label]
     projected_embeddings = project_tsne(data=all_embeddings, dimensions=2, perplexity=np.sqrt(len(all_embeddings)),

### 2023-06-19 paths.py
added paths

@@ -3,3 +3,6 @@ from os.path import join
 
 ROOT = os.path.dirname(os.path.realpath(__file__))
 DATA = join(ROOT, "data")
+TEST_CSV = join(DATA, "test.csv")
+TRAIN_CSV = join(DATA, "train.csv")
+ECO_CSV = join(DATA, "economic_data.csv")

### 2023-06-19 code/clustering_kpca.py
fixed imports in scripts

@@ -11,6 +11,7 @@ import matplotlib
 
 colors = matplotlib.colors.ListedColormap(plt.cm.tab20.colors).colors
 
+
 # Prints the results of clustering
 def print_clusters(data_labels, clustering_labels):
     clusters = {}
@@ -25,12 +26,14 @@ def print_clusters(data_labels, clustering_labels):
         print(clusters[c_label])
         print("\n")
 
+
 # Fits an instance of Kernel Principal Components Analysis using given data
 def fit_kernel_pca(data, kernel='poly', gamma=0.05, random_state=69):
     kpca = KernelPCA(n_components=2, kernel=kernel, gamma=gamma, random_state=random_state)
     kpca.fit(data)
 
     return kpca
+
 
 # Computes the clustering: First the data's dimensionality is reduced by transforming it according to the given PCA/KPCA
 # instance and then K-Means is applied to cluster the proejcted data
@@ -40,6 +43,7 @@ def cluster_data(data, kpca, n_clusters, random_state=69):
 
     return clustering
 
+
 # Assigns new data points to established clusters
 def predict_cluster(data, kpca, clustering):
     projected_data = kpca.transform(data)
@@ -47,12 +51,14 @@ def predict_cluster(data, kpca, clustering):
 
     return clustering_labels, projected_data
 
+
 # Visualizes the results of clustering as 2D or 3D scatter plots
 def visualize_clustering(train_clusters, train_labels, train_projected, test_clusters=None, test_labels=None,
                          test_projected=None, fontsize=5):
     fig = plt.figure(figsize=(15, 10))
     ax = fig.add_subplot()
-    ax.set_title("K-Means Clustering of Description Embeddings Projected into 2D Space Using KPCA", fontsize=fontsize+10)
+    ax.set_title("K-Means Clustering of Description Embeddings Projected into 2D Space Using KPCA",
+                 fontsize=fontsize + 10)
 
     if test_labels is not None:
         all_projected = np.concatenate((train_projected, test_projected), axis=0)
@@ -102,7 +108,8 @@ def visualize_clustering(train_clusters, train_labels, train_projected, test_clu
 
         # compute convex hull
         try:
-            hull = ConvexHull(points)  # computation might not work if data points in a cluster have a very weird position
+            hull = ConvexHull(
+                points)  # computation might not work if data points in a cluster have a very weird position
         except:
[…]

### 2023-06-19 scripts/cluster_descriptions.py

@@ -2,9 +2,9 @@
 This script computes a clustering for given data and makes predictions for new data points.
 """
 import numpy as np
-from description_data import train_descriptions, train_labels, test_descriptions, test_labels
-from embeddings import get_description_embeddings, get_full_embeddings
-from clustering import fit_pca, fit_kernel_pca, cluster_data, predict_cluster, visualize_clustering, visualize_tsne, print_clusters
+from code.description_data import train_descriptions, train_labels, test_descriptions, test_labels
+from code.embeddings import get_description_embeddings, get_full_embeddings
+from code.clustering import fit_pca, fit_kernel_pca, cluster_data, predict_cluster, visualize_clustering, visualize_tsne, print_clusters
 
 assert len(train_labels) == len(train_descriptions), print(len(train_labels), len(train_descriptions))
 

### 2023-06-19 scripts/names_to_file.py

@@ -1,4 +1,4 @@
-from description_data import train_labels
+from code.description_data import train_labels
 
 def save_strings_to_file(strings, filename):
     """

### 2023-06-19 scripts/optimize_pca.py

@@ -5,8 +5,8 @@ import numpy as np
 from sklearn.model_selection import GridSearchCV
 from sklearn.metrics import mean_squared_error
 from sklearn.decomposition import PCA, KernelPCA
-from description_data import train_descriptions
-from embeddings import get_description_embeddings, get_full_embeddings
+from code.description_data import train_descriptions
+from code.embeddings import get_description_embeddings, get_full_embeddings
 
 embeddings = get_full_embeddings(train_descriptions)
 def my_scorer(estimator, X, y=None):

### 2023-06-19 scripts/predictions_kpca.py

@@ -3,9 +3,9 @@ This script computes a clustering for the company description in the training da
 and assigns them to existing clusters. It uses KPCA for dimensionality reduction and K-Means clustering.
 """
 import numpy as np
-from description_data import train_descriptions, train_labels
-from embeddings import get_description_embeddings
-from clustering_kpca import fit_kernel_pca, cluster_data, predict_cluster, visualize_clustering
+from code.description_data import train_descriptions, train_labels
+from code.embeddings import get_description_embeddings
+from code.clustering_kpca import fit_kernel_pca, cluster_data, predict_cluster, visualize_clustering
 
 assert len(train_labels) == len(train_descriptions), print(len(train_labels), len(train_descriptions))
 

### 2023-06-19 scripts/predictions_tsne.py

@@ -3,9 +3,9 @@ This script computes a clustering for the company description in the training da
 and assigns them to existing clusters. It uses t-SNE for dimensionality reduction and Agglomerative clustering.
 """
 import numpy as np
-from description_data import train_descriptions, train_labels
-from embeddings import get_description_embeddings
-from clustering_tsne import project_tsne, predict_clusters, visualize_clustering
+from code.description_data import train_descriptions, train_labels
+from code.embeddings import get_description_embeddings
+from code.clustering_tsne import project_tsne, predict_clusters, visualize_clustering
 
 assert len(train_labels) == len(train_descriptions), print(len(train_labels), len(train_descriptions))
 

### 2023-06-19 paper/report.tex
add comments

@@
 \IEEEoverridecommandlockouts
+
+% TODO commands package
+\usepackage{todonotes}
+\newcommand{\pe}[1]{\todo[inline, backgroundcolor=green]{PE: #1}}
 
@@
 
+\pe{I find the claims made in this paragraph to be to not backed by evidence.
+While I have no economic background, I was able to source some existing literature, e.g.
+\href{http://biblioteca.fundacionicbc.edu.ar/images/d/de/Clusters_1.pdf}{1}, \href{https://onlinelibrary.wiley.com/doi/full/10.1111/j.1536-7150.2011.00819.x}{2},
+\href{https://www.jstor.org/stable/144358?seq=1}{3}, \href{https://www.emerald.com/insight/content/doi/10.1108/14715200280001472/full/pdf?title=cluster-theory-and-practice-advantages-for-the-small-business-locating-in-a-vibrant-cluster}{4}.
+Feel free to add the standard literature / different sources}
+
 However, the identification of market segments, and moreover that of business clusters, is complicated by the fact that data on regional companies is often unavailable or difficult to analyze due to non-numerical, irrelevant, or missing features.
+\pe{This seems a harsh claim, in practice one could argue that it is available through regional connections}
 
@@
 The system then recommends that the novel company locate its site near an established company acting in the same market segment, which fosters business cluster development in Saarland.
+\pe{I have yet to find a backing for this approach, feel free to help me out here}
 
@@
 \subsection{Identifying Market Segments through Clustering}
-Figure \hyperref{fig:pipeline}{$1$} shows a graphical representation of our clustering pipeline, consisting of $4$ steps: $1)$ Collection of descriptions from company websites, $2)$ converting the descriptions to embeddings, $3)$ reducing the dimensionality of the embeddings, and $4)$ applying a clustering algorithm.
+Figure \ref{fig:pipeline} shows a graphical representation of our clustering pipeline, consisting of $4$ steps: $1)$ Collection of descriptions from company websites, $2)$ converting the descriptions to embeddings, $3)$ reducing the dimensionality of the embeddings, and $4)$ applying a clustering algorithm.
 In the following, we will examine each of these steps in detail.
@@
 \textit{$1)$ Collect Descriptions:} Given that high-quality economic data is highly valuable, there are no freely available data sets we could rely on for our purposes, meaning we need to build our dataset from scratch.
-The traditional approach for building such a dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in Saarland and then store each in a fixed-size vector.
-However, this approach has several drawbacks: It is not straightforward to encode non-numerical attributes, like products and customer base, such that clustering algorithms can parse them without introducing an unwanted ordering of the attributes' values.
+\pe{TODO: rephrase} The traditional approach for building such a dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in Saarland and then store each in a fixed-size vector.
+\pe{TODO: backup with accepted approach} However, this approach has several drawbacks: It is not straightforward to encode non-numerical attributes, like products and customer base, such that clustering algorithms can parse them without introducing an unwanted ordering of the attributes' values.
 Further, some attributes may be unavailable for some companies, meaning we would need to discard them because we require fixed-size vectors, or we would need to insert dummy values, which could lead to unwanted effects.

### 2023-06-20 code/clustering_kpca.py
Company analysis implemented

@@ -28,8 +28,8 @@ def print_clusters(data_labels, clustering_labels):
 
 
 # Fits an instance of Kernel Principal Components Analysis using given data
-def fit_kernel_pca(data, kernel='poly', gamma=0.05, random_state=69):
-    kpca = KernelPCA(n_components=2, kernel=kernel, gamma=gamma, random_state=random_state)
+def fit_kernel_pca(data, kernel='poly', gamma=0.05, random_state=69, n_components=2):
+    kpca = KernelPCA(n_components=n_components, kernel=kernel, gamma=gamma, random_state=random_state)
     kpca.fit(data)
 
     return kpca

### 2023-06-20 code/embeddings.py

@@ -8,22 +8,42 @@ from sentence_transformers import SentenceTransformer
 
 # Computes embeddings for descriptions by transforming each sentence in a description using a sentence transformer model
 # and then taking the average or maximum across all dimensions.
-def get_description_embeddings(descriptions, max=True):
+def get_description_embeddings(descriptions, max=True, embed_type="max"):
     model = SentenceTransformer('sentence-transformers/all-MiniLM-L6-v2')
     #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
     description_embeddings = []
-    for description in descriptions:
-        sentences = re.split('\.|\!|\?', description)
-        sentence_embeddings = []
-        for sentence in sentences:
-            sentence_embedding = model.encode(sentence)
-            sentence_embeddings.append(sentence_embedding)
-        if max:
-            description_embedding = np.max(sentence_embeddings, axis=0)
-        else:
-            description_embedding = np.mean(sentence_embeddings, axis=0)
-        description_embeddings.append(description_embedding)
-    return description_embeddings
+    if embed_type in ["max", "mean"]:
+        max = embed_type == "max"
+        for description in descriptions:
+            sentences = re.split('\.|\!|\?', description)
+            sentence_embeddings = []
+            for sentence in sentences:
+                sentence_embedding = model.encode(sentence)
+                sentence_embeddings.append(sentence_embedding)
+            if max:
+                description_embedding = np.max(sentence_embeddings, axis=0)
+            else:
+                description_embedding = np.mean(sentence_embeddings, axis=0)
+            description_embeddings.append(description_embedding)
+        return description_embeddings
+    else:
+        for description in descriptions:
+            sentences = re.split('\.|\!|\?', description)
+            sentence_embeddings = []
+            embedding_shape = None
+            for sentence in sentences:
+                sentence_embedding = model.encode(sentence)
+                embedding_shape = sentence_embedding.shape
+                sentence_embeddings.append(sentence_embedding)
+            counter = 0
+            while len(sentence_embeddings) < 15:
+                sentence_embeddings.append(sentence_embeddings[counter])
+                counter += 1
+            flattened_embeddings = []
+            for embedding in sentence_embeddings:
+                flattened_embeddings += list(embedding)
+            description_embeddings.append(flattened_embeddings)
+        return description_embeddings
 
 
 def get_full_embeddings(descriptions):

### 2023-06-20 code/load_data.py

@@ -1,5 +1,6 @@
 import pandas as pd
 
+
 def get_economic_data(company_name):
     economic_dataframe = pd.read_csv('../data/economic_data.csv')
     description_dataframe = pd.read_csv('../data/train.csv')

### 2023-06-20 code/visualisation.py

@@ -1,0 +1,205 @@
+from code.clustering_tsne import project_tsne, predict_clusters
+from code.clustering_kpca import predict_cluster, fit_kernel_pca, cluster_data
+from code.embeddings import get_description_embeddings
+from code.description_data import train_descriptions, train_labels
+import numpy as np
+import streamlit as st
+import plotly.express as px
+import plotly.graph_objects as go
+import pandas as pd
+from paths import ECO_CSV
+from scipy.cluster.hierarchy import dendrogram
+from scipy.spatial import ConvexHull
+from scipy import interpolate
+
+
+@st.cache_data
+def get_hover_data():
+    df = pd.read_csv(ECO_CSV)
+    return df
+
+
+@st.cache_resource
+def get_embeddings(embedding_type="max"):
+    return get_description_embeddings(train_descriptions, embed_type=embedding_type)
+
+
+@st.cache_data
+def compute_hull(points):
+    if len(points) == 2:
+        # create fake points to compute convex hull
+        if abs(points[0, 0] - points[1, 0]) < 1:
+            # same x
+            fake_point_1 = np.array(
+                [np.mean(points[:, 0]), points[0, 1] + (np.max(points[:, 0] - np.mean(points[:, 0])))])
+            fake_point_2 = np.array(
+                [np.mean(points[:, 0]), points[0, 1] - (np.max(points[:, 0] - np.mean(points[:, 0])))])
+        elif abs(points[0, 1] - points[1, 1]) < 1:
+            # same y
+            fake_point_1 = np.array(
+                [points[0, 0] + (np.max(points[:, 1] - np.mean(points[:, 1]))), np.mean(points[:, 1])])
+            fake_point_2 = np.array(
+                [points[0, 0] - (np.max(points[:, 1] - np.mean(points[:, 1]))), np.mean(points[:, 1])])
+        else:
+            fake_point_1 = np.array([np.min(points[:, 0]), np.min(points[:, 1])])
+            fake_point_2 = np.array([np.max(points[:, 0]), np.max(points[:, 1])])
+        points = np.append(points, fake_point_1).reshape(-1, 2)
+        points = np.append(points, fake_point_2).reshape(-1, 2)
+    elif len(points) == 1:
+        return points[:, 0], points[:, 1]
+
+    # compute convex hull
+    try:
+        hull = ConvexHull(points)  # computation might not work if data points in a cluster have a very weird position
+    except:
[…]

### 2023-06-20 main.py

@@ -4,17 +4,15 @@ import numpy as np
 import pandas as pd
 import code.description_data as data
 import requests
-
+st.set_page_config(layout="wide")
 st.title("Home")
 if "submitted" not in st.session_state:
     st.session_state.submitted = False
 with st.form("Search"):
     st.text_input("Enter company name:")
     st.text_input("Enter your company description:")
+    method = st.radio("Clustering method", options=["t-SNE", "kPCA"])
     st.form_submit_button("Submit")
-
-with st.spinner("Analyzing..."):
-    time.sleep(3)
 
 
 def get_lat_lon_of_request(search_string):

### 2023-06-20 pages/01_Company_Analysis.py

@@ -1,43 +1,49 @@
 import streamlit as st
 import numpy as np
-import mpld3
-import streamlit.components.v1 as components
-from code.description_data import train_descriptions, train_labels, test_descriptions, test_labels
-from code.embeddings import get_description_embeddings
-from code.clustering import fit_pca, fit_kernel_pca, cluster_data, predict_cluster, \
-    get_clustering_plot, get_tSNE_plots, print_clusters
-
-st.title("Company Clustering")
+from code.visualisation import get_embeddings, compute_tsne, compute_kpca, \
+    plot_2d, plot_3d, get_hover_data, add_industry_clusters, add_clusters
 
 
 @st.cache_data
-def load_embeddings():
-    train_embeddings = get_description_embeddings(train_descriptions, max=True)
-    test_embeddings = get_description_embeddings(test_descriptions, max=True)#
-    return train_embeddings, test_embeddings
+def compute_clustering(embedding_type, method, n_clusters):
+    embedding_type = "max" if embedding_type == "Maximum of Features" else \
+        ("mean" if embedding_type == "Mean of Features" else embedding_type)
+    embeddings = get_embeddings(embedding_type)
+    if method == "t-SNE":
+        clusters_2d, projected_2d = compute_tsne(n_clusters, 2, embeddings)
+        clusters_3d, projected_3d = compute_tsne(n_clusters, 3, embeddings)
+    elif method == "Kernel PCA":
+        clusters_2d, projected_2d = compute_kpca(n_clusters, 2, embeddings)
+        clusters_3d, projected_3d = compute_kpca(n_clusters, 3, embeddings)
+    return {"2d": (clusters_2d, projected_2d),
+            "3d": (clusters_3d, projected_3d)}
 
 
-train_embeddings, test_embeddings = load_embeddings()
+st.set_page_config(layout="wide")
+st.title("Company Clustering")
 
-n_clusters = int(np.floor(np.sqrt(len(train_descriptions)))) + 4
+selection_area, plot_area = st.columns([1, 4])
+with selection_area:
+    with st.expander("Clustering parameters"):
+        with st.form("Clustering parameters"):
+            embedding_type = st.radio("Select embedding",
+                                      options=["Maximum of Features", "Mean of Features", "Concatenated Features"])
+            method = st.radio("Select dimensionality reduction method", options=["t-SNE", "Kernel PCA"])
[…]

### 2023-06-20 code/visualisation.py
added improved comparison to industry data

@@ -145,6 +145,7 @@ def plot_3d(clusters, projected):
                             "Customer Base": True,
                             "Market Positioning": True,
                             "Revenue": True})
+
     fig.update_traces(textposition='top center')
     fig.update_layout(
         height=750,
@@ -160,11 +161,11 @@ def plot_3d(clusters, projected):
 
 @st.cache_data
 def add_clusters(fig, clusters, projected):
-    new_fig = go.Figure(fig)
+    traces = []
     for cluster in np.unique(clusters):
         points = projected[clusters == cluster]
         cluster_x, cluster_y = compute_hull(points)
-        new_fig.add_trace(go.Scatter(
+        traces.append(go.Scatter(
             x=cluster_x,
             y=cluster_y,
             fill="toself",
@@ -176,21 +177,32 @@ def add_clusters(fig, clusters, projected):
             textposition="middle center",
             showlegend=False,
         ))
+    new_fig = go.Figure(data=traces)
+    new_fig.add_traces(data=fig.data)
+    new_fig.update_layout(
+        height=750,
+        margin=go.Margin(
+            l=0,
+            r=0,
+            b=0,
+            t=10
+        )
+    )
     return new_fig
 
 
 @st.cache_data
 def add_industry_clusters(fig, projected):
-    new_fig = go.Figure(fig)
     df = pd.merge(
         pd.DataFrame(projected),
         get_hover_data(),
         right_index=True, left_index=True
     )
+    traces = []
     for i, industry in enumerate(np.unique(df["Industry"])):
         points = projected[df["Industry"] == industry]
         cluster_x, cluster_y = compute_hull(points)
-        new_fig.add_trace(go.Scatter(
+        traces.append(go.Scatter(
             x=cluster_x,
             y=cluster_y,
             fill="toself",
@@ -202,4 +214,15 @@ def add_industry_clusters(fig, projected):
             textposition="middle center",
             showlegend=True,
         ))
+    new_fig = go.Figure(data=traces)
+    new_fig.add_traces(data=fig.data)
+    new_fig.update_layout(
+        height=750,
+        margin=go.Margin(
+            l=0,
+            r=0,
+            b=0,
+            t=10
+        )
+    )
     return new_fig

### 2023-06-20 code/visualisation.py
made the plots look better

@@ -84,33 +84,44 @@ def compute_kpca(n_clusters, dimensions, train_embeddings):
     return predict_cluster(train_embeddings, kpca, clustering)
 
 
-
 @st.cache_data
 def plot_2d(clusters, projected):
     str_cluster = [str(cluster) for cluster in clusters]
     df = pd.merge(
-        pd.DataFrame(projected),
+        pd.DataFrame(projected, columns=["x", "y"]),
         get_hover_data(),
         right_index=True, left_index=True
     )
     fig = px.scatter(df,
-                     x=0,
-                     y=1,
+                     x="x",
+                     y="y",
                      color=str_cluster,
                      labels={"color": "Cluster"},
                      category_orders={"color": list(sorted(str_cluster, key=lambda x: int(x)))},
                      color_discrete_sequence=px.colors.qualitative.Light24,
-                     text=train_labels,
+                     text="Company",
                      hover_name="Company",
+                     custom_data=df,
                      hover_data={
+                         "x": False,
+                         "y": False,
                          "Industry": True,
                          "Products": True,
                          "Customer Base": True,
                          "Market Positioning": True,
                          "Revenue": True})
-    fig.update_traces(textposition='top center')
+    fig.update_traces(textposition='top center',
+                      hovertemplate='<b>%{customdata[3]}</b><br>'
+                                    'Industry: %{customdata[4]} <br>'
+                                    'Products: %{customdata[5]} <br>'
+                                    'Customer base: %{customdata[6]} <br>'
+                                    'Market Position: %{customdata[7]} <br>'
+                                    'Revenue: %{customdata[8]}€')
     fig.update_layout(
         height=750,
+        hoverlabel=dict(
+            font_size=16
+        ),
         margin=go.Margin(
             l=0,
             r=0,
@@ -135,6 +146,7 @@ def plot_3d(clusters, projected):
                         z=2,
                         color=str_cluster,
                         labels={"color": "Cluster"},
+                        custom_data=df,
                         category_orders={"color": list(sorted(str_cluster, key=lambda x: int(x)))},
                         color_discrete_sequence=px.colors.qualitative.Light24,
                         text=train_labels,
@@ -146,9 +158,18 @@ def plot_3d(clusters, projected):
[…]

### 2023-06-20 pages/01_Company_Analysis.py

@@ -37,7 +37,8 @@ with selection_area:
     dimensions = st.radio("Select number of dimensions to display", options=["2d", "3d"])
 with plot_area:
     if dimensions == "2d":
-        compare_mode = st.checkbox("Compare to Industry data")
+        # compare_mode = st.checkbox("Compare to Industry data")
+        compare_mode = False
         if compare_mode:
             new_fig = add_industry_clusters(fig_2d, plot_data_dict["2d"][1])
         else:
@@ -45,5 +46,3 @@ with plot_area:
         st.plotly_chart(new_fig, use_container_width=True)
     else:
         st.plotly_chart(fig_3d, use_container_width=True)
-
-st.dataframe(get_hover_data())

### 2023-06-20 code/visualisation.py
added main functionality

@@ -19,9 +19,12 @@ def get_hover_data():
     return df
 
 
-@st.cache_resource
-def get_embeddings(embedding_type="max"):
-    return get_description_embeddings(train_descriptions, embed_type=embedding_type)
+@st.cache_data
+def get_embeddings(embedding_type="max", test_description=None):
+    if test_description:
+        return get_description_embeddings(train_descriptions + [test_description], embed_type=embedding_type)
+    else:
+        return get_description_embeddings(train_descriptions, embed_type=embedding_type)
 
 
 @st.cache_data

### 2023-06-20 main.py

@@ -4,15 +4,29 @@ import numpy as np
 import pandas as pd
 import code.description_data as data
 import requests
+from code.visualisation import get_embeddings, compute_tsne, compute_kpca, \
+    plot_2d, plot_3d, get_hover_data, add_industry_clusters, add_clusters
+import plotly.graph_objects as go
+import plotly.express as px
+
+
 st.set_page_config(layout="wide")
-st.title("Home")
-if "submitted" not in st.session_state:
-    st.session_state.submitted = False
-with st.form("Search"):
-    st.text_input("Enter company name:")
-    st.text_input("Enter your company description:")
-    method = st.radio("Clustering method", options=["t-SNE", "kPCA"])
-    st.form_submit_button("Submit")
+
+
+def close_expander():
+    st.session_state.expand_input = False
+
+
+@st.cache_data
+def compute_clustering(test_description, embedding_type, method, n_clusters, dimensions):
+    embedding_type = "max" if embedding_type == "Maximum of Features" else \
+        ("mean" if embedding_type == "Mean of Features" else embedding_type)
+    embeddings = get_embeddings(embedding_type, test_description)
+    if method == "t-SNE":
+        clusters, projected = compute_tsne(n_clusters, dimensions, embeddings)
+    elif method == "Kernel PCA":
+        clusters, projected = compute_kpca(n_clusters, dimensions, embeddings)
+    return clusters, projected
 
 
 def get_lat_lon_of_request(search_string):
@@ -36,10 +50,72 @@ def load_map_df(labels):
     coords_df = pd.DataFrame(data, columns=["latitude", "longitude"])
     return pd.merge(pd.DataFrame(labels, columns=["labels"]), coords_df, right_index=True, left_index=True)
 
-
-if st.session_state.submitted:
+if "expand_input" not in st.session_state:
+    st.session_state.expand_input = True
+st.title("Home")
+with st.expander("Input", expanded=st.session_state.expand_input):
+    with st.form("Search"):
+        test_label = st.text_input("Enter company name:")
+        test_description = st.text_input("Enter your company description:")
+        embedding_type = st.radio("Select embedding",
+                                  options=["Maximum of Features", "Mean of Features", "Concatenated Features"])
+        method = st.radio("Select dimensionality reduction method", options=["t-SNE", "Kernel PCA"])
+        n_clusters = st.slider("Select number of clusters", min_value=2, max_value=24, value=10)
[…]

### 2023-06-22 Home.py
refactored WebApp

@@ -1,0 +1,50 @@
+import streamlit as st
+
+text, images = st.columns([3, 2])
+
+with text:
+    st.markdown("# Team17 AI Analytics")
+
+    st.markdown("**Team17 AI Analytics**, we specialize in providing cutting-edge AI-powered solutions for"
+                " comprehensive company clustering and market segmentation. Leveraging advanced techniques such as "
+                "kernel PCA (Principal Component Analysis) and t-SNE (t-Distributed Stochastic Neighbor Embedding), "
+                "we offer businesses in Saarland an unparalleled insight into their industry landscape.")
+        
+    st.markdown("## Our Approach:")
+
+    st.markdown("Harnessing the power of state-of-the-art transformers, we embed company descriptions into "
+                "high-dimensional representations, enabling us to identify hidden patterns and similarities. "
+                "Through our innovative clustering methodology, we analyze these embeddings and provide businesses with"
+                " a holistic view of companies sharing similar characteristics based on their descriptions.")
+
+    st.markdown("[Read up on our approach in our WIP paper!](Paper)")
+        
+    st.markdown("## Unveiling Opportunities:")
+        
+    st.markdown("Our clustering analysis, Saarland companies gain a competitive edge by understanding their positioning "
+                "within the market, identifying potential collaborators or competitors, and targeting marketing efforts"
+                " more effectively. By exploring the relationships between companies and their descriptions, our solutions "
+                "facilitate informed decision-making and strategic planning.")
+
+    st.markdown("[Analyze your own company now](Analysis) or [check out our clustering for companies in Saarland](Clustering).")
+        
+    st.markdown("## Expert Team:")
+        
+    st.markdown("Multidisciplinary team consists of five highly skilled professionals, blending expertise from diverse "
+                "backgrounds. Two members hold a Bachelor of Science in Data Science and AI, possessing a deep"
+                " understanding of cutting-edge AI techniques and models. Another member brings a Bachelor of "
+                "Science in Computer Science, ensuring robust implementation and system optimization. "
+                "Finally, our two team members with Bachelor of Science degrees in Economics bring valuable insights "
+                "into market dynamics and business strategy.")
+
+    st.markdown("[Get to know the team!](Team)")
+        
+    st.markdown("**Team17 AI Analytics**, we are passionate about leveraging the power of AI and data science to help "
+                "businesses thrive in the ever-evolving landscape of Saarland's industries. We are dedicated to "
[…]

### 2023-06-22 main.py

@@ -1,121 +1,6 @@
-import streamlit as st
-import time
-import numpy as np
-import pandas as pd
-import code.description_data as data
-import requests
-from code.visualisation import get_embeddings, compute_tsne, compute_kpca, \
-    plot_2d, plot_3d, get_hover_data, add_industry_clusters, add_clusters
-import plotly.graph_objects as go
-import plotly.express as px
+import os
+import paths
 
 
-st.set_page_config(layout="wide")
-
-
-def close_expander():
-    st.session_state.expand_input = False
-
-
-@st.cache_data
-def compute_clustering(test_description, embedding_type, method, n_clusters, dimensions):
-    embedding_type = "max" if embedding_type == "Maximum of Features" else \
-        ("mean" if embedding_type == "Mean of Features" else embedding_type)
-    embeddings = get_embeddings(embedding_type, test_description)
-    if method == "t-SNE":
-        clusters, projected = compute_tsne(n_clusters, dimensions, embeddings)
-    elif method == "Kernel PCA":
-        clusters, projected = compute_kpca(n_clusters, dimensions, embeddings)
-    return clusters, projected
-
-
-def get_lat_lon_of_request(search_string):
-    url = 'https://nominatim.openstreetmap.org/search/' + urllib.parse.quote(search_string) + '?format=json'
-    response = requests.get(url).json()
-    return response[0]["lat"], response[0]["lon"]
-
-
-@st.cache_data
-def load_map_df(labels):
-    data = np.zeros((len(labels), 2))
-    for i, company in enumerate(labels):
-        print(i, company)
-        try:
-            lat, lon = get_lat_lon_of_request(company + ", Saarland")
-        except Exception as e:
-            print(e)
-            continue
-        data[i, 0] = lat
-        data[i, 1] = lon
-    coords_df = pd.DataFrame(data, columns=["latitude", "longitude"])
-    return pd.merge(pd.DataFrame(labels, columns=["labels"]), coords_df, right_index=True, left_index=True)
-
-if "expand_input" not in st.session_state:
-    st.session_state.expand_input = True
-st.title("Home")
-with st.expander("Input", expanded=st.session_state.expand_input):
-    with st.form("Search"):
-        test_label = st.text_input("Enter company name:")
-        test_description = st.text_input("Enter your company description:")
-        embedding_type = st.radio("Select embedding",
-                                  options=["Maximum of Features", "Mean of Features", "Concatenated Features"])
[…]

### 2023-06-22 pages/00_Analysis.py

@@ -1,0 +1,124 @@
+import streamlit as st
+import time
+import numpy as np
+import pandas as pd
+import code.description_data as data
+import requests
+from code.visualisation import get_embeddings, compute_tsne, compute_kpca, \
+    plot_2d, plot_3d, get_hover_data, add_industry_clusters, add_clusters
+import plotly.graph_objects as go
+import plotly.express as px
+
+
+st.set_page_config(layout="wide")
+
+
+def close_expander():
+    st.session_state.expand_input = False
+
+
+@st.cache_data
+def compute_clustering(test_description, embedding_type, method, n_clusters, dimensions):
+    embedding_type = "max" if embedding_type == "Maximum of Features" else \
+        ("mean" if embedding_type == "Mean of Features" else embedding_type)
+    embeddings = get_embeddings(embedding_type, test_description)
+    if method == "t-SNE":
+        clusters, projected = compute_tsne(n_clusters, dimensions, embeddings)
+    elif method == "Kernel PCA":
+        clusters, projected = compute_kpca(n_clusters, dimensions, embeddings)
+    return clusters, projected
+
+
+def get_lat_lon_of_request(search_string):
+    url = 'https://nominatim.openstreetmap.org/search/' + urllib.parse.quote(search_string) + '?format=json'
+    response = requests.get(url).json()
+    return response[0]["lat"], response[0]["lon"]
+
+
+@st.cache_data
+def load_map_df(labels):
+    data = np.zeros((len(labels), 2))
+    for i, company in enumerate(labels):
+        print(i, company)
+        try:
+            lat, lon = get_lat_lon_of_request(company + ", Saarland")
+        except Exception as e:
+            print(e)
+            continue
+        data[i, 0] = lat
+        data[i, 1] = lon
+    coords_df = pd.DataFrame(data, columns=["latitude", "longitude"])
+    return pd.merge(pd.DataFrame(labels, columns=["labels"]), coords_df, right_index=True, left_index=True)
+
+if "expand_input" not in st.session_state:
+    st.session_state.expand_input = True
+with st.expander("Input", expanded=st.session_state.expand_input):
+    with st.form("Search"):
+        test_label = st.text_input("Enter company name:")
+        test_description = st.text_input("Enter your company description:")
+        embedding_type = st.radio("Select embedding",
+                                  options=["Maximum of Features", "Mean of Features", "Concatenated Features"],
+                                  help="Select how text data will be embedded. "
+                                       "Maximum of Features: Takes the maximum of feature embeddings "
[…]

### 2023-06-22 pages/01_Clustering.py

@@ -24,13 +24,19 @@ st.title("Company Clustering")
 
 selection_area, plot_area = st.columns([1, 4])
 with selection_area:
-    with st.expander("Clustering parameters"):
-        with st.form("Clustering parameters"):
-            embedding_type = st.radio("Select embedding",
-                                      options=["Maximum of Features", "Mean of Features", "Concatenated Features"])
-            method = st.radio("Select dimensionality reduction method", options=["t-SNE", "Kernel PCA"])
-            n_clusters = st.slider("Select number of clusters", min_value=2, max_value=24, value=10)
-            st.form_submit_button("Compute clustering")
+    with st.form("Clustering parameters"):
+        embedding_type = st.radio("Select embedding",
+                                  options=["Maximum of Features", "Mean of Features", "Concatenated Features"],
+                                  help="Select how text data will be embedded. "
+                                       "Maximum of Features: Takes the maximum of feature embeddings "
+                                       "across sentences in the description.\n"
+                                       "Mean of Features: Takes the mean of feature embeddings "
+                                       "across sentences in the description.\n"
+                                       "Concatenated Features: Concatenates all features into a large input feature. "
+                                       "Computation usually takes longer using this method.")
+        method = st.radio("Select dimensionality reduction method", options=["t-SNE", "Kernel PCA"])
+        n_clusters = st.slider("Select number of clusters", min_value=2, max_value=24, value=10)
+        st.form_submit_button("Compute clustering")
     plot_data_dict = compute_clustering(embedding_type, method, n_clusters)
     fig_2d = plot_2d(plot_data_dict["2d"][0], plot_data_dict["2d"][1])
     fig_3d = plot_3d(plot_data_dict["3d"][0], plot_data_dict["3d"][1])

### 2023-06-22 pages/04_Paper.py

@@ -1,0 +1,22 @@
+import streamlit as st
+import os
+import paths
+import base64
+
+
+st.set_page_config("Paper", layout="wide")
+
+
+def displayPDF(file):
+    # Opening file from file path
+    with open(file, "rb") as f:
+        base64_pdf = base64.b64encode(f.read()).decode('utf-8')
+
+    # Embedding PDF in HTML
+    pdf_display = F'<iframe src="data:application/pdf;base64,{base64_pdf}" width="1700" height="1000" type="application/pdf"></iframe>'
+
+    # Displaying File
+    st.markdown(pdf_display, unsafe_allow_html=True)
+
+
+displayPDF(os.path.join(paths.ROOT, "paper", "report.pdf"))

### 2023-06-22 pages/01_Clustering.py
Clustering now includes a map

@@ -1,7 +1,17 @@
 import streamlit as st
 import numpy as np
+import requests
+import os
+
+import paths
+from code.description_data import train_labels
+import urllib
+import pandas as pd
 from code.visualisation import get_embeddings, compute_tsne, compute_kpca, \
-    plot_2d, plot_3d, get_hover_data, add_industry_clusters, add_clusters
+    plot_2d, plot_3d, plot_map, add_clusters
+
+
+st.set_page_config(layout="wide")
 
 
 @st.cache_data
@@ -18,9 +28,6 @@ def compute_clustering(embedding_type, method, n_clusters):
     return {"2d": (clusters_2d, projected_2d),
             "3d": (clusters_3d, projected_3d)}
 
-
-st.set_page_config(layout="wide")
-st.title("Company Clustering")
 
 selection_area, plot_area = st.columns([1, 4])
 with selection_area:
@@ -43,12 +50,24 @@ with selection_area:
     dimensions = st.radio("Select number of dimensions to display", options=["2d", "3d"])
 with plot_area:
     if dimensions == "2d":
-        # compare_mode = st.checkbox("Compare to Industry data")
-        compare_mode = False
-        if compare_mode:
-            new_fig = add_industry_clusters(fig_2d, plot_data_dict["2d"][1])
-        else:
+        compare_mode = st.radio("Plot Style", options=["Cluster Plot", "Map", "Both"], horizontal=True)
+        if compare_mode == "Map":
+            new_fig = plot_map(clusters=plot_data_dict["2d"][0])
+            st.plotly_chart(new_fig, use_container_width=True)
+            st.warning("Some companies might be missing on this map!")
+        elif compare_mode == "Cluster Plot":
             new_fig = add_clusters(fig_2d, plot_data_dict["2d"][0], plot_data_dict["2d"][1])
-        st.plotly_chart(new_fig, use_container_width=True)
+            st.plotly_chart(new_fig, use_container_width=True)
+        else:
+            plot, map_col = st.columns([1, 1])
+            with plot:
+                new_fig = add_clusters(fig_2d, plot_data_dict["2d"][0], plot_data_dict["2d"][1])
+                st.plotly_chart(new_fig, use_container_width=True)
+            with map_col:
+                new_fig = plot_map(clusters=plot_data_dict["2d"][0])
+                st.plotly_chart(new_fig, use_container_width=True)
+                st.warning("Some companies might be missing on this map!")
     else:
         st.plotly_chart(fig_3d, use_container_width=True)
+
+

### 2023-06-22 code/visualisation.py
Clustering now includes a map

@@ -7,10 +7,39 @@ import streamlit as st
 import plotly.express as px
 import plotly.graph_objects as go
 import pandas as pd
+import paths
+import requests
+import urllib
+import os
 from paths import ECO_CSV
 from scipy.cluster.hierarchy import dendrogram
 from scipy.spatial import ConvexHull
 from scipy import interpolate
+
+
+def get_lat_lon_of_request(search_string):
+    url = 'https://nominatim.openstreetmap.org/search/' + urllib.parse.quote(search_string) + '?format=json'
+    response = requests.get(url).json()
+    return response[0]["lat"], response[0]["lon"]
+
+
+@st.cache_data
+def load_map_df():
+    if os.path.exists(paths.MAP_CSV):
+        return pd.read_csv(paths.MAP_CSV)
+    data = np.zeros((len(train_labels), 2))
+    for i, company in enumerate(train_labels):
+        print(i, company)
+        try:
+            lat, lon = get_lat_lon_of_request(company + ", Saarland")
+        except Exception:
+            lat, lon = None, None
+        data[i, 0] = lat
+        data[i, 1] = lon
+    coords_df = pd.DataFrame(data, columns=["latitude", "longitude"])
+    df = pd.merge(pd.DataFrame(train_labels, columns=["labels"]), coords_df, right_index=True, left_index=True)
+    df.to_csv(paths.MAP_CSV)
+    return df
 
 
 @st.cache_data
@@ -85,6 +114,42 @@ def compute_kpca(n_clusters, dimensions, train_embeddings):
     kpca = fit_kernel_pca(train_embeddings, n_components=dimensions)
     clustering = cluster_data(train_embeddings, kpca, n_clusters)
     return predict_cluster(train_embeddings, kpca, clustering)
+
+
+@st.cache_data
+def plot_map(clusters):
+    map_df = load_map_df()
+    hover_df = get_hover_data()
+    df = pd.merge(map_df, hover_df, right_index=True, left_index=True)
+    df["Cluster"] = [str(cluster) for cluster in clusters]
+    selected = df.dropna()
+    fig = px.scatter_mapbox(selected, lat="latitude", lon="longitude", color="Cluster", custom_data=selected,
+                            text="Company", zoom=9,
+                            category_orders={"Cluster": list(sorted(selected["Cluster"], key=lambda x: int(x)))},
+                            hover_name="Company", hover_data=["Industry", "Customer Base", "Market Positioning"],
+                            color_discrete_sequence=px.colors.qualitative.Light24)
[…]

### 2023-06-22 paths.py

@@ -6,3 +6,4 @@ DATA = join(ROOT, "data")
 TEST_CSV = join(DATA, "test.csv")
 TRAIN_CSV = join(DATA, "train.csv")
 ECO_CSV = join(DATA, "economic_data.csv")
+MAP_CSV = join(DATA, "map_data.csv")

### 2023-06-22 pages/02_Map.py
deleted map tab

@@ -1,35 +1,0 @@
-import streamlit as st
-import pandas as pd
-import numpy as np
-import requests
-import urllib.parse
-from code.description_data import train_labels
-
-
-def get_lat_lon_of_request(search_string):
-    url = 'https://nominatim.openstreetmap.org/search/' + urllib.parse.quote(search_string) + '?format=json'
-    response = requests.get(url).json()
-    return response[0]["lat"], response[0]["lon"]
-
-
-st.title("Map")
-
-
-@st.cache_data
-def load_map_df():
-    data = np.zeros((len(train_labels), 2))
-    for i, company in enumerate(train_labels):
-        print(i, company)
-        try:
-            lat, lon = get_lat_lon_of_request(company + ", Saarland")
-        except Exception as e:
-            print(e)
-            continue
-        data[i, 0] = lat
-        data[i, 1] = lon
-    coords_df = pd.DataFrame(data, columns=["latitude", "longitude"])
-    return pd.merge(pd.DataFrame(train_labels, columns=["labels"]), coords_df, right_index=True, left_index=True)
-
-
-map_df = load_map_df()
-st.map(map_df)

### 2023-06-22 Home.py
updated spacing on Home page

@@ -1,6 +1,6 @@
 import streamlit as st
 
-text, images = st.columns([3, 2])
+text, images = st.columns([3, 1])
 
 with text:
     st.markdown("# Team17 AI Analytics")

### 2023-06-22 Home.py
Fixed some typos

@@ -5,14 +5,14 @@ text, images = st.columns([3, 1])
 with text:
     st.markdown("# Team17 AI Analytics")
 
-    st.markdown("**Team17 AI Analytics**, we specialize in providing cutting-edge AI-powered solutions for"
+    st.markdown("At **Team17 AI Analytics**, we specialize in providing cutting-edge AI-powered solutions for"
                 " comprehensive company clustering and market segmentation. Leveraging advanced techniques such as "
                 "kernel PCA (Principal Component Analysis) and t-SNE (t-Distributed Stochastic Neighbor Embedding), "
                 "we offer businesses in Saarland an unparalleled insight into their industry landscape.")
         
     st.markdown("## Our Approach:")
 
-    st.markdown("Harnessing the power of state-of-the-art transformers, we embed company descriptions into "
+    st.markdown("By harnessing the power of state-of-the-art transformers, we embed company descriptions into "
                 "high-dimensional representations, enabling us to identify hidden patterns and similarities. "
                 "Through our innovative clustering methodology, we analyze these embeddings and provide businesses with"
                 " a holistic view of companies sharing similar characteristics based on their descriptions.")
@@ -21,7 +21,7 @@ with text:
         
     st.markdown("## Unveiling Opportunities:")
         
-    st.markdown("Our clustering analysis, Saarland companies gain a competitive edge by understanding their positioning "
+    st.markdown("With our clustering analysis, Saarland companies gain a competitive edge by understanding their positioning "
                 "within the market, identifying potential collaborators or competitors, and targeting marketing efforts"
                 " more effectively. By exploring the relationships between companies and their descriptions, our solutions "
                 "facilitate informed decision-making and strategic planning.")
@@ -30,7 +30,7 @@ with text:
         
     st.markdown("## Expert Team:")
         
-    st.markdown("Multidisciplinary team consists of five highly skilled professionals, blending expertise from diverse "
+    st.markdown("Our multidisciplinary team consists of five highly skilled professionals, blending expertise from diverse "
                 "backgrounds. Two members hold a Bachelor of Science in Data Science and AI, possessing a deep"
                 " understanding of cutting-edge AI techniques and models. Another member brings a Bachelor of "
                 "Science in Computer Science, ensuring robust implementation and system optimization. "
@@ -39,7 +39,7 @@ with text:
 
     st.markdown("[Get to know the team!](Team)")
         
[…]

### 2023-06-22 code/visualisation.py
some better visualisation and analysis

@@ -117,11 +117,11 @@ def compute_kpca(n_clusters, dimensions, train_embeddings):
 
 
 @st.cache_data
-def plot_map(clusters):
+def plot_map(clusters, plot_connections=False):
     map_df = load_map_df()
     hover_df = get_hover_data()
     df = pd.merge(map_df, hover_df, right_index=True, left_index=True)
-    df["Cluster"] = [str(cluster) for cluster in clusters]
+    df["Cluster"] = [str(cluster) if cluster is not None else None for cluster in clusters]
     selected = df.dropna()
     fig = px.scatter_mapbox(selected, lat="latitude", lon="longitude", color="Cluster", custom_data=selected,
                             text="Company", zoom=9,
@@ -130,7 +130,7 @@ def plot_map(clusters):
                             color_discrete_sequence=px.colors.qualitative.Light24)
     fig.update_layout(mapbox_style='carto-darkmatter')
     fig.update_layout(margin={"r": 0, "t": 0, "l": 0, "b": 0})
-    fig.update_traces(textposition='top center',
+    fig.update_traces(mode="markers+text", showlegend=not plot_connections, textposition='top center',
                       hovertemplate='<b>%{customdata[5]}</b><br>'
                                     'Industry: %{customdata[6]} <br>'
                                     'Products: %{customdata[7]} <br>'
@@ -149,6 +149,33 @@ def plot_map(clusters):
             t=10
         )
     )
+    if plot_connections:
+        data = fig.data
+        for i in reversed(range(len(clusters))):
+            if clusters[i] is None:
+                del clusters[i]
+        for cluster in np.unique(clusters):
+            lats = selected[selected["Cluster"] == str(cluster)]["latitude"]
+            lons = selected[selected["Cluster"] == str(cluster)]["longitude"]
+            mean_lat = np.mean(lats)
+            mean_lon = np.mean(lons)
+            new_lats = []
+            new_lons = []
+            for lat, lon in zip(lats, lons):
+                new_lats += [mean_lat, lat]
+                new_lons += [mean_lon, lon]
+            fig.add_trace(go.Scattermapbox(
+                lat=new_lats,
+                lon=new_lons,
+                fillcolor=px.colors.qualitative.Light24[cluster],
+                mode="lines",
+                opacity=0.1,
+                line=dict(color=px.colors.qualitative.Light24[cluster]),
+                showlegend=False
+            ))
+        fig.add_traces(data=data)
[…]

### 2023-06-22 pages/00_Analysis.py

@@ -5,7 +5,7 @@ import pandas as pd
 import code.description_data as data
 import requests
 from code.visualisation import get_embeddings, compute_tsne, compute_kpca, \
-    plot_2d, plot_3d, get_hover_data, add_industry_clusters, add_clusters
+    plot_2d, plot_3d, plot_map, get_hover_data, add_industry_clusters, add_clusters
 import plotly.graph_objects as go
 import plotly.express as px
 
@@ -50,12 +50,13 @@ def load_map_df(labels):
     coords_df = pd.DataFrame(data, columns=["latitude", "longitude"])
     return pd.merge(pd.DataFrame(labels, columns=["labels"]), coords_df, right_index=True, left_index=True)
 
+
 if "expand_input" not in st.session_state:
     st.session_state.expand_input = True
 with st.expander("Input", expanded=st.session_state.expand_input):
     with st.form("Search"):
-        test_label = st.text_input("Enter company name:")
-        test_description = st.text_input("Enter your company description:")
+        test_label = st.text_input("Enter company name:", placeholder="Your company")
+        test_description = st.text_input("Enter your company description:", placeholder="Your company description")
         embedding_type = st.radio("Select embedding",
                                   options=["Maximum of Features", "Mean of Features", "Concatenated Features"],
                                   help="Select how text data will be embedded. "
@@ -71,54 +72,64 @@ with st.expander("Input", expanded=st.session_state.expand_input):
         dimensions = st.radio("Select number of dimensions to use for clustering", options=[2, 3])
         submit = st.form_submit_button("Submit", on_click=close_expander)
 if submit and test_description:
+    test_label = "Your company" if test_label is None else test_label
     clusters, projected = compute_clustering(test_description, embedding_type, method, n_clusters, dimensions)
     with st.expander("Competitors", expanded=True):
         df = get_hover_data()
         competitors = df[clusters[:-1] == clusters[-1]]
-        st.write(f"Your competitors are:")
-        st.dataframe(competitors)
-        st.write(f"Your competitors are working in the following industries: {np.unique(competitors['Industry'].values)}")
-        if dimensions == 2:
-            figure = plot_2d(clusters[:-1], projected[:-1])
-            figure = add_clusters(figure, clusters[:-1], projected[:-1])
-            figure.add_trace(go.Scatter(
-                x=[projected[-1, 0]],
-                y=[projected[-1, 1]],
-                marker=dict(
-                    color=px.colors.qualitative.Light24[clusters[-1]],
-                    size=20,
[…]

### 2023-06-23 code/visualisation.py
added heatmap for location recommendation

@@ -180,6 +180,31 @@ def plot_map(clusters, plot_connections=False):
 
 
 @st.cache_data
+def add_similarity_heatmap(fig, distances):
+    map_df = load_map_df()
+    hover_df = get_hover_data()
+    df = pd.merge(map_df, hover_df, right_index=True, left_index=True)
+    # df["Cluster"] = [str(cluster) if cluster is not None else None for cluster in clusters]
+    df["Distances"] = (max(distances) - distances) / (max(distances))
+    selected = df.dropna()
+    map_fig = px.density_mapbox(selected, lat="latitude", lon="longitude", z="Distances", custom_data=selected,
+                                radius=50, opacity=0.5,
+                                mapbox_style="carto-darkmatter",
+                                color_continuous_scale=px.colors.sequential.Hot)
+    fig.add_traces(data=map_fig.data)
+    fig.update_layout(mapbox_style='carto-darkmatter')
+    fig.update_layout(margin={"r": 0, "t": 0, "l": 0, "b": 0})
+    fig.update_traces(hovertemplate='<b>%{customdata[5]}</b><br>'
+                                    'Similarity: %{customdata[11]:.2%}<br>'
+                                    'Industry: %{customdata[6]} <br>'
+                                    'Products: %{customdata[7]} <br>'
+                                    'Customer base: %{customdata[8]} <br>'
+                                    'Market Position: %{customdata[9]} <br>'
+                                    'Revenue: %{customdata[10]}€')
+    return fig
+
+
+@st.cache_data
 def plot_2d(clusters, projected):
     str_cluster = [str(cluster) for cluster in clusters]
     df = pd.merge(
@@ -259,7 +284,7 @@ def plot_3d(clusters, projected):
                                     'Products: %{customdata[6]} <br>'
                                     'Customer base: %{customdata[7]} <br>'
                                     'Market Position: %{customdata[8]} <br>'
-                                    'Revenue: %{customdata[9]}€',)
+                                    'Revenue: %{customdata[9]}€', )
     fig.update_layout(
         height=750,
         hoverlabel=dict(

### 2023-06-23 pages/00_Analysis.py

@@ -5,7 +5,7 @@ import pandas as pd
 import code.description_data as data
 import requests
 from code.visualisation import get_embeddings, compute_tsne, compute_kpca, \
-    plot_2d, plot_3d, plot_map, get_hover_data, add_industry_clusters, add_clusters
+    plot_2d, plot_3d, plot_map, get_hover_data, add_similarity_heatmap, add_clusters
 import plotly.graph_objects as go
 import plotly.express as px
 
@@ -15,6 +15,7 @@ st.set_page_config(layout="wide")
 
 def close_expander():
     st.session_state.expand_input = False
+    st.session_state.submit = True
 
 
 @st.cache_data
@@ -53,6 +54,8 @@ def load_map_df(labels):
 
 if "expand_input" not in st.session_state:
     st.session_state.expand_input = True
+if "submit" not in st.session_state:
+    st.session_state.submit = True
 with st.expander("Input", expanded=st.session_state.expand_input):
     with st.form("Search"):
         test_label = st.text_input("Enter company name:", placeholder="Your company")
@@ -70,8 +73,8 @@ with st.expander("Input", expanded=st.session_state.expand_input):
         method = st.radio("Select dimensionality reduction method", options=["t-SNE", "Kernel PCA"])
         n_clusters = st.slider("Select number of clusters", min_value=2, max_value=24, value=10)
         dimensions = st.radio("Select number of dimensions to use for clustering", options=[2, 3])
-        submit = st.form_submit_button("Submit", on_click=close_expander)
-if submit and test_description:
+        st.form_submit_button("Submit", on_click=close_expander)
+if st.session_state.submit and test_description:
     test_label = "Your company" if test_label is None else test_label
     clusters, projected = compute_clustering(test_description, embedding_type, method, n_clusters, dimensions)
     with st.expander("Competitors", expanded=True):
@@ -123,13 +126,24 @@ if submit and test_description:
             with plot:
                 st.plotly_chart(figure, use_container_width=True)
             with map_plot:
+                heatmap = st.checkbox("Overlay similarity heatmap")
                 selected = [cluster if cluster == clusters[-1] else None for cluster in clusters[:-1]]
                 map_fig = plot_map(selected, plot_connections=True)
-                map_fig.update_layout(height=400)
+                if heatmap:
+                    distances = []
+                    point_of_interest = projected[-1]
+                    for point in projected[:-1]:
+                        distances.append(np.sqrt(
+                            np.sum(
+                                [np.power((point_2 - point_1), 2)
[…]

### 2023-06-26 code/data_util.py
some refactoring & added all features to clustering

@@ -1,0 +1,64 @@
+import pandas as pd
+import numpy as np
+import streamlit as st
+import paths
+import requests
+import urllib
+import os
+from code.description_data import train_labels, train_descriptions
+from code.embeddings import get_description_embeddings
+
+
+def get_economic_data_for_company(company_name):
+    economic_dataframe = pd.read_csv('../data/economic_data.csv')
+    description_dataframe = pd.read_csv('../data/train.csv')
+    company_data = economic_dataframe[economic_dataframe['Company'] == company_name]
+    company_description = description_dataframe[description_dataframe['label'] == company_name]['description'].values[0]
+
+    return company_data, company_description
+
+
+@st.cache_data
+def load_economic_df():
+    df = pd.read_csv(paths.ECO_CSV)
+    return df
+
+
+def get_lat_lon_of_request(search_string):
+    url = 'https://nominatim.openstreetmap.org/search/' + urllib.parse.quote(search_string) + '?format=json'
+    response = requests.get(url).json()
+    return response[0]["lat"], response[0]["lon"]
+
+
+@st.cache_data
+def load_map_df():
+    if os.path.exists(paths.MAP_CSV):
+        return pd.read_csv(paths.MAP_CSV)
+    data = np.zeros((len(train_labels), 2))
+    for i, company in enumerate(train_labels):
+        print(i, company)
+        try:
+            lat, lon = get_lat_lon_of_request(company + ", Saarland")
+        except Exception:
+            lat, lon = None, None
+        data[i, 0] = lat
+        data[i, 1] = lon
+    coords_df = pd.DataFrame(data, columns=["latitude", "longitude"])
+    df = pd.merge(pd.DataFrame(train_labels, columns=["labels"]), coords_df, right_index=True, left_index=True)
+    df.to_csv(paths.MAP_CSV)
+    return df
+
+
+@st.cache_data
+def get_embeddings(embedding_type="max", test_feature=None, data_to_embed=None):
+    """Embeds the data given or if none given embeds training descriptions."""
+    if data_to_embed is None:
+        if test_feature:
+            return get_description_embeddings(train_descriptions + [test_feature], embed_type=embedding_type)
+        else:
+            return get_description_embeddings(train_descriptions, embed_type=embedding_type)
+    else:
+        if test_feature:
+            return get_description_embeddings(data_to_embed + [test_feature], embed_type=embedding_type)
+        else:
+            return get_description_embeddings(data_to_embed, embed_type=embedding_type)

### 2023-06-26 code/load_data.py

@@ -1,13 +1,0 @@
-import pandas as pd
-
-
-def get_economic_data(company_name):
-    economic_dataframe = pd.read_csv('../data/economic_data.csv')
-    description_dataframe = pd.read_csv('../data/train.csv')
-    company_data = economic_dataframe[economic_dataframe['Company'] == company_name]
-    company_description = description_dataframe[description_dataframe['label'] == company_name]['description'].values[0]
-
-    return company_data, company_description
-
-
-print(get_economic_data('ZF'))

### 2023-06-26 code/visualisation.py

@@ -7,53 +7,9 @@ import streamlit as st
 import plotly.express as px
 import plotly.graph_objects as go
 import pandas as pd
-import paths
-import requests
-import urllib
-import os
-from paths import ECO_CSV
-from scipy.cluster.hierarchy import dendrogram
 from scipy.spatial import ConvexHull
 from scipy import interpolate
-
-
-def get_lat_lon_of_request(search_string):
-    url = 'https://nominatim.openstreetmap.org/search/' + urllib.parse.quote(search_string) + '?format=json'
-    response = requests.get(url).json()
-    return response[0]["lat"], response[0]["lon"]
-
-
-@st.cache_data
-def load_map_df():
-    if os.path.exists(paths.MAP_CSV):
-        return pd.read_csv(paths.MAP_CSV)
-    data = np.zeros((len(train_labels), 2))
-    for i, company in enumerate(train_labels):
-        print(i, company)
-        try:
-            lat, lon = get_lat_lon_of_request(company + ", Saarland")
-        except Exception:
-            lat, lon = None, None
-        data[i, 0] = lat
-        data[i, 1] = lon
-    coords_df = pd.DataFrame(data, columns=["latitude", "longitude"])
-    df = pd.merge(pd.DataFrame(train_labels, columns=["labels"]), coords_df, right_index=True, left_index=True)
-    df.to_csv(paths.MAP_CSV)
-    return df
-
-
-@st.cache_data
-def get_hover_data():
-    df = pd.read_csv(ECO_CSV)
-    return df
-
-
-@st.cache_data
-def get_embeddings(embedding_type="max", test_description=None):
-    if test_description:
-        return get_description_embeddings(train_descriptions + [test_description], embed_type=embedding_type)
-    else:
-        return get_description_embeddings(train_descriptions, embed_type=embedding_type)
+from code.data_util import load_map_df, load_economic_df
 
 
 @st.cache_data
@@ -119,7 +75,7 @@ def compute_kpca(n_clusters, dimensions, train_embeddings):
 @st.cache_data
 def plot_map(clusters, plot_connections=False):
     map_df = load_map_df()
-    hover_df = get_hover_data()
+    hover_df = load_economic_df()
     df = pd.merge(map_df, hover_df, right_index=True, left_index=True)
     df["Cluster"] = [str(cluster) if cluster is not None else None for cluster in clusters]
     selected = df.dropna()
@@ -182,7 +138,7 @@ def plot_map(clusters, plot_connections=False):
 @st.cache_data
[…]

### 2023-06-26 pages/00_Analysis.py

@@ -4,8 +4,9 @@ import numpy as np
 import pandas as pd
 import code.description_data as data
 import requests
-from code.visualisation import get_embeddings, compute_tsne, compute_kpca, \
-    plot_2d, plot_3d, plot_map, get_hover_data, add_similarity_heatmap, add_clusters
+from code.visualisation import compute_tsne, compute_kpca, \
+    plot_2d, plot_3d, plot_map, load_economic_df, add_similarity_heatmap, add_clusters
+from code.data_util import get_embeddings
 import plotly.graph_objects as go
 import plotly.express as px
 
@@ -19,14 +20,26 @@ def close_expander():
 
 
 @st.cache_data
-def compute_clustering(test_description, embedding_type, method, n_clusters, dimensions):
+def compute_clustering(test_features, embedding_type, features, method, n_clusters, dimensions):
     embedding_type = "max" if embedding_type == "Maximum of Features" else \
         ("mean" if embedding_type == "Mean of Features" else embedding_type)
-    embeddings = get_embeddings(embedding_type, test_description)
+    economic_df = load_economic_df()
+    input_features = []
+    if "Description" in features:
+        embeddings = get_embeddings(embedding_type,
+                                    test_feature=test_features["Description"])
+        input_features += list(np.moveaxis(np.array(embeddings), 0, -1))
+        features.remove("Description")
+    for feature in features:
+        embeddings = get_embeddings(embedding_type,
+                                    test_feature=test_features[feature],
+                                    data_to_embed=list(economic_df[feature]))
+        input_features += list(np.moveaxis(np.array(embeddings), 0, -1))
+    input = np.moveaxis(np.array(input_features), 0, -1)
     if method == "t-SNE":
-        clusters, projected = compute_tsne(n_clusters, dimensions, embeddings)
+        clusters, projected = compute_tsne(n_clusters, dimensions, input)
     elif method == "Kernel PCA":
-        clusters, projected = compute_kpca(n_clusters, dimensions, embeddings)
+        clusters, projected = compute_kpca(n_clusters, dimensions, input)
     return clusters, projected
 
 
@@ -55,30 +68,58 @@ def load_map_df(labels):
 if "expand_input" not in st.session_state:
     st.session_state.expand_input = True
 if "submit" not in st.session_state:
-    st.session_state.submit = True
-with st.expander("Input", expanded=st.session_state.expand_input):
-    with st.form("Search"):
-        test_label = st.text_input("Enter company name:", placeholder="Your company")
[…]

### 2023-06-26 pages/01_Clustering.py

@@ -7,7 +7,8 @@ import paths
 from code.description_data import train_labels
 import urllib
 import pandas as pd
-from code.visualisation import get_embeddings, compute_tsne, compute_kpca, \
+from code.data_util import get_embeddings, load_economic_df, load_map_df
+from code.visualisation import compute_tsne, compute_kpca, \
     plot_2d, plot_3d, plot_map, add_clusters
 
 
@@ -15,16 +16,30 @@ st.set_page_config(layout="wide")
 
 
 @st.cache_data
-def compute_clustering(embedding_type, method, n_clusters):
+def compute_clustering(embedding_type, features: list[str], method, n_clusters):
     embedding_type = "max" if embedding_type == "Maximum of Features" else \
         ("mean" if embedding_type == "Mean of Features" else embedding_type)
-    embeddings = get_embeddings(embedding_type)
+    economic_df = load_economic_df()
+    map_df = load_map_df()
+    input_features = []
+    if "Description" in features:
+        embeddings = get_embeddings(embedding_type)
+        input_features += list(np.moveaxis(np.array(embeddings), 0, -1))
+        features.remove("Description")
+    if "Location" in features:
+        input_features.append(list(map_df["latitude"]))
+        input_features.append(list(map_df["longitude"]))
+        features.remove("Location")
+    for feature in features:
+        embeddings = get_embeddings(embedding_type, data_to_embed=list(economic_df[feature]))
+        input_features += list(np.moveaxis(np.array(embeddings), 0, -1))
+    input = np.moveaxis(np.array(input_features), 0, -1)
     if method == "t-SNE":
-        clusters_2d, projected_2d = compute_tsne(n_clusters, 2, embeddings)
-        clusters_3d, projected_3d = compute_tsne(n_clusters, 3, embeddings)
+        clusters_2d, projected_2d = compute_tsne(n_clusters, 2, input)
+        clusters_3d, projected_3d = compute_tsne(n_clusters, 3, input)
     elif method == "Kernel PCA":
-        clusters_2d, projected_2d = compute_kpca(n_clusters, 2, embeddings)
-        clusters_3d, projected_3d = compute_kpca(n_clusters, 3, embeddings)
+        clusters_2d, projected_2d = compute_kpca(n_clusters, 2, input)
+        clusters_3d, projected_3d = compute_kpca(n_clusters, 3, input)
     return {"2d": (clusters_2d, projected_2d),
             "3d": (clusters_3d, projected_3d)}
 
@@ -43,8 +58,11 @@ with selection_area:
[…]

### 2023-06-26 pages/00_Analysis.py
proper heatmap

@@ -154,8 +154,7 @@ if st.session_state.submit:
                     z=[projected[-1, 2]],
                     marker=dict(
                         color=px.colors.qualitative.Light24[clusters[-1]],
-                        size=20,
-                        symbol="square",),
+                        size=15,),
                     mode="markers+text",
                     hoverinfo="none",
                     text=test_label,

### 2023-06-26 pages/01_Clustering.py
added map plots for 3d clustering too

@@ -67,8 +67,8 @@ with selection_area:
     fig_3d = plot_3d(plot_data_dict["3d"][0], plot_data_dict["3d"][1])
     dimensions = st.radio("Select number of dimensions to display", options=["2d", "3d"])
 with plot_area:
+    compare_mode = st.radio("Plot Style", options=["Cluster Plot", "Map", "Both"], horizontal=True)
     if dimensions == "2d":
-        compare_mode = st.radio("Plot Style", options=["Cluster Plot", "Map", "Both"], horizontal=True)
         if compare_mode == "Map":
             new_fig = plot_map(clusters=plot_data_dict["2d"][0])
             st.plotly_chart(new_fig, use_container_width=True)
@@ -86,6 +86,21 @@ with plot_area:
                 st.plotly_chart(new_fig, use_container_width=True)
                 st.warning("Some companies might be missing on this map!")
     else:
+        if compare_mode == "Map":
+            new_fig = plot_map(clusters=plot_data_dict["3d"][0])
+            st.plotly_chart(new_fig, use_container_width=True)
+            st.warning("Some companies might be missing on this map!")
+        elif compare_mode == "Cluster Plot":
+            new_fig = add_clusters(fig_2d, plot_data_dict["2d"][0], plot_data_dict["2d"][1])
+            st.plotly_chart(new_fig, use_container_width=True)
+        else:
+            plot, map_col = st.columns([1, 1])
+            with plot:
+                st.plotly_chart(fig_3d, use_container_width=True)
+            with map_col:
+                new_fig = plot_map(clusters=plot_data_dict["3d"][0])
+                st.plotly_chart(new_fig, use_container_width=True)
+                st.warning("Some companies might be missing on this map!")
         st.plotly_chart(fig_3d, use_container_width=True)
 
 

### 2023-06-26 pages/01_Clustering.py
removed "Location" as a clustering feature

@@ -58,7 +58,7 @@ with selection_area:
                                        "Computation usually takes longer using this method.")
         method = st.radio("Select dimensionality reduction method", options=["t-SNE", "Kernel PCA"])
         n_clusters = st.slider("Select number of clusters", min_value=2, max_value=24, value=10)
-        features = st.multiselect("Select features", options=["Description", "Location", "Industry", "Products",
+        features = st.multiselect("Select features", options=["Description", "Industry", "Products",
                                                               "Customer Base", "Market Positioning", "Revenue"],
                                   default=["Description"])
         st.form_submit_button("Compute clustering")

### 2023-06-26 code/visualisation.py
legend fix

@@ -147,8 +147,8 @@ def add_similarity_heatmap(fig, distances):
                                 radius=50, opacity=0.5,
                                 mapbox_style="carto-darkmatter",
                                 color_continuous_scale=px.colors.sequential.Hot,
-                                range_color=[0.0, 1.0])
-    fig.add_trace(map_fig.data[0])
+                                range_color=[0.0, 1.0],
+                                labels={"Distances": "Similarity"})
     map_fig.update_layout(margin={"r": 0, "t": 0, "l": 0, "b": 0})
     map_fig.add_traces(data=fig.data)
     map_fig.update_traces(hovertemplate='<b>%{customdata[5]}</b><br>'

### 2023-06-26 report/report.tex
working on rewrite

--- 2023-06-19 paper/report.tex
@@
 \newcommand{\pe}[1]{\todo[inline, backgroundcolor=green]{PE: #1}}
+\definecolor{eyecancerpink}{rgb}{1.0, 0.0, 1.0}
+\newcommand{\nm}[1]{\todo[inline, backgroundcolor=eyecancerpink]{NM: #1}}
 
@@
 \pe{This seems a harsh claim, in practice one could argue that it is available through regional connections}
+\nm{Keep the current motivation for using company descriptions and then only later mention that we can also add other features?}
 
 This work demonstrates how to identify market segments and develop business clusters by introducing an automatic clustering pipeline and location recommendation system for economic data from the German federal state Saarland.
+The novelty of our approach is that we rely on language models to encode the companies' information.
 
@@
 
-We provide a graphical user interface for our methods, which visualizes the clustering of companies in Saarland and their locations in an interactive manner, allowing end-users to analyze the various market segments.
+We provide a graphical user-interface for our methods, which visualizes the clustering of companies in Saarland and their locations in an interactive manner, allowing end-users to analyze the various market segments.
 Further, the interface supports making location recommendations for new company sites using text inputs.
@@
 \begin{itemize}
-    \item We circumvent the challenges of traditional economic data collection by relying solely on publicly available company descriptions.
+    \item We circumvent the challenges of traditional economic data collection by relying on publicly available company descriptions.
     \item We leverage state-of-the-art language models to apply clustering algorithms to the high-dimensional text data.
+    \item We show how our methods can be extended to handle additional features.
     \item We demonstrate our approach's feasibility using Saarland's economy.
@@
 
+\nm{Adjust this when related work is finally done}
 The remaining parts of this paper are structured as follows: In section \MakeUppercase{\romannumeral 2}, we first examine the economy in Saarland and the theory behind business clusters.
-Then we look upon existing work on using clustering for economic analysis, and lastly, we investigate work on language models for extracting information from text.
+Then we look upon existing work on using clustering for economic analysis, and lastly, we investigate work on language models for extracting information from text data.
 Next, in section \MakeUppercase{\romannumeral 3}, we present our methods in more detail, discussing each step of our clustering pipeline and location recommendation system, and in \MakeUppercase{\romannumeral 4}, we present how we apply our methods to the economy of Saarland.
@@
 \color{black}
+\nm{Related work for business stuff is still missing! Also adjust motivation for embeddings?}
 
@@
 \subsection{Identifying Market Segments through Clustering}
-Figure \ref{fig:pipeline} shows a graphical representation of our clustering pipeline, consisting of $4$ steps: $1)$ Collection of descriptions from company websites, $2)$ converting the descriptions to embeddings, $3)$ reducing the dimensionality of the embeddings, and $4)$ applying a clustering algorithm.
+Figure \ref{fig:pipeline} shows a graphical representation of our general clustering pipeline, consisting of $4$ steps: $1)$ Collection of descriptions from company websites, $2)$ converting the descriptions to embeddings, $3)$ reducing the dimensionality of the embeddings, and $4)$ applying a clustering algorithm.
 In the following, we will examine each of these steps in detail.
@@
 \pe{TODO: rephrase} The traditional approach for building such a dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in Saarland and then store each in a fixed-size vector.
-\pe{TODO: backup with accepted approach} However, this approach has several drawbacks: It is not straightforward to encode non-numerical attributes, like products and customer base, such that clustering algorithms can parse them without introducing an unwanted ordering of the attributes' values.
+\pe{TODO: backup with accepted approach} However, it is not straightforward to encode non-numerical attributes, like products and customer base, such that clustering algorithms can parse them without introducing an unwanted ordering of the attributes' values.
 Further, some attributes may be unavailable for some companies, meaning we would need to discard them because we require fixed-size vectors, or we would need to insert dummy values, which could lead to unwanted effects.
@@
 We rely on a sentence transformer neural network architecture to compute embeddings for each sentence in a company's description.
-We propose two approaches to get a single embedding for each description: we repeatedly concatenate individual sentence embeddings until a fixed size is achieved, or we take the maximum over each feature dimension.
-The first approach, which we will call padding, preserves each sentence embedding's information but may introduce bias and high dimensionality, whereas the second approach, which we will call max pooling, achieves a lower dimensionality but may discard relevant information by only keeping the largest features.
+We propose three approaches to attain a single embedding for each description: we repeatedly concatenate individual sentence embeddings until a fixed size is achieved, take the average over each feature dimension, or take the maximum over each feature dimension.
+The first approach, which we will call concatenation, preserves each sentence embedding's information but may introduce bias and high dimensionality, whereas the second and third approaches, which we will call average and max pooling, achieve a lower dimensionality but may discard relevant information by only keeping the average of the features or the largest features.
 
@@
 Further, clustering data in high-dimensional space prevents the visualization of clustered data points.
-To avoid the course of dimensionality and to enable user-friendly visualization of our results, we will project the embeddings to 2D space using two dimensionality reduction techniques.
+To avoid the course of dimensionality and to enable user-friendly visualization of our results, we will project the embeddings to 2D or 3D space using two dimensionality reduction techniques.
 \emph{Kernel Principal Components Analysis} (KPCA) is a dimensionality reduction technique that computes a linear transformation that projects the data in the kernel space onto the dimensions with the highest variance, such that a non-linear transformation in the original feature space is attained.
@@
 
+Although our general pipeline represents companies using their descriptions, we emphasize that our approach can also handle utilizing other features.
+For instance, we can include the companies' products in the encoding by computing the corresponding sentence embeddings and merging them with the description embedding using concatenation, average or max pooling.
+In section \MakeUppercase{\romannumeral 5}, we will investigate the results of combining company descriptions with other features.
+
+Figure \ref{fig:clustering-analysis} depicts the clustering analysis tab of our user-interface.
+On the left side, users can define how the description embeddings are computed, the technique and target dimensionality of the dimensionality reduction, and the number of clusters.
+Additionally, users can specify a subset of additional features, including industry, products, customer base, market positioning, and revenue, which will be combined with the descriptions.
+After clicking "Compute clustering", the clustered data points are shown on the right side as a 2D or 3D scatter plot.
+Further, users can see the location and clustering assignment of all companies in our dataset on a map.
+When hovering the mouse over a company's data point, additional information about the company is shown.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\textwidth]{figures/clustering_analysis.png}
+	\caption{Clustering analysis page of our user-interface.}
+	\label{fig:clustering-analysis}
+\end{figure}
+
 \subsection{Fostering Business Clusters through Location Recommendations}
@@
 Thus, the second approach accounts for the possibility that introducing a novel company might change existing market segments, whereas the first approach does not.
-In our experiments (section \MakeUppercase{\romannumeral 4}), we will investigate which of these approaches is more suitable.
 Given the cluster label of the novel company, the location recommendation is to establish the new company site nearby the most similar company within the cluster, meaning we recommend placing the novel site near the most similar company acting in the same market segment.
@@
 
-We present the results of our clustering of Saarland's economy in a user-friendly way by providing a web interface that shows our clustered data points, where we highlight the clusters by drawing the interpolated convex hull around the data points in each cluster.
-Further, users can see the location of each company on a map, and additional tables provide supplementary information such as industry, products, market positioning, and customer base.
-The interface also offers a text box where users can enter the name and description of their company to receive a location recommendation.
-The user then receives an output that shows all companies in the predicted cluster, ordered according to their similarity.
-The interface then makes a location recommendation by recommending the user locate his company near the most similar company from the same cluster.
-The most similar company is also highlighted on the map, so the user can visually inspect the recommended location.
+Our user-interface offers a dedicated tab for location recommendations.
+In figure \ref{fig:location-recommendation-input} we see the text boxes where users can provide their company's name and description.
+Additionally, users can specify their company's industry, products, customer base, market position, and revenue which can be used to support the location recommendations.
+After clicking "Submit", users are shown the output depicted in figure \ref{fig:location-recommendation-output}.
+The table at the top shows the names and features of the companies in the cluster, to which the user's company was assigned.
+The scatter plot at the bottom left shows the clustered data points, where the point of the user's company is highlighted.
+Lastly, the map at the bottom right displays the location of the novel company's cluster members and the distances between them.
+The user can also overlay a heatmap which show the similarity between his company and all other companies in out dataset.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\textwidth]{figures/location_recommendation_input.png}
+	\caption{Input to the location recommendation feature of our user-interface.}
+	\label{fig:location-recommendation-input}
+\end{figure}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\textwidth]{figures/location_recommendation_output.png}
+	\caption{Output of the location recommendation feature of our user-interface.}
+	\label{fig:location-recommendation-output}
+\end{figure}
 
 \section{Experiments}
-
 To build our dataset of company descriptions, we manually extracted the descriptions of $50$ of the largest companies in Saarland.
 When a description was only available in German, we translated it to English using the online translator DeepL.
-A list of all companies in our dataset can be found in the appendix.
+A list of all companies in our dataset can be found in the appendix \ref{sec:appendix-a}.
 We conducted the data collection manually since company websites are generally structured very differently, making it complicated to extract such information automatically.
@@
 To test our location recommendation feature, we created company descriptions using GPT-4.
+To test the impact of providing additional features to the clustering pipeline, we also gathered the features industry, products, customer base, market positioning, and revenue for each company.
 
 We utilize the popular pre-trained sentence transformer "all-MiniLM-L6-v2" from the HuggingFace hub to compute sentence embeddings for each description.
-An embedding for the full description is then attained using our padding or max pooling approach.
-Afterward, the embeddings are projected onto 2D space using either KPCA or t-SNE.
+An embedding for the full description is then attained using our concatenation, average, or max pooling approach.
+When using additional features, we compute embeddings for each feature and combine them with the description embedding in the same way the individual sentence embeddings were combined.
+Afterward, the embeddings are projected onto 2D or 3D space using KPCA or t-SNE.
 We chose suitable hyperparameters for KPCA by conducting a grid search over the values $\textit{kernel} = \{\textit{radial basis function}, \textit{sigmoid}, \textit{linear}, \textit{polynomial} \}$ and $\textit{gamma} = \{0.03, 0.032, 0.034, \dots, 0.05\}$, where we found the best values to be $\textit{kernel} = \textit{polynomial}$ and $\textit{gamma} = 0.05$.
-For t-SNE, we manually fine-tuned the perplexity hyperparameter until we achieve a suitable separation of data points.
+For t-SNE, we manually fine-tuned the perplexity hyperparameter until we achieved a suitable separation of data points.
 
-To choose the number of clusters for K-Means, we started with $K = \sqrt{N}$, where $N$ is the size of the dataset, and then increased $K$ until the clustering aligned with our expectations based on our supplementary economic data (section \MakeUppercase{\romannumeral 2}).
+To choose the number of clusters for $K$-Means, we started with $K = \sqrt{N}$, where $N$ is the size of the dataset, and then increased $K$ until the clustering aligned with our expectations.
 For Agglomerative clustering, we chose the final number of clusters through visual inspection of the dendrogram returned by the algorithm.
@@
 \section{Results}
+\nm{Move current clustering results to appendix and rewrite section for the new results, keep location recommendation results as they are?}
 \begin{figure}[H]
     \centering
-    \includegraphics[width=0.5\textwidth]{figures/clustering_tsne.png}
-    \caption{Clustering of company descriptions using t-SNE and Agglomerative clustering.}
+    \includegraphics[width=0.5\textwidth]{figures/clustering_results.png}
+    \caption{Clustering of company descriptions using t-SNE and Agglomerative clustering. The company descriptions and industries were used as features.}
     \label{fig:t-sne-agglomerative}
@@
 \appendix
+\nm{Upload all LaTeX files to overleaf when its done since they want a link! Update readme in repo!}
 \begin{itemize}
@@
 
+\subsection{Companies in our Dataset}
+\label{sec:appendix-a}
+We list the $50$ Saarland companies in our dataset:
+\begin{itemize}
+	\item ZF
+	\item Saarstahl
+	\item Dillinger
+	\item Bosch
+	\item Festo
+	\item Ford
+	\item Schaeffler
+	\item Fresenius
+	\item Wagner
+	\item Villery\&Boch
+	\item Michelin
+	\item ThyssenKrupp
+	\item Hager
+	\item Purem
+	\item SaarGummi
+	\item VOIT
+	\item Meiser
+	\item SAP
+	\item Nemak
+	\item Peter Gross Bau
+	\item OBG Group
+	\item URSAPHARM
+	\item Hörmann
+	\item Kunzler
+	\item Diehl Defence
+	\item HYDAC
+	\item Backes AG
+	\item Karlsberg
+	\item Globus
+	\item Caritas
+	\item Uni Saar
+	\item Welocalize
+	\item Möbel Martin
+	\item IKK Südwest
+	\item Dr. Theiss
+	\item Unimed
+	\item CosmosDirekt
+	\item ORBIS
+	\item eurodata
+	\item energis
+	\item CISPA
+	\item Greencells
+	\item Scheer
+	\item Iqony Energies
+	\item PLUSCARD
+	\item IAS Software
+	\item Ludwig Schokolade
+	\item MAT Foundries
+	\item Adient
+	\item Schröder
+\end{itemize}
+
+\subsection{Additional Clustering Results}
+
+\subsection{Link to Code}
+\url{https://github.com/NicolaMueller42/data_science_project}
+
+\subsection{Link to Overleaf}
+
 \end{document}

### 2023-06-26 report/report.tex
still working on report

@@
 \color{black}
-\nm{Related work for business stuff is still missing! Also adjust motivation for embeddings?}
+\nm{Related work for business stuff is still missing!}
 
@@
 \section{Results}
-\nm{Move current clustering results to appendix and rewrite section for the new results, keep location recommendation results as they are?}
+\nm{Rewrite clustering section for the new results, keep location recommendation results as they are?}
 \begin{figure}[H]
@@
 These results were obtained using the following configuration: the description embeddings were computed using max pooling, the embeddings were projected into 2D space using t-SNE, and the clustering was achieved using Agglomerative clustering.
+We also used the companies' industry as an additional feature.
  We found that this configuration yields the most sensible predictions of market segments and location recommendations.
-Figure \hyperref[fig:t-sne-agglomerative]{$2$} displays the resulting clustered data points, and the plots of the other configurations can be found in the appendix.
+Figure \ref{fig:t-sne-agglomerative} displays the resulting clustered data points.
 
@@
 \appendix
-\nm{Upload all LaTeX files to overleaf when its done since they want a link! Update readme in repo!}
+\nm{Upload all \LaTeX{} files to overleaf when its done since they want a link! Update readme in repo!}
 \begin{itemize}

### 2023-06-26 code/visualisation.py
final fixes

@@ -136,12 +136,12 @@ def plot_map(clusters, plot_connections=False):
 
 
 @st.cache_data
-def add_similarity_heatmap(fig, distances):
+def add_similarity_heatmap(fig, distances, cluster, clusters):
     map_df = load_map_df()
     hover_df = load_economic_df()
     df = pd.merge(map_df, hover_df, right_index=True, left_index=True)
     # df["Cluster"] = [str(cluster) if cluster is not None else None for cluster in clusters]
-    df["Distances"] = (max(distances) - distances) / (max(distances))
+    df["Distances"] = [max(((50 - distance) / 50), 0) for distance in distances]
     selected = df.dropna()
     map_fig = px.density_mapbox(selected, lat="latitude", lon="longitude", z="Distances", custom_data=selected,
                                 radius=50, opacity=0.5,
@@ -150,6 +150,14 @@ def add_similarity_heatmap(fig, distances):
                                 range_color=[0.0, 1.0],
                                 labels={"Distances": "Similarity"})
     map_fig.update_layout(margin={"r": 0, "t": 0, "l": 0, "b": 0})
+    fig.update_traces(customdata=selected[clusters == cluster])
+    fig.update_traces(hovertemplate='<b>%{customdata[5]}</b><br>'
+                                    'Similarity: %{customdata[11]:.2%}<br>'
+                                    'Industry: %{customdata[6]} <br>'
+                                    'Products: %{customdata[7]} <br>'
+                                    'Customer base: %{customdata[8]} <br>'
+                                    'Market Position: %{customdata[9]} <br>'
+                                    'Revenue: %{customdata[10]}€')
     map_fig.add_traces(data=fig.data)
     map_fig.update_traces(hovertemplate='<b>%{customdata[5]}</b><br>'
                                     'Similarity: %{customdata[11]:.2%}<br>'
@@ -158,6 +166,7 @@ def add_similarity_heatmap(fig, distances):
                                     'Customer base: %{customdata[8]} <br>'
                                     'Market Position: %{customdata[9]} <br>'
                                     'Revenue: %{customdata[10]}€')
+
     return map_fig
 
 

### 2023-06-26 pages/00_Analysis.py

@@ -166,7 +166,7 @@ if st.session_state.submit:
             with plot:
                 st.plotly_chart(figure, use_container_width=True)
             with map_plot:
-                heatmap = st.checkbox("Overlay similarity heatmap")
+                heatmap = st.checkbox("Overlay similarity heatmap", value=True)
                 selected = [cluster if cluster == clusters[-1] else None for cluster in clusters[:-1]]
                 map_fig = plot_map(selected, plot_connections=True)
                 if heatmap:
@@ -178,7 +178,7 @@ if st.session_state.submit:
                                 [np.power((point_2 - point_1), 2)
                                     for point_1, point_2 in zip(point, point_of_interest)])
                         ))
-                    map_fig = add_similarity_heatmap(map_fig, distances)
+                    map_fig = add_similarity_heatmap(map_fig, distances, clusters[-1], clusters[:-1])
                 map_fig.update_layout(height=390)
                 st.plotly_chart(map_fig)
         else:

### 2023-06-26 code/visualisation.py
using spread to compute similarity now

@@ -136,12 +136,12 @@ def plot_map(clusters, plot_connections=False):
 
 
 @st.cache_data
-def add_similarity_heatmap(fig, distances, cluster, clusters):
+def add_similarity_heatmap(fig, distances, max_distance, cluster, clusters):
     map_df = load_map_df()
     hover_df = load_economic_df()
     df = pd.merge(map_df, hover_df, right_index=True, left_index=True)
     # df["Cluster"] = [str(cluster) if cluster is not None else None for cluster in clusters]
-    df["Distances"] = [max(((50 - distance) / 50), 0) for distance in distances]
+    df["Distances"] = [max(((max_distance - distance) / max_distance), 0) for distance in distances]
     selected = df.dropna()
     map_fig = px.density_mapbox(selected, lat="latitude", lon="longitude", z="Distances", custom_data=selected,
                                 radius=50, opacity=0.5,

### 2023-06-26 pages/00_Analysis.py

@@ -178,7 +178,14 @@ if st.session_state.submit:
                                 [np.power((point_2 - point_1), 2)
                                     for point_1, point_2 in zip(point, point_of_interest)])
                         ))
-                    map_fig = add_similarity_heatmap(map_fig, distances, clusters[-1], clusters[:-1])
+                    min_points = np.min(projected, axis=1)
+                    max_points = np.max(projected, axis=1)
+                    spread = np.sqrt(np.sum(
+                                [np.power((point_2 - point_1), 2)
+                                    for point_1, point_2 in zip(min_points, max_points)])
+                        )
+                    max_distance = spread / 5
+                    map_fig = add_similarity_heatmap(map_fig, distances, max_distance, clusters[-1], clusters[:-1])
                 map_fig.update_layout(height=390)
                 st.plotly_chart(map_fig)
         else:

### 2023-06-26 Home.py
major refactor to remove PEP Warnings

@@ -21,16 +21,20 @@ with text:
         
     st.markdown("## Unveiling Opportunities:")
         
-    st.markdown("With our clustering analysis, Saarland companies gain a competitive edge by understanding their positioning "
+    st.markdown("With our clustering analysis, Saarland companies gain a competitive edge by understanding their "
+                "positioning "
                 "within the market, identifying potential collaborators or competitors, and targeting marketing efforts"
-                " more effectively. By exploring the relationships between companies and their descriptions, our solutions "
+                " more effectively. By exploring the relationships between companies and their descriptions, "
+                "our solutions "
                 "facilitate informed decision-making and strategic planning.")
 
-    st.markdown("[Analyze your own company now](Analysis) or [check out our clustering for companies in Saarland](Clustering).")
+    st.markdown("[Analyze your own company now](Analysis) or "
+                "[check out our clustering for companies in Saarland](Clustering).")
         
     st.markdown("## Expert Team:")
         
-    st.markdown("Our multidisciplinary team consists of five highly skilled professionals, blending expertise from diverse "
+    st.markdown("Our multidisciplinary team consists of five highly skilled professionals, blending expertise "
+                "from diverse "
                 "backgrounds. Two members hold a Bachelor of Science in Data Science and AI, possessing a deep"
                 " understanding of cutting-edge AI techniques and models. Another member brings a Bachelor of "
                 "Science in Computer Science, ensuring robust implementation and system optimization. "
@@ -39,7 +43,8 @@ with text:
 
     st.markdown("[Get to know the team!](Team)")
         
-    st.markdown("At **Team17 AI Analytics**, we are passionate about leveraging the power of AI and data science to help "
+    st.markdown("At **Team17 AI Analytics**, we are passionate about leveraging the power of AI and data "
+                "science to help "
                 "businesses thrive in the ever-evolving landscape of Saarland's industries. We are dedicated to "
                 "delivering tailored solutions that empower companies to make informed decisions, unlock new "
                 "opportunities, and drive sustainable growth.")

### 2023-06-26 code/clustering.py

@@ -1,13 +1,12 @@
 """
 This script contains all the functions necessary for clustering data.
 """
-import matplotlib.colors
 import matplotlib.pyplot as plt
 from sklearn.cluster import KMeans
 from sklearn.manifold import TSNE
 from sklearn.decomposition import PCA, KernelPCA
 import numpy as np
-import plotly.express as px
+
 
 # Prints the results of clustering
 def print_clusters(data_labels, clustering_labels):
@@ -23,6 +22,7 @@ def print_clusters(data_labels, clustering_labels):
         print(clusters[c_label])
         print("")
 
+
 # Fits an instance of Principal Components Analysis using given data
 def fit_pca(data, dimensions):
     pca = PCA(n_components=dimensions)
@@ -30,12 +30,14 @@ def fit_pca(data, dimensions):
 
     return pca
 
+
 # Fits an instance of Kernel Principal Components Analysis using given data
 def fit_kernel_pca(data, dimensions, kernel='poly', degree=4, gamma=0.05, random_state=69):
     kpca = KernelPCA(n_components=dimensions, kernel=kernel, gamma=gamma, random_state=random_state, degree=degree)
     kpca.fit(data)
 
     return kpca
+
 
 # Computes the clustering: First the data's dimensionality is reduced by transforming it according to the given PCA/KPCA
 # instance and then K-Means is applied to cluster the proejcted data
@@ -45,6 +47,7 @@ def cluster_data(data, pca, n_clusters, n_init=50, init="random", random_state=6
 
     return clustering
 
+
 # Assigns new data points to established clusters
 def predict_cluster(data, pca, clustering):
     projected_data = pca.transform(data)
@@ -52,10 +55,11 @@ def predict_cluster(data, pca, clustering):
 
     return clustering_labels, projected_data
 
+
 # Visualizes the results of clustering as 2D or 3D scatter plots
 def visualize_clustering(train_clusters, train_labels, train_projected, test_clusters=None, test_labels=None,
                          test_projected=None, fontsize=5, cmap="rainbow", dimensions=2):
-    #cmap = matplotlib.colors.Colormap(name=cmap)
+    # cmap = matplotlib.colors.Colormap(name=cmap)
     if dimensions == 2:
         fig = plt.figure()
         ax = fig.add_subplot()
@@ -92,37 +96,6 @@ def visualize_clustering(train_clusters, train_labels, train_projected, test_clu
 
     plt.show(block=True)
 
[…]

### 2023-06-26 code/clustering_kpca.py

@@ -110,7 +110,8 @@ def visualize_clustering(train_clusters, train_labels, train_projected, test_clu
         try:
             hull = ConvexHull(
                 points)  # computation might not work if data points in a cluster have a very weird position
-        except:
+        except Exception as e:
+            print(e)
             # plot the label of the cluster
             offset = (np.max(all_projected[:, 1]) - np.min(all_projected[:, 1])) * 0.025
             ax.text(np.min(points[:, 0]), np.max(points[:, 1]) + offset, "Cluster " + str(cluster),

### 2023-06-26 code/clustering_tsne.py

@@ -11,31 +11,32 @@ from scipy import interpolate
 import matplotlib
 
 colors = matplotlib.colors.ListedColormap(
-        [
-            "rosybrown",
-            "darkred",
-            "tan",
-            "darkkhaki",
-            "forestgreen",
-            "teal",
-            "steelblue",
-            "rebeccapurple",
-            "magenta",
-            "crimson",
-            "silver",
-            "brown",
-            "orange",
-            "darkgoldenrod",
-            "olive",
-            "lime",
-            "aqua",
-            "royalblue",
-            "darkorchid",
-            "hotpink"
-        ]
-    ).colors
+    [
+        "rosybrown",
+        "darkred",
+        "tan",
+        "darkkhaki",
+        "forestgreen",
+        "teal",
+        "steelblue",
+        "rebeccapurple",
+        "magenta",
+        "crimson",
+        "silver",
+        "brown",
+        "orange",
+        "darkgoldenrod",
+        "olive",
+        "lime",
+        "aqua",
+        "royalblue",
+        "darkorchid",
+        "hotpink"
+    ]
+).colors
 
 colors = matplotlib.colors.ListedColormap(plt.cm.tab20.colors).colors
+
 
 # Prints the results of clustering
 def print_clusters(data_labels, clustering_labels):
@@ -51,11 +52,14 @@ def print_clusters(data_labels, clustering_labels):
         print(clusters[c_label])
         print("\n")
 
+
 # Fits an instance of t-SNE using given data
 def project_tsne(data, dimensions, perplexity, random_state=69):
-    projected_data = TSNE(n_components=dimensions, perplexity=perplexity, random_state=random_state).fit_transform(np.array(data))
+    projected_data = TSNE(n_components=dimensions, perplexity=perplexity, random_state=random_state).fit_transform(
+        np.array(data))
 
     return projected_data
+
 
 # Creates a dendrogram to decide the number of clusters
 def plot_dendrogram(model, **kwargs):
@@ -76,21 +80,21 @@ def plot_dendrogram(model, **kwargs):
 
     dendrogram(linkage_matrix, **kwargs)
 
+
 # Computes clusters
 def predict_clusters(projected_data, n_clusters):
     clustering = AgglomerativeClustering(n_clusters=n_clusters, linkage='ward').fit(projected_data)
[…]

### 2023-06-26 code/data_util.py

@@ -39,7 +39,8 @@ def load_map_df():
         print(i, company)
         try:
             lat, lon = get_lat_lon_of_request(company + ", Saarland")
-        except Exception:
+        except Exception as e:
+            print(e)
             lat, lon = None, None
         data[i, 0] = lat
         data[i, 1] = lon

### 2023-06-26 code/description_data.py

@@ -2,56 +2,494 @@
 This script contains descriptions of companies taken from their websites.
 """
 
-train_descriptions = ["ZF is a global technology company supplying systems for passenger cars, commercial vehicles and industrial technology, enabling the next generation of mobility. ZF allows vehicles to see, think and act. In the four technology domains of Vehicle Motion Control, Integrated Safety, Automated Driving, and Electric Mobility, ZF offers comprehensive product and software solutions for established vehicle manufacturers. With some 165,000 employees worldwide, ZF reported sales of €43.8 billion in fiscal 2022. The company operates 168 production locations in 32 countries.",
-                      "The locations of Saarstahl AG not only have a long tradition but have also contributed to the shaping of the creation of history in the region. The Neunkirchen plant was mentioned as early as 1593. This makes it Saarstahl AG's location with the richest in tradition and, at the same time, it is even the oldest steelmaking location in Germany that is still active today. Burbach and Völklingen are both younger, having been founded in 1856 and 1873 as part of the increasing industrialisation of Germany. Each of the three steelworks then rapidly developed and, during the 20th century, they rose to become renowned large-scale enterprises with several thousand employees. In the 1970s, it started to make sense to combine forces. The current locations merged to a company that has had the name Saarstahl AG since 1989 and has made a name for itself as a global manufacturer of long products.",
-                      "The Dillinger Group is made up of a series of top-ranking companies which together provide maximum quality and best possible service in the field of heavy plate. This applies both to the work of our integrated iron-and-steel plant, to the production of coke and smelting of iron by Zentralkokerei Saar GmbH and ROGESA Roheisengesellschaft Saar mbH, two subsidiaries owned jointly with Saarstahl AG, and to the production of liquid steel and semi-fabricates. Heavy plate is produced at two locations, Dillinger Hütte, in Dillingen, and Dillinger France, in Dunkirk. In addition, our trading, flame-cutting and semi-fabrication affiliates provide further downstream services and customised solutions for sales, plus semi-fabrication of heavy plates and other steel products. The 2014 business year also witnessed the inauguration of Steelwind Nordenham GmbH, a 100% Dillinger subsidiary, specialising in the production of monopiles for the offshore wind-energy market. EUROPIPE GmbH, the world's leading producer of pipes for oil and natural gas pipelines, with locations in Germany and the USA, was founded in Mülheim an der Ruhr as a 50% subsidiary of Dillinger specifically for the production of pipes from pipe-making plates in 1991.",
[…]

### 2023-06-26 code/embeddings.py

@@ -8,19 +8,18 @@ from sentence_transformers import SentenceTransformer
 
 # Computes embeddings for descriptions by transforming each sentence in a description using a sentence transformer model
 # and then taking the average or maximum across all dimensions.
-def get_description_embeddings(descriptions, max=True, embed_type="max"):
+def get_description_embeddings(descriptions, embed_type="max", **kwargs):
     model = SentenceTransformer('sentence-transformers/all-MiniLM-L6-v2')
-    #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
     description_embeddings = []
     if embed_type in ["max", "mean"]:
-        max = embed_type == "max"
+        maximum = embed_type == "max"
         for description in descriptions:
-            sentences = re.split('\.|\!|\?', description)
+            sentences = re.split('[.!?]', description)
             sentence_embeddings = []
             for sentence in sentences:
                 sentence_embedding = model.encode(sentence)
                 sentence_embeddings.append(sentence_embedding)
-            if max:
+            if maximum:
                 description_embedding = np.max(sentence_embeddings, axis=0)
             else:
                 description_embedding = np.mean(sentence_embeddings, axis=0)
@@ -28,12 +27,10 @@ def get_description_embeddings(descriptions, max=True, embed_type="max"):
         return description_embeddings
     else:
         for description in descriptions:
-            sentences = re.split('\.|\!|\?', description)
+            sentences = re.split('[.!?]', description)
             sentence_embeddings = []
-            embedding_shape = None
             for sentence in sentences:
                 sentence_embedding = model.encode(sentence)
-                embedding_shape = sentence_embedding.shape
                 sentence_embeddings.append(sentence_embedding)
             counter = 0
             while len(sentence_embeddings) < 15:
@@ -44,32 +41,3 @@ def get_description_embeddings(descriptions, max=True, embed_type="max"):
                 flattened_embeddings += list(embedding)
             description_embeddings.append(flattened_embeddings)
         return description_embeddings
-
-
-def get_full_embeddings(descriptions):
-#def get_description_embeddings(descriptions):
-    model = SentenceTransformer('sentence-transformers/all-MiniLM-L6-v2')
-    description_embeddings = []
-    min_sentences = 100
-    max_sentences = 0
-    for description in descriptions:
-        sentences = re.split('\.|\!|\?', description)
-        min_sentences = min(min_sentences, len(sentences))
[…]

### 2023-06-26 code/visualisation.py

@@ -1,7 +1,6 @@
 from code.clustering_tsne import project_tsne, predict_clusters
 from code.clustering_kpca import predict_cluster, fit_kernel_pca, cluster_data
-from code.embeddings import get_description_embeddings
-from code.description_data import train_descriptions, train_labels
+from code.description_data import train_labels
 import numpy as np
 import streamlit as st
 import plotly.express as px
@@ -39,7 +38,8 @@ def compute_hull(points):
     # compute convex hull
     try:
         hull = ConvexHull(points)  # computation might not work if data points in a cluster have a very weird position
-    except:
+    except Exception as e:
+        print(e)
         return points[:, 0], points[:, 1]
     x_hull = np.append(points[hull.vertices, 0],
                        points[hull.vertices, 0][0])
@@ -160,12 +160,12 @@ def add_similarity_heatmap(fig, distances, max_distance, cluster, clusters):
                                     'Revenue: %{customdata[10]}€')
     map_fig.add_traces(data=fig.data)
     map_fig.update_traces(hovertemplate='<b>%{customdata[5]}</b><br>'
-                                    'Similarity: %{customdata[11]:.2%}<br>'
-                                    'Industry: %{customdata[6]} <br>'
-                                    'Products: %{customdata[7]} <br>'
-                                    'Customer base: %{customdata[8]} <br>'
-                                    'Market Position: %{customdata[9]} <br>'
-                                    'Revenue: %{customdata[10]}€')
+                                        'Similarity: %{customdata[11]:.2%}<br>'
+                                        'Industry: %{customdata[6]} <br>'
+                                        'Products: %{customdata[7]} <br>'
+                                        'Customer base: %{customdata[8]} <br>'
+                                        'Market Position: %{customdata[9]} <br>'
+                                        'Revenue: %{customdata[10]}€')
 
     return map_fig
 

### 2023-06-26 pages/00_Analysis.py

@@ -1,15 +1,10 @@
 import streamlit as st
-import time
 import numpy as np
-import pandas as pd
-import code.description_data as data
-import requests
 from code.visualisation import compute_tsne, compute_kpca, \
     plot_2d, plot_3d, plot_map, load_economic_df, add_similarity_heatmap, add_clusters
 from code.data_util import get_embeddings
 import plotly.graph_objects as go
 import plotly.express as px
-
 
 st.set_page_config(layout="wide")
 
@@ -20,49 +15,30 @@ def close_expander():
 
 
 @st.cache_data
-def compute_clustering(test_features, embedding_type, features, method, n_clusters, dimensions):
-    embedding_type = "max" if embedding_type == "Maximum of Features" else \
-        ("mean" if embedding_type == "Mean of Features" else embedding_type)
+def compute_clustering(test_features, embed_type, feature_list, dim_reduct_method, num_clusters, num_dims):
+    embed_type = "max" if embed_type == "Maximum of Features" else \
+        ("mean" if embed_type == "Mean of Features" else embed_type)
     economic_df = load_economic_df()
     input_features = []
-    if "Description" in features:
-        embeddings = get_embeddings(embedding_type,
+    if "Description" in feature_list:
+        embeddings = get_embeddings(embed_type,
                                     test_feature=test_features["Description"])
         input_features += list(np.moveaxis(np.array(embeddings), 0, -1))
-        features.remove("Description")
-    for feature in features:
-        embeddings = get_embeddings(embedding_type,
+        feature_list.remove("Description")
+    for feature in feature_list:
+        embeddings = get_embeddings(embed_type,
                                     test_feature=test_features[feature],
                                     data_to_embed=list(economic_df[feature]))
         input_features += list(np.moveaxis(np.array(embeddings), 0, -1))
-    input = np.moveaxis(np.array(input_features), 0, -1)
-    if method == "t-SNE":
-        clusters, projected = compute_tsne(n_clusters, dimensions, input)
-    elif method == "Kernel PCA":
-        clusters, projected = compute_kpca(n_clusters, dimensions, input)
-    return clusters, projected
-
-
-def get_lat_lon_of_request(search_string):
-    url = 'https://nominatim.openstreetmap.org/search/' + urllib.parse.quote(search_string) + '?format=json'
-    response = requests.get(url).json()
-    return response[0]["lat"], response[0]["lon"]
-
-
-@st.cache_data
[…]

### 2023-06-26 pages/01_Clustering.py

@@ -1,12 +1,5 @@
 import streamlit as st
 import numpy as np
-import requests
-import os
-
-import paths
-from code.description_data import train_labels
-import urllib
-import pandas as pd
 from code.data_util import get_embeddings, load_economic_df, load_map_df
 from code.visualisation import compute_tsne, compute_kpca, \
     plot_2d, plot_3d, plot_map, add_clusters
@@ -16,30 +9,32 @@ st.set_page_config(layout="wide")
 
 
 @st.cache_data
-def compute_clustering(embedding_type, features: list[str], method, n_clusters):
-    embedding_type = "max" if embedding_type == "Maximum of Features" else \
-        ("mean" if embedding_type == "Mean of Features" else embedding_type)
+def compute_clustering(embed_type, feature_list: list[str], dim_reduct_method, num_clusters):
+    embed_type = "max" if embed_type == "Maximum of Features" else \
+        ("mean" if embed_type == "Mean of Features" else embed_type)
     economic_df = load_economic_df()
     map_df = load_map_df()
     input_features = []
-    if "Description" in features:
-        embeddings = get_embeddings(embedding_type)
+    if "Description" in feature_list:
+        embeddings = get_embeddings(embed_type)
         input_features += list(np.moveaxis(np.array(embeddings), 0, -1))
-        features.remove("Description")
-    if "Location" in features:
+        feature_list.remove("Description")
+    if "Location" in feature_list:
         input_features.append(list(map_df["latitude"]))
         input_features.append(list(map_df["longitude"]))
-        features.remove("Location")
-    for feature in features:
-        embeddings = get_embeddings(embedding_type, data_to_embed=list(economic_df[feature]))
+        feature_list.remove("Location")
+    for feature in feature_list:
+        embeddings = get_embeddings(embed_type, data_to_embed=list(economic_df[feature]))
         input_features += list(np.moveaxis(np.array(embeddings), 0, -1))
-    input = np.moveaxis(np.array(input_features), 0, -1)
-    if method == "t-SNE":
-        clusters_2d, projected_2d = compute_tsne(n_clusters, 2, input)
-        clusters_3d, projected_3d = compute_tsne(n_clusters, 3, input)
-    elif method == "Kernel PCA":
-        clusters_2d, projected_2d = compute_kpca(n_clusters, 2, input)
-        clusters_3d, projected_3d = compute_kpca(n_clusters, 3, input)
[…]

### 2023-06-26 pages/03_Team.py

@@ -3,7 +3,7 @@ import PIL.Image as Image
 
 st.title("Team")
 placeholder = Image.open("pages/images/placeholder_person.png")
-col1, col2 = st.columns([1,1])
+col1, col2 = st.columns([1, 1])
 with col1:
     st.image(placeholder)
     st.subheader("Nicola Müller")

### 2023-06-26 pages/04_Paper.py

@@ -13,7 +13,8 @@ def displayPDF(file):
         base64_pdf = base64.b64encode(f.read()).decode('utf-8')
 
     # Embedding PDF in HTML
-    pdf_display = F'<iframe src="data:application/pdf;base64,{base64_pdf}" width="1700" height="1000" type="application/pdf"></iframe>'
+    pdf_display = F'<iframe src="data:application/pdf;base64,{base64_pdf}" ' \
+                  F'width="1700" height="1000" type="application/pdf"></iframe>'
 
     # Displaying File
     st.markdown(pdf_display, unsafe_allow_html=True)

### 2023-06-26 scripts/cluster_descriptions.py

@@ -3,22 +3,20 @@ This script computes a clustering for given data and makes predictions for new d
 """
 import numpy as np
 from code.description_data import train_descriptions, train_labels, test_descriptions, test_labels
-from code.embeddings import get_description_embeddings, get_full_embeddings
-from code.clustering import fit_pca, fit_kernel_pca, cluster_data, predict_cluster, visualize_clustering, visualize_tsne, print_clusters
+from code.embeddings import get_description_embeddings
+from code.clustering import fit_pca, fit_kernel_pca, cluster_data, predict_cluster, visualize_clustering, \
+    visualize_tsne, print_clusters
 
 assert len(train_labels) == len(train_descriptions), print(len(train_labels), len(train_descriptions))
 
-# = get_description_embeddings(train_descriptions, max=True)
-#test_embeddings = get_description_embeddings(test_descriptions, max=True)
-
-train_embeddings = get_full_embeddings(train_descriptions)
-test_embeddings = get_full_embeddings(test_descriptions)
+train_embeddings = get_description_embeddings(train_descriptions, embed_type="max")
+test_embeddings = get_description_embeddings(test_descriptions, embed_type="max")
 
 n_clusters = int(np.floor(np.sqrt(len(train_descriptions)))) + 4
 
 pca = fit_kernel_pca(data=train_embeddings, dimensions=3)
 
-clustering = cluster_data(data=train_embeddings, kpca=pca, n_clusters=n_clusters, n_init=50,
+clustering = cluster_data(data=train_embeddings, pca=pca, n_clusters=n_clusters, n_init=50,
                           init="random", random_state=69)
 
 train_clusters, train_projected = predict_cluster(data=train_embeddings, pca=pca, clustering=clustering)
@@ -30,6 +28,5 @@ visualize_clustering(train_clusters=train_clusters, train_labels=train_labels, t
                      test_clusters=test_clusters, test_labels=test_labels, test_projected=test_projected,
                      fontsize=8, cmap="rainbow", dimensions=3)
 
-#"""
-visualize_tsne(data=train_embeddings+test_embeddings, labels=train_labels+test_labels, dimensions=2,
-            perplexity=np.sqrt(len(train_embeddings)+len(test_embeddings)), fontsize=5, random_state=69)
+visualize_tsne(data=train_embeddings + test_embeddings, labels=train_labels + test_labels, dimensions=2,
+               perplexity=np.sqrt(len(train_embeddings) + len(test_embeddings)), fontsize=5, random_state=69)

### 2023-06-26 scripts/excel_to_csv.py

@@ -1,5 +1,6 @@
 import pandas as pd
 
+
 def xlsx_to_csv(input_file_path, output_file_path):
     # Load spreadsheet
     xl = pd.read_excel(input_file_path)
@@ -7,5 +8,6 @@ def xlsx_to_csv(input_file_path, output_file_path):
     # Save it as csv file
     xl.to_csv(output_file_path, index=False, encoding='utf-8')
 
+
 # usage
-xlsx_to_csv('../Book1.xlsx', '../data/economic_data.csv')
+# xlsx_to_csv('../Book1.xlsx', '../data/economic_data.csv')

### 2023-06-26 scripts/names_to_file.py

@@ -1,5 +1,3 @@
-from code.description_data import train_labels
-
 def save_strings_to_file(strings, filename):
     """
     This function saves a list of strings to a file with each string on a new line.
@@ -10,8 +8,3 @@ def save_strings_to_file(strings, filename):
     with open(filename, 'w') as f:
         for item in strings:
             f.write("%s\n" % item)
-
-
-# usage
-filename = "companies.txt"
-save_strings_to_file(train_labels, filename)

### 2023-06-26 scripts/optimize_pca.py

@@ -6,13 +6,16 @@ from sklearn.model_selection import GridSearchCV
 from sklearn.metrics import mean_squared_error
 from sklearn.decomposition import PCA, KernelPCA
 from code.description_data import train_descriptions
-from code.embeddings import get_description_embeddings, get_full_embeddings
+from code.embeddings import get_description_embeddings
 
-embeddings = get_full_embeddings(train_descriptions)
-def my_scorer(estimator, X, y=None):
-    X_reduced = estimator.transform(X)
-    X_preimage = estimator.inverse_transform(X_reduced)
-    return -1 * mean_squared_error(X, X_preimage)
+embeddings = get_description_embeddings(train_descriptions, embed_type="max")
+
+
+def my_scorer(estimator, x):
+    x_reduced = estimator.transform(x)
+    x_preimage = estimator.inverse_transform(x_reduced)
+    return -1 * mean_squared_error(x, x_preimage)
+
 
 param_grid = [{
     "gamma": np.linspace(0.03, 0.05, 10),

### 2023-06-26 scripts/predictions_kpca.py

@@ -12,7 +12,6 @@ assert len(train_labels) == len(train_descriptions), print(len(train_labels), le
 # Compute the clustering of the training data
 train_embeddings = get_description_embeddings(train_descriptions)
 n_clusters = int(np.floor(np.sqrt(len(train_descriptions)))) + 4
-n_clusters = 11
 pca = fit_kernel_pca(data=train_embeddings, random_state=42)
 clustering = cluster_data(data=train_embeddings, kpca=pca, n_clusters=n_clusters, random_state=42)
 train_clusters, train_projected = predict_cluster(data=train_embeddings, kpca=pca, clustering=clustering)
@@ -45,7 +44,8 @@ while True:
     test_clusters, test_projected = predict_cluster(data=test_embeddings, kpca=pca, clustering=clustering)
 
     print("\n")
-    print(f"Our analysis assigned {test_label} to the cluster {test_clusters[0]}, which contains the following companies (ordered according to similarity):")
+    print(f"Our analysis assigned {test_label} to the cluster {test_clusters[0]},"
+          f" which contains the following companies (ordered according to similarity):")
 
     labels_and_distances = []
     for company in clusters_dict[test_clusters[0]]:

### 2023-06-26 scripts/predictions_tsne.py

@@ -12,13 +12,13 @@ assert len(train_labels) == len(train_descriptions), print(len(train_labels), le
 # Compute the clustering of the training data
 train_embeddings = get_description_embeddings(train_descriptions)
 n_clusters = int(np.floor(np.sqrt(len(train_descriptions)))) + 5
-n_clusters = 11
-projected_train_embeddings = project_tsne(data=train_embeddings, dimensions=2, perplexity=np.sqrt(len(train_embeddings)),
+projected_train_embeddings = project_tsne(data=train_embeddings, dimensions=2,
+                                          perplexity=np.sqrt(len(train_embeddings)),
                                           random_state=42)
 clusters, projected = predict_clusters(projected_data=projected_train_embeddings, n_clusters=n_clusters)
 
 visualize_clustering(clusters=clusters, labels=train_labels, projected=projected,
-                             fontsize=8)
+                     fontsize=8)
 
 print("Welcome to LM-based Saarland Economy Clustering!")
 while True:
@@ -35,11 +35,13 @@ while True:
     all_embeddings = train_embeddings + new_embedding
     all_labels = train_labels + [new_label]
     projected_embeddings = project_tsne(data=all_embeddings, dimensions=2, perplexity=np.sqrt(len(all_embeddings)),
-                                             random_state=69)
+                                        random_state=69)
     clusters, projected = predict_clusters(projected_data=projected_embeddings, n_clusters=n_clusters)
 
     print("\n")
-    print(f"Our analysis assigned {new_label} to the cluster {clusters[-1]}, which contains the following companies (ordered according to similarity):")
+    print(
+        f"Our analysis assigned {new_label} to the cluster {clusters[-1]}, which contains"
+        f" the following companies (ordered according to similarity):")
 
     clusters_dict = {}
     for c_label in clusters:
@@ -55,13 +57,13 @@ while True:
     for company in clusters_dict[clusters[-1]]:
         if company != new_label:
             company_projected = projected_dict[company]
-            distance = np.linalg.norm(new_projected-company_projected)
+            distance = np.linalg.norm(new_projected - company_projected)
             labels_and_distances.append((company, distance))
 
     labels_and_distances.sort(key=lambda x: x[1])
 
     for i in range(len(labels_and_distances)):
-        print(f"{i+1}: {labels_and_distances[i][0]} (similarity: {labels_and_distances[i][1]:.3f})")
[…]

### 2023-06-27 report/report.tex
feat: Dockerbuild & rework readme

@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
+% Multi-column list
+\usepackage{multicol}
 
@@
 When a description was only available in German, we translated it to English using the online translator DeepL.
-A list of all companies in our dataset can be found in the appendix \ref{sec:appendix-a}.
+A list of all companies in our dataset can be found in the appendix \ref{sec:appendix-companies}.
 We conducted the data collection manually since company websites are generally structured very differently, making it complicated to extract such information automatically.
@@
 
+\newpage
 \appendix
@@
 
+\subsection{Additional Clustering Results}
+
+\subsection{Link to Code}
+\url{https://github.com/NicolaMueller42/data_science_project}
+
+\subsection{Link to Overleaf}
+
 \subsection{Companies in our Dataset}
-\label{sec:appendix-a}
+\label{sec:appendix-companies}
+
 We list the $50$ Saarland companies in our dataset:
-\begin{itemize}
+\begin{multicols}{2} \begin{itemize}
 	\item ZF
@@
 	\item Schröder
-\end{itemize}
-
-\subsection{Additional Clustering Results}
-
-\subsection{Link to Code}
-\url{https://github.com/NicolaMueller42/data_science_project}
-
-\subsection{Link to Overleaf}
+\end{itemize}\end{multicols}
 

### 2023-06-27 Home.py

@@ -35,8 +35,8 @@ with text:
         
     st.markdown("Our multidisciplinary team consists of five highly skilled professionals, blending expertise "
                 "from diverse "
-                "backgrounds. Two members hold a Bachelor of Science in Data Science and AI, possessing a deep"
-                " understanding of cutting-edge AI techniques and models. Another member brings a Bachelor of "
+                "backgrounds. One member holds a Bachelor of Science in Data Science and AI, possessing a deep"
+                " understanding of cutting-edge AI techniques and models. One member brings a Bachelor of "
                 "Science in Computer Science, ensuring robust implementation and system optimization. "
                 "Finally, our two team members with Bachelor of Science degrees in Economics bring valuable insights "
                 "into market dynamics and business strategy.")

### 2023-06-27 pages/03_Team.py

@@ -16,7 +16,7 @@ col3, col4 = st.columns([1, 1])
 with col3:
     st.image(placeholder)
     st.subheader("Paul Eichler")
-    st.write("Bachelor of Science - Data Science and Artificial Intelligence")
+    st.write("Computer Science")
 with col4:
     st.image(placeholder)
     st.subheader("Tobias Recktenwald")

### 2023-06-28 report/report.tex
rewrite of results section

@@
 \subsection{Clustering}
+\label{sec:clustering-results}
 In the following, we analyze each of the found clusters and interpret them with respect to potential market segments:
 \begin{itemize}
-    \item \textit{Cluster 0 (dark blue)}: This cluster contains the four large food producers Karlsberg, Kunzler, Ludwig Schokolade, and Schröder.
-Hence, we classify it as the food market segment.
-It also contains Globus, a large supermarket chain that also produces its own foods.
-The last member of this cluster is Dillinger, which we can discard as incorrectly assigned since it is a steel manufacturer.
+    \item \textit{Cluster 0 (red)}: This cluster consists of automotive manufacturers and suppliers, such as Ford and Michelin.
+Hence, we follow that this cluster represents the automotive industry market segment.
 
-    \item \textit{Cluster 1 (light blue)}: We cannot infer a market segment from the members of this cluster since it contains vastly different companies, such as the pharmaceutical company URSAPHARM, the ceramics manufacturer Villeroy\&Boch, and the steel manufacturer Saarstahl.
-However, it contains the construction companies Peter Gross Bau and Backes AG, and the OBG Group, which is assigned to Cluster $5$, is another construction company close to the first two companies.
-Hence, we follow that there is a construction market segment in Saarland.
+    \item \textit{Cluster 1 (light green)}: The steel industry companies MAT Foundries, ThyssenKrupp, and Meiser are part of this cluster.
+Further cluster members are companies like Hörmann and HYDAC, which also offer products manufactured from steel.
+Accordingly, we assign this cluster to the steel products market segment.
+Note that the food manufacturer Wagner can be considered misclassified, as it should be contained in Cluster 10.
 
-    \item \textit{Cluster 2 (dark orange)}: The data points of this cluster have the largest relative distance due to them sharing no commonalities, and thus we cannot derive a potential market segment.
+    \item \textit{Cluster 2 (dark blue)}: We attribute this cluster to the healthcare market segment since it contains the medicine manufacturers Dr.
+Theiss and URSAPARM, Fresenius which produces dialysis machines, and Unimed which provides accounting services for hospitals.
+Note that the IT consulting firm Scheer can be considered misclassified and should be added to Cluster 3.
 
-    \item \textit{Cluster 3 (light orange)}: The large automotive suppliers ZF and Michelin are part of this cluster, which explains its proximity to Cluster $7$ (automotive industry market segment).
-However, Hörmann, which produces doors for commercial and industrial applications, and Festo, which produces industrial automation systems, are also part of this cluster.
-Since the only commonality between these companies is that they are large, multi-national, industrial companies, we cannot assign them to a single market segment.
+    \item \textit{Cluster 3 (beige)}: This cluster contains the IT companies SAP, ORBIS, eurodata, IAS Software, and Welcoalize, so it represents IT products and IT consulting market segment.
+Although the cluster member Bosch is not an IT company, it also offers software products, so we do not consider it misclassified.
 
-    \item \textit{Cluster 4 (dark green)}: The IT / IT consulting firms eurodata, ORBIS, Scheer, and SAP are part of this cluster, so we classify it as the IT consulting market segment.
-The fifth member of this cluster is Iqony Energies, which is seemingly misclassified since it provides energy solutions, yet it resembles the other cluster members since it also does consulting and IT infrastructure.
+    \item \textit{Cluster 4 (purple)}: This cluster consists of the companies Globus, Möbel Martin, and Villeroy\&Boch, which offer very different products but are all large retailers.
+Hence, we assign this cluster to the retail market segment.
 
-    \item \textit{Cluster 5 (light green)}: This cluster contains the companies Welocalize, Unimed, and IAS Software, which provide IT services such as document translation, accounting, and data collection.
-Hence, we follow that this cluster is representative of the IT service market segment.
-Note that the remaining two cluster members can be considered incorrectly assigned.
-HYDAC should be added to Cluster $7$ (automotive industry market segment), and OBG Group should be in a single cluster with Peter Gross Bau and Backes AG (construction market segment).
+    \item \textit{Cluster 5 (light blue)}: The energy provider energis and the energy service providers Iqony Energies and Greencells are contained in this cluster.
+Hager, which specializes in electrical installation and energy distribution, is also a cluster member.
+Accordingly, we infer that this cluster represents the energy market segment.
 
-    \item \textit{Cluster 6 (dark red)}: The only two members of this cluster are Uni Saar and CISPA, making it representative of the academia market segment.
+    \item \textit{Cluster 6 (yellow)}: We assign this cluster to the steel production market segment since it contains the steel manufacturers Dillinger and Saarstahl.
+The defence company Diehl Defence can be considered misclassified, as it should be in its own cluster due to it being the only defence company in our dataset.
 
-    \item \textit{Cluster 7 (light red)}: It corresponds to the automotive industry market segment since it comprises the automotive manufacturers and suppliers Nemak, Ford, ThyssenKrupp, Schaeffler, and SaarGummi.
+    \item \textit{Cluster 7 (orange)}: This cluster consists of the construction companies Backes AG, Peter Gross Bau, and OBG Group, so it represents the construction work market segment.
 
-    \item \textit{Cluster 8 (dark purple)}: This cluster contains Bosch, VOIT, Fresenius, and Purem, which focus on electrical engineerings, such as filtration systems and powertrain components for electric cars.
-Thus, this cluster corresponds to the electronics industry market segment.
+    \item \textit{Cluster 8 (dark green)}: Because the insurance companies CosmosDirekt and IKK Südwest are part of this cluster, it could indicate the insurance market segment.
+However, this cluster also contains the healthcare service provider Caritas, which should be in Cluster 2, and the credit card provider PLUSCARD.
 
-    \item \textit{Cluster 9 (light purple)}: The companies MAT Foundries and Meiser, which specialize in steel products, are part of this cluster, and the last cluster member is the weapons manufacturer Diehl Defence.
-This suggests that this cluster represents the steel industry market segment, and we note that the companies Dillinger and Saarstahl should also be contained in it.
+    \item \textit{Cluster 9 (lavender)}: The only two members of this cluster are Uni Saar and CISPA, making it representative of the academia market segment.
 
-    \item \textit{Cluster $10$ (brown)}: This cluster consists of Caritas, IKK Südwest, and CosmosDirekt, and thus we classify it as the healthcare and insurance market segment.
+    \item \textit{Cluster $10$ (pink)}: This cluster consists of food producers such as Kunzler, and Ludwig Schokolade, and thus it represents the food market segment.
 \end{itemize}
+We conclude that our clustering methods are effective since we saw that each of the 11 clusters mostly contained similar companies, allowing us to infer various market segments.
 
@@
 \subsection{Limitations}
-We observed in subsection \textit{A} that we could not derive corresponding market segments for a small number of clusters because the cluster members had too different characteristics.
-These companies mostly belonged to sectors that are underrepresented in our dataset, such as ceramics manufacturing and pharmaceutics, so we would likely achieve more concise cluster assignments if we added more companies from these sectors to our dataset.
+We observed in subsection \ref{sec:clustering-results} that a small number of companies were assigned to the wrong clusters.
+These companies mostly belonged to sectors that are underrepresented in our dataset, such as defence and financial services, so we would likely achieve more concise cluster assignments if we added more companies from these sectors to our dataset.
 
 Another reason for invalid cluster assignments could be that our utilized sentence transformer was not fine-tuned for company descriptions, so that it could have produced inaccurate embeddings for some descriptions.
-Further, projecting the embeddings into 2D space could also cause inaccurate cluster assignments due to a large loss of information.
-Projecting the embeddings into higher dimensions might avoid this information loss, yet it would likely complicate or prevent a user-friendly visualization of the clustering results.
-We note that we observed no benefits from projecting the embeddings into 3D space.
+Further, projecting the embeddings into 2D or 3D space could also cause inaccurate cluster assignments due to a large loss of information.
+Projecting the embeddings into higher dimensions might avoid this information loss, yet it would complicate or prevent a user-friendly visualization of the clustering results.
 

### 2023-06-28 report/report.tex
fixed typos

@@
 \section{Introduction}
-\color{red} 
-I need the business guys to check the following paragraph!
-\color{black}
-
 Identifying market segments in regional economies is crucial for effective marketing strategies and making well-informed business decisions.
@@
 Accordingly, we assign this cluster to the steel products market segment.
-Note that the food manufacturer Wagner can be considered misclassified, as it should be contained in Cluster 10.
+The food manufacturer Wagner can be considered misclassified, as it should be contained in Cluster 10.
 
 	\item \textit{Cluster 2 (dark blue)}: We attribute this cluster to the healthcare market segment since it contains the medicine manufacturers Dr.
-Theiss and URSAPARM, Fresenius which produces dialysis machines, and Unimed which provides accounting services for hospitals.
+Theiss and URSAPARM, Fresenius, which produces dialysis machines, and Unimed, which provides accounting services for hospitals.
 Note that the IT consulting firm Scheer can be considered misclassified and should be added to Cluster 3.
 
-    \item \textit{Cluster 3 (beige)}: This cluster contains the IT companies SAP, ORBIS, eurodata, IAS Software, and Welcoalize, so it represents IT products and IT consulting market segment.
+	\item \textit{Cluster 3 (beige)}: This cluster contains the IT companies SAP, ORBIS, eurodata, IAS Software, and Welcoalize, representing the IT products and IT consulting market segment.
 Although the cluster member Bosch is not an IT company, it also offers software products, so we do not consider it misclassified.
@@
 	\item \textit{Cluster 5 (light blue)}: The energy provider energis and the energy service providers Iqony Energies and Greencells are contained in this cluster.
-Hager, which specializes in electrical installation and energy distribution, is also a cluster member.
+Hager is also a cluster member specializing in electrical installation and energy distribution.
 Accordingly, we infer that this cluster represents the energy market segment.
@@
 	\item \textit{Cluster 6 (yellow)}: We assign this cluster to the steel production market segment since it contains the steel manufacturers Dillinger and Saarstahl.
-The defence company Diehl Defence can be considered misclassified, as it should be in its own cluster due to it being the only defence company in our dataset.
+The defense company Diehl Defence can be considered misclassified, as it should be in a single cluster because it is the only defense company in our dataset.
 
@@
 
-    \item \textit{Cluster $10$ (pink)}: This cluster consists of food producers such as Kunzler, and Ludwig Schokolade, and thus it represents the food market segment.
+	\item \textit{Cluster $10$ (pink)}: This cluster consists of food producers such as Kunzler and Ludwig Schokolade, and thus it represents the food market segment.
 \end{itemize}
@@
 We observed in subsection \ref{sec:clustering-results} that a small number of companies were assigned to the wrong clusters.
-These companies mostly belonged to sectors that are underrepresented in our dataset, such as defence and financial services, so we would likely achieve more concise cluster assignments if we added more companies from these sectors to our dataset.
+These companies mostly belonged to sectors that are underrepresented in our dataset, such as defense and financial services, so we would likely achieve more concise cluster assignments if we added more companies from these sectors to our dataset.
 

### 2023-06-28 report/report.tex
wrote conclusion

@@
 Further, users can see the location and clustering assignment of all companies in our dataset on a map.
-When hovering the mouse over a company's data point, additional information about the company is shown.
+When hovering the mouse over a company's data point, additional information about the company is shown, and when double clicking the labels on the legend, only the companies of the corresponding cluster are shown.
 
@@
 \section{Conclusion}
-\begin{itemize}
-	\item \textbf{Recapitulate the Objectives:} Begin by restating the main project objectives or questions that guided your study.
-This helps to remind the reader of the purpose and scope of your research \cite{sample-article}.
-	\item \textbf{Summarize the Key Findings:} Provide a brief summary of the main findings from your study.
-Highlight the most important results and their implications.
-However, avoid repeating all the details presented in the Results section.
-Instead, focus on the key outcomes that directly address your research objectives \cite{sample-web}.
-	\item \textbf{Future Research Suggestions:} Identify potential directions for future research based on the limitations or gaps identified in your study.
-Discuss areas that would benefit from additional investigation or areas where more data or different methodologies could provide deeper insights.
-	\item \textbf{Final remarks:} Provide a concise and thoughtful closing statement that summarizes the overall significance of your research.
-Reflect on the importance of your study and its potential impact on the field.
-Consider the broader implications of your findings and emphasize the value of your research contribution.
-\end{itemize}
+The goal of this project was to collect data on companies in Saarland and apply clustering algorithms such that the results can be used to identify market segments and to give location recommendations for novel companies such that business clusters are fostered.
+
+To circumvent the challenges of feature selection and encoding non-numerical features, we represented companies by their publicly available descriptions.
+We leveraged state-of-the-art language models to transform this highly informative text data into machine-readable embeddings.
+Lastly, we utilized two approaches to project the embeddings into low-dimensional space where clustering can be applied.
+Further, our methods allowed straightforwardly including other standard company attributes, such as industry, customer base, market positioning, and revenue. 
+To make location recommendations, we passed the descriptions and features of novel companies to our clustering pipeline and then recommended establishing new sites next to the most similar companies in our dataset.
+
+A qualitative evaluation of our methods has shown that they can reliably cluster similar companies, which allowed us to infer market segments in Saarland.
+Further, our location recommendation system demonstrated its capability of identifying similar companies, given the description of a new company, independently of the total number of similar companies in the dataset.
+
+To allow end-users to leverage our methods, we implemented a user-friendly interface with many functionalities, such as visualizing the clustered data points, modifying the clustering parameters, showing the location of companies, and giving detailed and interpretable location recommendations.
+
+We see many opportunities for future work.
+Collecting data from more companies in Saarland could improve the clustering results, although the number of (large) companies in Saarland is limited.
+Thus, applying our methods to larger economies would be highly interesting.
+Further, fine-tuning our language models using text data from the business sector might lead to more expressive embeddings.
+To this end, we have demonstrated the feasibility and potential of applying language models to economic analysis.
 

### 2023-06-28 report/report.tex
adjusted comments

@@
 \pe{This seems a harsh claim, in practice one could argue that it is available through regional connections}
-\nm{Keep the current motivation for using company descriptions and then only later mention that we can also add other features?}
+\nm{We keep the current motivation for using company descriptions and then only later mention that we can also add other features}
 
@@
 \section{Results}
-\nm{Rewrite clustering section for the new results, keep location recommendation results as they are?}
 \begin{figure}[H]

### 2023-06-30 paper/paper.tex
add paper template

\documentclass[12pt]{article}

\include{./wits_template.zex}

\author{gg}
\title{test}
\begin{document}
    \maketitle
    gg
\end{document}

### 2023-06-30 report/report.tex
added matriculation number
add paper template

@@
 \IEEEauthorblockN{5\textsuperscript{th} Nazari Hameed}
-\IEEEauthorblockA{Email Address \\ Matriculation No.}
+\IEEEauthorblockA{abna00001@stud.uni-saarland.de \\ 7004543}
 }
@@
 \section{Introduction}
+
 Identifying market segments in regional economies is crucial for effective marketing strategies and making well-informed business decisions.
@@
 
-This work demonstrates how to identify market segments and develop business clusters by introducing an automatic clustering pipeline and location recommendation system for economic data from the German federal state Saarland.
+At the same time, recent advances in natural language processing (NLP), e.g.
+in the form of the popular ChatGPT \cite{chatgpt}, have led to surprisingly good results in numerous applications.
+Examples range from complex Code generation to essays to cooking recipes.
+
+This work demonstrates market segments and business clusters can be identified effectively by introducing an automatic clustering pipeline.
+Utilizing those clusters, our system is then able to provide a strategic location, which we will demonstrate by using the German federal state Saarland as an example.
 The novelty of our approach is that we rely on language models to encode the companies' information.
@@
 
+\subsection{Identification and Impacts of Business Clusters}
+
+\subsection{Natural Language Processing}
+
 In natural language processing (NLP), translating text data to machine-processable representations is a fundamental challenge for numerous tasks, such as machine translation~\cite{qi2018and}, sentiment analysis~\cite{rezaeinia2019sentiment}, and information retrieval~\cite{ye2016word}, due to the complexity and variability of natural language.
@@
 Starting with pre-trained BERT-networks, Sentence-BERT is fine-tuned using text classification or cosine-similarity tasks, yielding a model capable of generating high-quality sentence embeddings using only a fraction of the original BERT model's computational effort.
+
+\pe{Maybe we should bring out the connection to our approach here a little bit more}
 

### 2023-07-01 report/report.tex
add related work on economy

@@
 
-Identifying market segments in regional economies is crucial for effective marketing strategies and making well-informed business decisions.
-Further, combining geographical data of companies' locations with information on their corresponding market segments allows for detecting business clusters, which are local concentrations of businesses, manufacturers, suppliers, and institutions from the same field.
-This geographic proximity of related businesses enables efficient cooperation and knowledge transfer, which has been shown to significantly increase the productivity of all businesses within the cluster (citation).
+Deciding on location of a business is a vital strategic decision.
+Finding the right location can have a number of benefits: First, it is crucial to most businesses to be located close to its customers and suppliers, for more effective marketing or reduced transportation costs, secondly, being located in an active regional cluster can significantly benefit a business development \cite{clustersandcomp,gems-model, regionaladv, clustertheory}.
+
+Clusters are local concentrations of businesses, manufacturers, suppliers, and institutions from the same field.
+Identifying regional clusters is done by combining geographical data of companies' locations with information on their corresponding market segments.
+This geographic proximity of related businesses enables efficient cooperation and knowledge transfer, which has been shown to significantly increase the productivity of all businesses within the cluster \cite{clustersandcomp,gems-model, regionaladv, clustertheory}.
 Thus, establishing or further developing business clusters is of high interest to companies and local governments.
+Therefore, significant effort is spent identifying clusters and market segments in regional economies.
 
-\pe{I find the claims made in this paragraph to be to not backed by evidence.
-While I have no economic background, I was able to source some existing literature, e.g.
-\href{http://biblioteca.fundacionicbc.edu.ar/images/d/de/Clusters_1.pdf}{1}, \href{https://onlinelibrary.wiley.com/doi/full/10.1111/j.1536-7150.2011.00819.x}{2},
-\href{https://www.jstor.org/stable/144358?seq=1}{3}, \href{https://www.emerald.com/insight/content/doi/10.1108/14715200280001472/full/pdf?title=cluster-theory-and-practice-advantages-for-the-small-business-locating-in-a-vibrant-cluster}{4}.
-Feel free to add the standard literature / different sources}
+However, the identification of market segments, and moreover that of business clusters, requires significant amount of manual labor.
+Typically, one first has to collect information about companies with a location in the targeted region.
+Afterwards, for each company, their publicly available information must be analyzed to better understand their products, strategic position and market positioning.
 
-However, the identification of market segments, and moreover that of business clusters, is complicated by the fact that data on regional companies is often unavailable or difficult to analyze due to non-numerical, irrelevant, or missing features.
-\pe{This seems a harsh claim, in practice one could argue that it is available through regional connections}
-\nm{We keep the current motivation for using company descriptions and then only later mention that we can also add other features}
+This process is very labor-intensive, as businesses do not provide any specific data on the latter points, but it has to be inferred from their product portfolio and websites.
+Additionally, even simpler data like the number of employees is often unavailable, or only available inside hard to parse company websites, especially for small regional companies.
 
@@
 in the form of the popular ChatGPT \cite{chatgpt}, have led to surprisingly good results in numerous applications.
-Examples range from complex Code generation to essays to cooking recipes.
+Especially, they have proven be very efficient at extracting data and summaries from human written texts.
 
-This work demonstrates market segments and business clusters can be identified effectively by introducing an automatic clustering pipeline.
+The main contribution of this work is an automatic clustering pipeline to identify market segments and business clusters effectively from publicly available information.
 Utilizing those clusters, our system is then able to provide a strategic location, which we will demonstrate by using the German federal state Saarland as an example.
-The novelty of our approach is that we rely on language models to encode the companies' information.
+The novelty of our approach is that we rely on language models to process the companies' information.
 
@@
 The system then recommends that the novel company locate its site near an established company acting in the same market segment, which fosters business cluster development in Saarland.
-\pe{I have yet to find a backing for this approach, feel free to help me out here}
+\pe{We might want to shorten this part a little as we will explore it in all details later}
 
@@
     \item We show how our methods can be extended to handle additional features.
-    \item We demonstrate our approach's feasibility using Saarland's economy.
-    \item We provide a user-friendly graphical interface for our methods, allowing for analyzing market segments and location recommendations for establishing business clusters.
+    \item We demonstrate our approach's feasibility using Saarland's economy and provide a user-friendly graphical interface for our methods, allowing for analyzing market segments and location recommendations for establishing business clusters.
 \end{itemize}
@@
 \subsection{Identification and Impacts of Business Clusters}
+
+Clusters and their advantage have been studied in many works.
+For example \cite{regionaladv}, examined the well known technology cluster in the Silicon Valley, famous for being the home of many innovative startups even in recent years.
+
+\cite{clustertheory} provides detailed discussion of the cluster phenomenon.
+It discusses preexisting literature on clusters and reviews the two main postivies effects commonly observed in clusters, positive feedback, and productivity \& growth.
+Additionally, it provides examples for well-known clusters.
+
+Our region of choice for testing our approach has also been subject of scientific work.
+It should be noted that most of them examine it for its location on the border of France and Luxembourg or because of its mining and steel producing past.
+
+These factors are however of no interest to this work.
+For example, \cite{saarlandeco1} has focused on the agglomeration of automotive industry in Saarland and the neighboring regions, but focuses on the challenges that the country borders pose to this industry.
+
+The paper \cite{saarlandeco2} specifically compares the economic strategies for development of the regions economy and with a focus on how clusters are developed.
+Most importantly, they identify some regional clusters.
+We will revisit these when evaluating our clustering algorithm and compare on the clusters identified by our approach.
+It should be noted however that the paper was published in 2009, therefore the analysis conducted by this paper was based on the economy at least 14 years before this paper.
+
+\pe{This is on the sparse side but going deeper into the techniques would require more in depth research on what are accepted approaches. Would be good if the business people help here}
 
@@
 
-\subsection{Identifying Market Segments through Clustering}
+\subsection{Identifying related companies through Clustering}
 Figure \ref{fig:pipeline} shows a graphical representation of our general clustering pipeline, consisting of $4$ steps: $1)$ Collection of descriptions from company websites, $2)$ converting the descriptions to embeddings, $3)$ reducing the dimensionality of the embeddings, and $4)$ applying a clustering algorithm.
@@
 
-\textit{$1)$ Collect Descriptions:} Given that high-quality economic data is highly valuable, there are no freely available data sets we could rely on for our purposes, meaning we need to build our dataset from scratch.
-\pe{TODO: rephrase} The traditional approach for building such a dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in Saarland and then store each in a fixed-size vector.
+\textit{$1)$ Collect Descriptions:} The traditional approach for building such a dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in Saarland and then store each in a fixed-size vector.
 \pe{TODO: backup with accepted approach}  However, it is not straightforward to encode non-numerical attributes, like products and customer base, such that clustering algorithms can parse them without introducing an unwanted ordering of the attributes' values.
 Further, some attributes may be unavailable for some companies, meaning we would need to discard them because we require fixed-size vectors, or we would need to insert dummy values, which could lead to unwanted effects.
+
 Lastly, representing a company using a small number of publicly available attributes might be insufficient for capturing all relevant characteristics.
@@
 Yet, it is commonly known that Apple, with its minimalist design, high-end smartphones targeted toward customers looking to differentiate themselves from other people, and Samsung, with its more utilitarian smartphones targeted toward a broad customer base, are companies with fundamentally different characters.
+\pe{This is a very shallow argument to me, would propose to remove}
+
 To address these challenges to dataset construction, we propose representing companies by the description on their websites instead of numerical attributes.
-Since companies want to present themselves publicly in a way that attracts customers and investors, these descriptions contain the information needed to represent them accurately.
+The benefit of using this data is that companies usually design their website to appeal to a very targeted audience.
+Additionally, they usually include very detailed information on their products, their size and capabilities, as they want to present themselves publicly in a way that attracts customers and investors.
+Using the text directly circumvents the problem of creating a targeted aggregator for specific information.
+This makes our approach simpler to implement and a lot more scalable \& automatable for larger target regions.
 
@@
 
-\textit{$3)$ Projection into 2D Space:} Although the embeddings are of much lower dimensionality than the original text data, the number of features might still be too large relative to the size of our dataset.
+\textit{$3)$ Projection into 2D / 3D Space:} Although the embeddings are of much lower dimensionality than the original text data, the number of features might still be too large relative to the size of our dataset.
 This might invoke the curse of dimensionality, meaning that the few data points are so distant from each other in the high-dimensional space that it is impossible to derive meaningful clusters.
@@
 To avoid the course of dimensionality and to enable user-friendly visualization of our results, we will project the embeddings to 2D or 3D space using two dimensionality reduction techniques.
+
 \emph{Kernel Principal Components Analysis} (KPCA) is a dimensionality reduction technique that computes a linear transformation that projects the data in the kernel space onto the dimensions with the highest variance, such that a non-linear transformation in the original feature space is attained.
@@
 We combine $K$-Means with KPCA since it returns a set of cluster centers that can be used to classify novel data points.
-If t-SNE is used, we cluster the data using Agglomerative clustering, which initially assigns each data point to a separate cluster and then iteratively merges close clusters until all data points are in the same cluster.
+If t-SNE is used, we cluster the data using agglomerative clustering, which initially assigns each data point to a separate cluster and then iteratively merges close clusters until all data points are in the same cluster.
 The intermediate clustering that achieves the largest overall separation between data points can then be chosen as the final clustering.
-The advantage of Agglomerative clustering over $K$-Means is that it does not require a pre-specified number of clusters and can compute hierarchically structured clusters.
+The advantage of agglomerative clustering over $K$-Means is that it does not require a pre-specified number of clusters and can compute hierarchically structured clusters.
 Once the clustering algorithm converges, we receive cluster labels for each company in our dataset, corresponding to the predicted market segments.
@@
 A list of all companies in our dataset can be found in the appendix \ref{sec:appendix-companies}.
-We conducted the data collection manually since company websites are generally structured very differently, making it complicated to extract such information automatically.
-Thus, building a scraping tool was out of this project's scope.
-To test our location recommendation feature, we created company descriptions using GPT-4.
-To test the impact of providing additional features to the clustering pipeline, we also gathered the features industry, products, customer base, market positioning, and revenue for each company.
+
+For the purpose of the experimental evaluation we conducted the data collection manually.
+As our target region was very narrow this was easily feasible.
+However, in the future we might create a simple HTML scraper to scale our approach to larger regions.
+To test our location recommendation feature, we created company descriptions using GPT-4 \cite{chatgpt}.
+
+Additionally, we evaluate the impact of providing additional features to the clustering pipeline,for which also gathered the features industry, products, customer base, market positioning, and revenue for each company.
 
@@
 When using additional features, we compute embeddings for each feature and combine them with the description embedding in the same way the individual sentence embeddings were combined.
+\pe{Links and references plz}
 Afterward, the embeddings are projected onto 2D or 3D space using KPCA or t-SNE.
@@
 For Agglomerative clustering, we chose the final number of clusters through visual inspection of the dendrogram returned by the algorithm.
-
-Given that we have no ground truth labels, we will evaluate the results of our clustering process based on our investigation of Saarland's economy in \MakeUppercase{\romannumeral 2}.
 
@@
 
-In this section, we will investigate the results of the best-performing configuration of our clustering and location recommendation system.
+In the following, we will investigate the results of the best-performing configuration of our clustering and location recommendation system.
 These results were obtained using the following configuration: the description embeddings were computed using max pooling, the embeddings were projected into 2D space using t-SNE, and the clustering was achieved using Agglomerative clustering.
@@
 	\item \textit{Cluster 1 (light green)}: The steel industry companies MAT Foundries, ThyssenKrupp, and Meiser are part of this cluster.
-Further cluster members are companies like Hörmann and HYDAC, which also offer products manufactured from steel.
+Further, cluster members are companies like Hörmann and HYDAC, which also offer products manufactured from steel.
 Accordingly, we assign this cluster to the steel products market segment.
@@
 
+\subsection{Comparison to clusters identified by other work}
+
+As mentioned \cite{saarlandeco2} also identified clusters for the region of Saarland. Specifically, they identified the following clusters by industry (\cite{saarlandeco2}, Table 4, p. 1226)
+
+\begin{itemize}
+	\item Coal and mining industries
+	\item Metal industry
+	\item Automobile industry
+	\item Energy sector
+	\item Information and communication technology
+	\item Biotechnology and nanotechnology
+\end{itemize}
+
+Comparing these results with the output of our pipeline we can see that
+
+\begin{itemize}
+	\item Coal and mining industries: With the decline of coal mining in recent years, there are no more coal mines in Saarland. As the last one closed in 2012, this cluster does not exist anymore. 
+	\item Metal industry is covered by cluster 1 (light green) and cluster 6 (yellow).
+	\item Automobile industry is covered by cluster 0 (red).
+	\item Energy sector is covered by cluster 5 (light blue).
+	\item Information and communication technology is covered by cluster 3 (beige).
+	\item Biotechnology and nanotechnology is covered by cluster 2 (dark blue).
+\end{itemize}
+
+One can see that the results of our pipeline do agree with the general sectors identified by \cite{saarlandeco2}.
+However, our approach did lead to more fine-grained separation.
+Additionally, we for example include construction companies, leading to additional companies.
+However, these sectors are usually not contributing significantly to the region's economy, which is most probably why they are not mentioned in \cite{saarlandeco2}.
+In summary, the output of our pipeline matches very well with traditionally identified clusters.
+
 \subsection{Location Recommendation}
@@
 \section{Conclusion}
-The goal of this project was to collect data on companies in Saarland and apply clustering algorithms such that the results can be used to identify market segments and to give location recommendations for novel companies such that business clusters are fostered.
+The goal of this project was to collect data on companies in Saarland and apply clustering algorithms such that the results can be used to identify regional clusters and give location recommendations for novel companies such that business clusters are fostered.
 
@@
 
-A qualitative evaluation of our methods has shown that they can reliably cluster similar companies, which allowed us to infer market segments in Saarland.
+A qualitative evaluation of our methods has shown that they can reliably cluster similar companies, which allowed us to infer major industry segments in Saarland.
 Further, our location recommendation system demonstrated its capability of identifying similar companies, given the description of a new company, independently of the total number of similar companies in the dataset.
@@
 Collecting data from more companies in Saarland could improve the clustering results, although the number of (large) companies in Saarland is limited.
-Thus, applying our methods to larger economies would be highly interesting.
+Thus, applying our methods to larger economies would be of great interest.
+This would also allow more comparisons to traditionally identified clusters.
 Further, fine-tuning our language models using text data from the business sector might lead to more expressive embeddings.
+To achieve this, efficiently, an automated aggregation system could be developed.
+As we utilize publicly available websites, this would be easily possible without utilizing 3rd party services.
 To this end, we have demonstrated the feasibility and potential of applying language models to economic analysis.

### 2023-07-02 report/report.tex
report nearly finished

@@
 \begin{abstract}
-With this guide, we give an example of what a write-up for the mini-project report could look like. We provide a \LaTeX template that you 
-can use in your own write-up, if you want to. We explain some important points regarding specific types of sections that need to be included in the report.
+Identifying market segments is crucial for effective marketing strategies and well-informed business decisions.
+Further, combining companies' geographical locations with their market segments allows for detecting business clusters.
+However, acquiring and processing the data needed to gain such insights into regional economies is labor-intensive.
+
+We propose to circumvent these challenges by leveraging state-of-the-art language models to transform companies' highly informative public text data into machine-readable data points, and then applying clustering to identify market segments and make location recommendations for novel companies to support business cluster development.
+
+A qualitative evaluation of our methods being applied to data from the German municipality Saarland demonstrates that our methods can accurately cluster similar companies and assign novel companies to clusters.
 \end{abstract}
@@
 
-Deciding on location of a business is a vital strategic decision.
-Finding the right location can have a number of benefits: First, it is crucial to most businesses to be located close to its customers and suppliers, for more effective marketing or reduced transportation costs, secondly, being located in an active regional cluster can significantly benefit a business development \cite{clustersandcomp,gems-model, regionaladv, clustertheory}.
+Deciding on the location of a business is a vital strategic decision.
+Finding the right location can have several benefits: First, it is crucial to most businesses to be located close to their customers and suppliers for more effective marketing or reduced transportation costs.
+Secondly, being located in an active regional cluster can significantly benefit a business development \cite{clustersandcomp,gems-model, regionaladv, clustertheory}.
 
-Clusters are local concentrations of businesses, manufacturers, suppliers, and institutions from the same field.
+Business clusters are local concentrations of businesses, manufacturers, suppliers, and institutions from the same field.
 Identifying regional clusters is done by combining geographical data of companies' locations with information on their corresponding market segments.
@@
 
-However, the identification of market segments, and moreover that of business clusters, requires significant amount of manual labor.
-Typically, one first has to collect information about companies with a location in the targeted region.
-Afterwards, for each company, their publicly available information must be analyzed to better understand their products, strategic position and market positioning.
+However, the identification of market segments, and moreover that of business clusters, requires a significant amount of manual labor.
+Typically, one must first collect information about companies with a location in the targeted region.
+Afterward, for each company, their publicly available information must be analyzed to understand their products, strategic position, and market positioning.
 
-This process is very labor-intensive, as businesses do not provide any specific data on the latter points, but it has to be inferred from their product portfolio and websites.
-Additionally, even simpler data like the number of employees is often unavailable, or only available inside hard to parse company websites, especially for small regional companies.
+This process is very labor-intensive, as businesses do not provide specific data on the latter points, but it must be inferred from their product portfolio and websites.
+Additionally, even simpler data like the number of employees is often unavailable or only available inside hard-to-parse company websites, especially for small regional companies.
 
-At the same time, recent advances in natural language processing (NLP), e.g.
-in the form of the popular ChatGPT \cite{chatgpt}, have led to surprisingly good results in numerous applications.
-Especially, they have proven be very efficient at extracting data and summaries from human written texts.
+At the same time, recent advances in natural language processing (NLP), e.g., the popular ChatGPT \cite{chatgpt}, have yielded surprisingly good results in numerous applications.
+Especially they have proven to be very efficient at extracting data and summaries from human written texts.
 
-The main contribution of this work is an automatic clustering pipeline to identify market segments and business clusters effectively from publicly available information.
-Utilizing those clusters, our system is then able to provide a strategic location, which we will demonstrate by using the German federal state Saarland as an example.
+The main contribution of this work is an automatic clustering pipeline to effectively identify market segments and business clusters from publicly available information.
+Utilizing those clusters, our system can provide a strategic location, which we will demonstrate by using the German federal state Saarland as an example.
 The novelty of our approach is that we rely on language models to process the companies' information.
@@
 The system then recommends that the novel company locate its site near an established company acting in the same market segment, which fosters business cluster development in Saarland.
-\pe{We might want to shorten this part a little as we will explore it in all details later}
 
@@
     \item We show how our methods can be extended to handle additional features.
-    \item We demonstrate our approach's feasibility using Saarland's economy and provide a user-friendly graphical interface for our methods, allowing for analyzing market segments and location recommendations for establishing business clusters.
+    \item We demonstrate our approach's feasibility using Saarland's economy and provide a user-friendly graphical interface for our methods.
 \end{itemize}
 
-\nm{Adjust this when related work is finally done}
-The remaining parts of this paper are structured as follows: In section \MakeUppercase{\romannumeral 2}, we first examine the economy in Saarland and the theory behind business clusters.
-Then we look upon existing work on using clustering for economic analysis, and lastly, we investigate work on language models for extracting information from text data.
+The remaining parts of this paper are structured as follows: In section \MakeUppercase{\romannumeral 2}, we examine the concept of business clusters in general and with respect to Saarland.
+Afterward, we investigate work on language models for extracting information from text data.
 Next, in section \MakeUppercase{\romannumeral 3}, we present our methods in more detail, discussing each step of our clustering pipeline and location recommendation system, and in \MakeUppercase{\romannumeral 4}, we present how we apply our methods to the economy of Saarland.
@@
 \section{Related Work}
-\color{red}
-\begin{itemize}
-    \item General stuff about Saarland's economy and its market segments?
-    \item How market segments are normally identified?
-    \item Theory behind business clusters and maybe related work?
-    \item Related Work on clustering in economy?
-    \item Mention that we collected traditional economic data?
-\end{itemize}
-\color{black}
-\nm{Related work for business stuff is still missing!}
+In this section, we will examine previous work on business clusters, and recent advances in natural language processing.
 
@@
 
-Clusters and their advantage have been studied in many works.
-For example \cite{regionaladv}, examined the well known technology cluster in the Silicon Valley, famous for being the home of many innovative startups even in recent years.
+Business clusters and their advantages have been studied in many works.
+For example, \cite{regionaladv} examined the well known technology cluster in the Silicon Valley, famous for being the home of many innovative startups even in recent years.
 
@@
 
-Our region of choice for testing our approach has also been subject of scientific work.
+Our region of choice for testing our approach, Saarland, has also been subject of scientific work.
 It should be noted that most of them examine it for its location on the border of France and Luxembourg or because of its mining and steel producing past.
@@
 It should be noted however that the paper was published in 2009, therefore the analysis conducted by this paper was based on the economy at least 14 years before this paper.
-
-\pe{This is on the sparse side but going deeper into the techniques would require more in depth research on what are accepted approaches. Would be good if the business people help here}
 
@@
 GloVe, developed by Pennington et al.~\cite{pennington2014glove}, improved upon Word2Vec by effectively encoding both local context information and global statistical information into the embeddings, thereby offering more detailed semantic capture.
-More recently, transformer-based models like BERT, developed by Devlin et al.~\cite{devlin2018bert}, and GPT models by OpenAI~\cite{radford2018improving} have leveraged context-dependent word embeddings by encoding the words themselves and the context in which they are used.
+More recently, transformer-based models like BERT, developed by Devlin et al.~\cite{devlin2018bert}, and GPT models by OpenAI~\cite{radford2018improving, chatgpt} have leveraged context-dependent word embeddings by encoding the words themselves and the context in which they are used.
 So-called sentence transformers extended these approaches by computing embeddings for entire sentences to capture more contextual information than individual word embeddings.
@@
 Starting with pre-trained BERT-networks, Sentence-BERT is fine-tuned using text classification or cosine-similarity tasks, yielding a model capable of generating high-quality sentence embeddings using only a fraction of the original BERT model's computational effort.
-
-\pe{Maybe we should bring out the connection to our approach here a little bit more}
 
@@
 
-\subsection{Identifying related companies through Clustering}
+\subsection{Identifying Related Companies through Clustering}
 Figure \ref{fig:pipeline} shows a graphical representation of our general clustering pipeline, consisting of $4$ steps: $1)$ Collection of descriptions from company websites, $2)$ converting the descriptions to embeddings, $3)$ reducing the dimensionality of the embeddings, and $4)$ applying a clustering algorithm.
@@
 \textit{$1)$ Collect Descriptions:} The traditional approach for building such a dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in Saarland and then store each in a fixed-size vector.
-\pe{TODO: backup with accepted approach}  However, it is not straightforward to encode non-numerical attributes, like products and customer base, such that clustering algorithms can parse them without introducing an unwanted ordering of the attributes' values.
-Further, some attributes may be unavailable for some companies, meaning we would need to discard them because we require fixed-size vectors, or we would need to insert dummy values, which could lead to unwanted effects.
-
-Lastly, representing a company using a small number of publicly available attributes might be insufficient for capturing all relevant characteristics.
-For instance, consider the smartphone manufacturers Apple and Samsung: Both companies build smartphones, have over $100.000$ employees, have revenues of over $200$ billion dollars, and have production and sales sites worldwide.
-Given these attributes, one could argue that Apple and Samsung are very similar companies.
-Yet, it is commonly known that Apple, with its minimalist design, high-end smartphones targeted toward customers looking to differentiate themselves from other people, and Samsung, with its more utilitarian smartphones targeted toward a broad customer base, are companies with fundamentally different characters.
-\pe{This is a very shallow argument to me, would propose to remove}
-
+However, it is generally unclear which are the best attributes for representing companies.
+Further, it is not straightforward to encode non-numerical attributes, like products and customer base, so clustering algorithms can parse them without introducing an unwanted ordering of the attributes' values.
+Lastly, some attributes may be unavailable for some companies, meaning we would need to discard them because we require fixed-size vectors, or we would need to insert dummy values, which could lead to unwanted effects.
 To address these challenges to dataset construction, we propose representing companies by the description on their websites instead of numerical attributes.
-The benefit of using this data is that companies usually design their website to appeal to a very targeted audience.
-Additionally, they usually include very detailed information on their products, their size and capabilities, as they want to present themselves publicly in a way that attracts customers and investors.
+The benefit of using this data is that, since companies design their website to attract customers and investors, they include detailed information, such as their products, market positioning, and customer base.
 Using the text directly circumvents the problem of creating a targeted aggregator for specific information.
@@
 Given the description of the novel company, we compute an embedding using a sentence transformer and apply KPCA or t-SNE to get a low-dimensional feature vector.
-We then assign the feature vector to a cluster according to the $K$-Means or Agglomerative clustering algorithm and then compute which company within the cluster is most similar to the novel company.
-Note that when using KPCA and $K$-Means, we can assign the novel data points to a pre-computed clustering, and when using t-SNE and Agglomerative clustering, we compute a new clustering.
+We then assign the feature vector to a cluster according to the $K$-Means or agglomerative clustering algorithm and then compute which company within the cluster is most similar to the novel company.
+Note that when using KPCA and $K$-Means, we can assign the novel data points to a pre-computed clustering, and when using t-SNE and agglomerative clustering, we compute a new clustering.
 Thus, the second approach accounts for the possibility that introducing a novel company might change existing market segments, whereas the first approach does not.
@@
 
-Additionally, we evaluate the impact of providing additional features to the clustering pipeline,for which also gathered the features industry, products, customer base, market positioning, and revenue for each company.
+Additionally, we evaluate the impact of providing additional features to the clustering pipeline, for which also gathered the features industry, products, customer base, market positioning, and revenue of each company.
 
-We utilize the popular pre-trained sentence transformer "all-MiniLM-L6-v2" from the HuggingFace hub to compute sentence embeddings for each description.
+We utilize the popular pre-trained sentence transformer model "all-MiniLM-L6-v2" from the HuggingFace hub~\cite{sentence-transformer-model} to compute sentence embeddings for each description.
 An embedding for the full description is then attained using our concatenation, average, or max pooling approach.
 When using additional features, we compute embeddings for each feature and combine them with the description embedding in the same way the individual sentence embeddings were combined.
-\pe{Links and references plz}
 Afterward, the embeddings are projected onto 2D or 3D space using KPCA or t-SNE.
@@
 To choose the number of clusters for $K$-Means, we started with $K = \sqrt{N}$, where $N$ is the size of the dataset, and then increased $K$ until the clustering aligned with our expectations.
-For Agglomerative clustering, we chose the final number of clusters through visual inspection of the dendrogram returned by the algorithm.
+For agglomerative clustering, we chose the final number of clusters through visual inspection of the dendrogram returned by the algorithm.
 
@@
 In the following, we will investigate the results of the best-performing configuration of our clustering and location recommendation system.
-These results were obtained using the following configuration: the description embeddings were computed using max pooling, the embeddings were projected into 2D space using t-SNE, and the clustering was achieved using Agglomerative clustering.
+These results were obtained using the following configuration: the description embeddings were computed using max pooling, the embeddings were projected into 2D space using t-SNE, and the clustering was achieved using agglomerative clustering.
 We also used the companies' industry as an additional feature.
@@
 
-\subsection{Comparison to clusters identified by other work}
+\subsection{Comparison to Clusters Identified by Other Work}
 
-As mentioned \cite{saarlandeco2} also identified clusters for the region of Saarland. Specifically, they identified the following clusters by industry (\cite{saarlandeco2}, Table 4, p. 1226)
-
-\begin{itemize}
-	\item Coal and mining industries
-	\item Metal industry
-	\item Automobile industry
-	\item Energy sector
-	\item Information and communication technology
-	\item Biotechnology and nanotechnology
-\end{itemize}
-
-Comparing these results with the output of our pipeline we can see that
+As mentioned \cite{saarlandeco2} also identified clusters for the region of Saarland. We compare their results (\cite{saarlandeco2}, Table 4, p. 1226) with the output of our pipeline:
 
@@
 	\item Coal and mining industries: With the decline of coal mining in recent years, there are no more coal mines in Saarland. As the last one closed in 2012, this cluster does not exist anymore. 
-	\item Metal industry is covered by cluster 1 (light green) and cluster 6 (yellow).
-	\item Automobile industry is covered by cluster 0 (red).
-	\item Energy sector is covered by cluster 5 (light blue).
-	\item Information and communication technology is covered by cluster 3 (beige).
-	\item Biotechnology and nanotechnology is covered by cluster 2 (dark blue).
+	\item Metal industry: Covered by cluster 1 (light green) and cluster 6 (yellow).
+	\item Automobile industry: Covered by cluster 0 (red).
+	\item Energy sector: Covered by cluster 5 (light blue).
+	\item Information and communication technology: Covered by cluster 3 (beige).
+	\item Biotechnology and nanotechnology: Covered by cluster 2 (dark blue).
 \end{itemize}
@@
 However, our approach did lead to more fine-grained separation.
-Additionally, we for example include construction companies, leading to additional companies.
+Additionally, we identified sectors not covered in their work, such as cluster 7 which represents the construction work market segment.
 However, these sectors are usually not contributing significantly to the region's economy, which is most probably why they are not mentioned in \cite{saarlandeco2}.
@@
 To achieve this, efficiently, an automated aggregation system could be developed.
-As we utilize publicly available websites, this would be easily possible without utilizing 3rd party services.
+As we utilize publicly available websites, this would be easily possible without relying on 3rd party services.
 To this end, we have demonstrated the feasibility and potential of applying language models to economic analysis.

### 2023-07-02 paper/paper.tex
test doc
first paper draft

@@
 
-\author{gg}
-\title{test}
+\usepackage{todonotes}
+\newcommand{\pe}[1]{\todo[inline, backgroundcolor=green]{PE: #1}}
+\definecolor{eyecancerpink}{rgb}{1.0, 0.0, 1.0}
+\newcommand{\nm}[1]{\todo[inline, backgroundcolor=eyecancerpink]{NM: #1}}
+
+\usepackage{cite}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\usepackage{tikz}
+\usepackage{hyperref}
+\usepackage{float}
+\usepackage{multicol}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{enumitem}
+
+\author{Nicola J. Müller, Robert Leist, Paul Eichler, \\and Tobias Recktenwald}
+\title{Towards Language Model-based Identification of Market Segments and Fostering of Business Clusters}
+
 \begin{document}
     \maketitle
-    gg
+   \begin{abstract}
+   	Identifying market segments is crucial for effective marketing strategies and well-informed business decisions.
+Further, combining companies' geographical locations with their market segments allows for detecting business clusters.
+However, acquiring and processing the data needed to gain such insights into regional economies is labor-intensive.
+
+   	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform companies' highly informative public text data into low-dimensional vectors and then applying clustering to identify market segments and make location recommendations for novel companies to support business cluster development.
+
+   	A qualitative evaluation of our methods being applied to data from the German municipality Saarland demonstrates that our methods can accurately cluster similar companies and assign novel companies to existing clusters.
+   \end{abstract}
+
+   \section{Introduction}
+   Deciding on the location of a business is a vital strategic decision: First, most businesses must be located close to their customers and suppliers for more effective marketing or reduced transportation costs.
+Secondly, being located in an active regional cluster can significantly benefit business growth \cite{clustersandcomp,gems-model, regionaladv, clustertheory}.
+
+   Business clusters are local concentrations of companies, manufacturers, suppliers, and institutions from the same field.
+Identifying clusters combines geographical data of companies' locations with information on their corresponding market segments.
+This proximity of related companies enables efficient cooperation and knowledge transfer, which has been shown to significantly increase the productivity of all companies within the cluster \cite{clustersandcomp,gems-model, regionaladv, clustertheory}.
+Thus, establishing or further developing business clusters is of high interest to companies and local governments.
+Therefore, significant effort is spent identifying clusters and market segments in regional economies.
+
+   However, identifying market segments and business clusters requires a significant amount of manual labor.
+Typically, one must first collect information about companies in the targeted region.
+Afterward, for each company, their publicly available information must be analyzed to understand their products, strategic position, market positioning, and further characteristics.
+   This process is labor-intensive, as businesses do not provide specific data on the latter points, but it must be inferred from their product portfolio and websites.
+Additionally, even basic data like the number of employees is often unavailable or difficult to collect automatically, especially for small regional companies.
+   At the same time, recent advances in natural language processing (NLP), e.g., the popular ChatGPT \cite{chatgpt}, have yielded surprisingly good results in numerous applications.
+Especially they have proven to be very efficient at extracting data and summaries from human written texts.
+
+   The main contribution of this work is an automatic clustering pipeline to identify market segments and business clusters from publicly available information.
+Additionally, our system can utilize the found clusters to provide strategic location recommendations, which we will demonstrate using the German federal state Saarland as an example.
+The novelty of our approach is that we rely on language models to process the companies' information, allowing us to circumvent many of the challenges attributed to gathering economic data.
+   Our clustering pipeline can be divided into $4$ distinct steps: $1)$ gathering descriptions from the websites of companies in the region of interest, $2)$ computing embeddings of the text data, $3)$ reducing the embeddings' dimensionality, and $4)$ applying clustering algorithms.
+   Our location recommendation system builds upon the clustering pipeline by computing an embedding of a novel company's description, assigning it to a cluster, and then identifying the most similar companies within the cluster.
+The system then recommends that the novel company locate its site near an established company acting in the same market segment, which fosters business cluster development.
+   We provide a graphical user-interface for our methods, which visualizes the clustering of companies and their locations in an interactive manner, allowing end-users to analyze the various predicted market segments.
+Further, the interface supports making location recommendations for new company sites using text inputs.
+
+   In summary, our main contributions are:
+   \begin{itemize}[noitemsep]
+   	\item Circumventing the challenges of economic data collection by relying on public text data.
+   	\item Leveraging state-of-the-art language models to apply clustering algorithms to text data.
+   	\item Showing how our methods can be extended to handle additional features.
+   	\item Demonstrating our approach's feasibility using Saarland's economy and providing a user-friendly graphical interface.
+   \end{itemize}
+
+   \section{Related Work}
+   This section will examine previous work on business clusters and recent advances in natural language processing.
+
+   Business clusters and their advantages have been studied in many works.
+For example, \cite{regionaladv} examined the well-known technology cluster in Silicon Valley, famous for being the home of many innovative start-ups.
+   \cite{clustertheory} provides a detailed discussion of the cluster phenomenon.
+It discusses preexisting literature on clusters and reviews the main positive effects commonly observed in clusters, positive feedback and productivity \& growth.
+Additionally, it provides examples of well-known clusters.
+
+   The region of choice for testing our approach, Saarland, has also been the subject of scientific work.
+It should be noted that Saarland is mostly investigated for its location on the border of France and Luxembourg or because of its mining and steel-producing past.
+   These factors are, however, of no interest to this work.
+For example, \cite{saarlandeco1} has focused on the agglomeration of the automotive industry in Saarland and the neighboring regions but focuses on the challenges that the country borders pose to this industry.
+   The paper \cite{saarlandeco2} specifically compares the economic strategies for developing the region's economy with a focus on how clusters are developed.
+Most importantly, they identify some regional business clusters.
+We will revisit these when evaluating our clustering algorithm and compare the clusters and market segments identified by our approach.
+It should be noted, however, that the paper was published in 2009, meaning their analysis could be outdated to some extent.
+
+   In natural language processing (NLP), translating text data to machine-processable representations is a fundamental challenge for numerous tasks, such as sentiment analysis~\cite{rezaeinia2019sentiment}, and information retrieval~\cite{ye2016word}, due to the complexity and variability of natural language.
+A popular approach for representing text data is the utilization of so-called \emph{embeddings}: vectorized representations of text with the property that vectors of text data with similar semantic and syntactic properties will have a smaller distance to vectors of text data with different properties, making them ideal for applying clustering to our sparse dataset of high-dimensional company descriptions.
+   Mikolov et al~\cite{mikolov2013efficient}.
+popularized learning word embeddings from raw text data in $2013$ by introducing their Word2Vec model.
+More recently, transformer-based models like BERT, developed by Devlin et al.~\cite{devlin2018bert}, and GPT models by OpenAI~\cite{radford2018improving, chatgpt} have leveraged context-dependent word embeddings by encoding the words themselves and the context in which they are used.
+So-called sentence transformers extended these approaches by computing embeddings for entire sentences to capture more contextual information than individual word embeddings.
+Reimers and Gurevych~\cite{reimers2019sentence} introduced the Sentence-BERT model, capable of generating high-quality sentence embeddings using only a fraction of the original BERT model's computational effort.
+
+   \section{Procedure}
+   \input{figure}
+   Our goal is to collect data points on companies in the region of interest and cluster them to identify market segments and recommend locations for companies who plan to establish new sites, such that it supports the development of business clusters.
+We will present our clustering pipeline and then examine how we can use the results to provide location recommendations.
+
+   Figure \ref{fig:pipeline} shows a graphical representation of our general clustering pipeline, consisting of $4$ steps: $1)$ Collection of company descriptions, $2)$ computing embeddings, $3)$ reducing the embeddings' dimensionality, and $4)$ applying a clustering algorithm.
+In the following, we will examine each of these steps in detail.
+
+   \textit{$1)$ Collect Descriptions:} The traditional approach for building an economic dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in the region of interest and then store each in a fixed-size vector.
+However, it is generally unclear which are the best attributes for representing companies.
+Further, encoding non-numerical attributes, like products and customer base, so that clustering algorithms can parse them is not straightforward.
+   Lastly, some attributes may be unavailable for some companies, meaning we would need to discard them or we would need to insert dummy values, which could lead to unwanted effects.
+   To address these challenges to dataset construction, we propose representing companies by the description on their websites instead of numerical attributes.
+The benefit of using this data is that, since companies design their website to attract customers and investors, they include the most relevant information.
+Hence, we circumvent the problem of creating a targeted aggregator for specific information, making our approach simpler to implement and significantly more scalable \& automatable for larger target regions.
+
+   \textit{$2)$ Compute Embeddings:} To achieve the fixed-size inputs, we map each company description to an embedding that describes the data in a low-dimensional space.
+We rely on a sentence transformer model to compute embeddings for each sentence in a company's description.
+We then attain a single embedding for each description by taking the maximum over each feature dimension, which we denote as max pooling.
+
+   \textit{$3)$ Projection into 2D Space:} The embeddings' number of features might be too large relative to the size of the dataset, potentially invoking the curse of dimensionality~\cite{koppen2000curse}.
+Further, clustering data in high-dimensional space prevents visualizing the results.
+Hence, we project the embeddings to 2D space.
+To do so, we apply the \emph{t-distributed stochastic neighbor embedding} (t-SNE) technique, which computes a probability distribution representing the pairwise similarity between data points in the feature space and then projects the data points to a low-dimensional space according to a second probability distribution that minimizes the Kullback-Leibler divergence to the first distribution.
+This enables t-SNE to accurately preserve local structures in the data, making it suitable for identifying clusters.
+
+   \textit{$4)$ Clustering:} We cluster the data using agglomerative clustering, which initially assigns each data point to a separate cluster and then iteratively merges close clusters until all data points are in the same cluster.
+The intermediate clustering that achieves the largest separation between data points is chosen as the final clustering.
+   Once the algorithm converges, we receive cluster labels for each company in our dataset, allowing us to infer market segments.
+
+   Although our general pipeline represents companies using their descriptions, we emphasize that our approach can also utilize additional features.
+For instance, we can include the companies' products in the encoding by computing the corresponding sentence embeddings and merging them with the description embedding using max pooling.
+
+   Figure \ref{fig:clustering-analysis} depicts the clustering analysis tab of our user-interface.
+On the left side, users can define how the description embeddings are computed, the technique and target dimensionality of the dimensionality reduction, and the number of clusters.
+Additionally, users can specify a subset of additional features, including industry, products, customer base, market positioning, and revenue, which will be combined with the descriptions.
+After clicking "Compute clustering", the clustered data points are shown on the right side.
+Further, users can see the location and clustering assignment of all companies in the given dataset on a map.
+When hovering the mouse over a company's data point, additional information about the company is shown.
+
+   \begin{figure}[H]
+   	\centering
+   	\begin{subfigure}[b]{0.48\textwidth}
+   		\centering
+   		\includegraphics[width=\textwidth]{figures/clustering_analysis.png}
+   		\caption{Clustering analysis page of our user-interface.}
+   		\label{fig:clustering-analysis}
+   	\end{subfigure}
+   	\hfil
+   	\begin{subfigure}[b]{0.48\textwidth}
+   		\centering
+   		\includegraphics[width=\textwidth]{figures/location_recommendation_output.png}
+   		\caption{Output of the location recommendation feature of our user-interface.}
+   		\label{fig:location-recommendation-output}
+   	\end{subfigure}
+   \end{figure}
+
+   %\subsection{Fostering Business Clusters through Location Recommendations}
+   To give location recommendations for companies seeking to establish new sites in the region of interest, we utilize parts of our clustering pipeline.
+Given the novel company's description, we compute an embedding and apply dimensionality reduction.
+We then assign the data point to a cluster and compute which company within the cluster is most similar to the novel company.
+   Given the novel company's cluster label, the location recommendation is to establish a new site nearby the most similar company within the cluster.
+Thus, our location recommendations support the geographical concentration of companies acting in the same market segment, which helps to foster business clusters.
+
+   Our user-interface offers a dedicated tab for location recommendations.
+Users can provide their company's name and description in text boxes.
+Additionally, they can specify their company's industry, products, customer base, market position, and revenue.
+After clicking "Submit", users are shown the output depicted in figure \ref{fig:location-recommendation-output}.
+The table at the top shows the names and features of the companies in the cluster to which the user's company was assigned.
+The scatter plot at the bottom left shows the clustered data points, where the point of the user's company is highlighted.
+Lastly, the map at the bottom right displays the location of the novel company's cluster members and the distances between them.
+The user can also overlay a heatmap that shows the similarity between his company and all other companies in the dataset.
+
+   \section{Results}
+   To build a dataset of company descriptions, we extracted the descriptions of $50$ of the largest companies in Saarland, which are listed in the appendix \ref{sec:appendix-companies}.
+   For the experimental evaluation, we conducted the data collection manually.
+However, in the future, we aim to create an HTML scraper to scale our approach to larger regions.
+To test our location recommendation feature, we created company descriptions using GPT-4 \cite{chatgpt}.
+   Additionally, we evaluate the impact of providing additional features to the clustering pipeline, for which we also gathered the features industry, products, customer base, market positioning, and revenue of each company.
+   We utilize the popular pre-trained sentence transformer model "all-MiniLM-L6-v2"~\cite{sentence-transformer-model} to compute sentence embeddings for each description.
+
+   \begin{figure}[H]
+   	\centering
+   	\includegraphics[width=0.5\textwidth]{figures/clustering_results.png}
+   	\caption{Clustering of company descriptions using t-SNE and Agglomerative clustering. The company descriptions and industries were used as features.}
+   	\label{fig:t-sne-agglomerative}
+   \end{figure}
+
+   We will now investigate the results of our clustering and location recommendation system.
+Besides the company descriptions, we used the companies' industry as an additional feature since this yielded the most concise clustering.
+Figure \ref{fig:t-sne-agglomerative} displays the resulting clustered data points.
+   To evaluate  the clustering of our pipeline, we will compare the found clusters to those identified in \cite{saarlandeco2} (Table 4, p. 1226):
+   \textit{Coal and mining industries}: With the decline of coal mining in recent years, there are no more coal mines in Saarland. Accordingly, no such companies are present in our dataset.    
+   \textit{Metal industry}: Covered by cluster 1 (light green) and cluster 6 (yellow), which contain steel producers like SaarStahl and Dillinger and companies offering steel products like Hörmann, a producer of various types of doors.
+   \textit{Automobile industry}: Saarland's large automobile market segment is covered by cluster 0 (red), including companies like Ford, ZF, and Michelin.    
+   \textit{Energy}: Cluster 5 (light blue) comprises the energy provider energis and the energy service providers Iqony Energies and Greencells, representing the energy market segment.    
+   \textit{Information and communication technology}: The IT products and IT consulting market segment, to which companies like SAP, ORBIS, and eurodata belong, is covered by cluster 3 (beige).    
+   \textit{Biotechnology and nanotechnology}: Covered by cluster 2 (dark blue), with members such as Fresenius, which produces dialysis machines, and USRAPHAM, which manufactures medicine.        
+   One can see that the results of our pipeline agree with the general sectors identified by \cite{saarlandeco2}.
+However, our approach did lead to more fine-grained separation.
+Additionally, we identified sectors not covered in their work, such as cluster 7 (orange), which represents the construction work market segment, and cluster 10 (pink), which represents the food production market segment.
+
+   To test our location recommendation system, we generated descriptions for three fictional German companies with vastly different characteristics:
+   \textit{FluxAI}: A young artificial intelligence start-up with ambitious goals of revolutionizing healthcare, finance, energy, and transportation.    
+   \textit{ABC Auto}: A well-established automotive manufacturer offering a wide range of cars focusing on sustainability.    
+   \textit{PanzerTech}: A weapons manufacturer with a wide spectrum of products, from armored vehicles to cybersecurity solutions.       
+   For FluxAI, our system recommends placing the new site close to CISPA, which is sensible since CISPA is a world leader in information security research, including artificial intelligence, and thus knowledge transfer between both companies could be highly beneficial.
+   For ABC Auto, the location recommendation is to establish a new site close to VOIT, which specializes in manufacturing car components with a focus on hybrid and electric cars.
+Thus, placing ABC Auto near VOIT would allow ABC Auto to source parts for its hybrid and electric cars from a company nearby, leading to a more robust supply chain.
+   Lastly, our system recommends placing PanzerTech's new site close to Diehl Defence, corresponding to the only weapons manufacturer in our dataset.
+Hence, this shows that our system does not need many samples from each market segment to give reasonable location recommendations.
+   We conclude that our location recommendation system can reliably identify companies in our dataset with similar characteristics to companies seeking to establish sites in Saarland and thus can be used to foster the development of business clusters.
+
+   \section{Conclusion}
+   In this work, we demonstrated how language models and clustering algorithms could be combined to identify market segments and give location recommendations for novel companies such that business clusters are fostered.
+
+   We represented companies by their public descriptions, which allowed us to leverage state-of-the-art language models to transform the highly informative text data into embeddings.
+Further, our methods enabled straightforwardly including other company attributes.
+Given the embeddings, we applied a clustering algorithm to infer potential market segments.
+   To make location recommendations, we passed the descriptions and features of novel companies to our clustering pipeline and recommended establishing new sites next to the most similar companies in our dataset.
+
+   A qualitative evaluation of our methods has shown that they can reliably cluster similar companies, which allowed us to infer market segments in Saarland.
+Further, our location recommendation system demonstrated its capability of identifying similar companies, given the description of a new company.
+
+   To allow end-users to leverage our methods, we implemented a user-friendly interface with many functionalities, such as visualizing the clustered data points, showing the location of companies, and giving detailed and interpretable location recommendations.
+
+   A promising opportunity for future work would be fine-tuning our language models using text data from the business sector since it might lead to more expressive embeddings.
+To achieve this efficiently, an automated aggregation system could be developed.
+As we rely on public websites, such a system could be easily implemented without relying on 3rd party services.
+
+   To this end, we have demonstrated the feasibility and potential of applying language models to economic analysis.
+
+    \bibliographystyle{IEEEtran}
+	\bibliography{bibliography}
+
+	\newpage
+	\section{Appendix}
+
+	\subsection{Link to Code}
+	\url{https://github.com/NicolaMueller42/data_science_project}
+
+	\subsection{Companies in our Dataset}
+	\label{sec:appendix-companies}
+
+	We list the $50$ Saarland companies in our dataset:
+	\begin{multicols}{4} \begin{itemize}
+	   		\item ZF
+	   		\item Saarstahl
+	   		\item Dillinger
+	   		\item Bosch
+	   		\item Festo
+	   		\item Ford
+	   		\item Schaeffler
+	   		\item Fresenius
+	   		\item Wagner
+	   		\item \footnotesize Villery\&Boch \normalsize
+	   		\item Michelin
+	   		\item \scriptsize ThyssenKrupp \normalsize
+	   		\item Hager
+	   		\item Purem
+	   		\item \small SaarGummi \normalsize
+	   		\item VOIT
+	   		\item Meiser
+	   		\item SAP
+	   		\item Nemak
+	   		\item Peter Gross Bau
+	   		\item OBG Group
+	   		\item \scriptsize URSAPHARM \normalsize
+	   		\item Hörmann
+	   		\item Kunzler
+	   		\item Diehl \\Defence
+	   		\item HYDAC
+	   		\item Backes AG
+	   		\item Karlsberg
+	   		\item Globus
+	   		\item Caritas
+	   		\item Uni Saar
+	   		\item Welocalize
+	   		\item Möbel Martin
+	   		\item IKK Südwest
+	   		\item Dr. Theiss
+	   		\item Unimed
+	   		\item CosmosDirekt
+	   		\item ORBIS
+	   		\item eurodata
+	   		\item energis
+	   		\item CISPA
+	   		\item Greencells
+	   		\item Scheer
+	   		\item Iqony Energies
+	   		\item PLUSCARD
+	   		\item IAS Software
+	   		\item Ludwig Schokolade
+	   		\item MAT Foundries
+	   		\item Adient
+	   		\item Schröder
+	\end{itemize}\end{multicols}
+
 \end{document}

### 2023-07-02 report/report.tex
first paper draft
polished report

@@
 
-We propose to circumvent these challenges by leveraging state-of-the-art language models to transform companies' highly informative public text data into machine-readable data points, and then applying clustering to identify market segments and make location recommendations for novel companies to support business cluster development.
+	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform companies' highly informative public text data into machine-readable data points and then applying clustering to identify market segments and make location recommendations for novel companies to support business cluster development.
 
@@
 Deciding on the location of a business is a vital strategic decision.
-Finding the right location can have several benefits: First, it is crucial to most businesses to be located close to their customers and suppliers for more effective marketing or reduced transportation costs.
+Finding the right location can have several benefits: First, it is crucial for most businesses to be located close to their customers and suppliers for more effective marketing or reduced transportation costs.
 Secondly, being located in an active regional cluster can significantly benefit a business development \cite{clustersandcomp,gems-model, regionaladv, clustertheory}.
@@
 Business clusters are local concentrations of businesses, manufacturers, suppliers, and institutions from the same field.
-Identifying regional clusters is done by combining geographical data of companies' locations with information on their corresponding market segments.
+Identifying business clusters is done by combining geographical data of companies' locations with information on their corresponding market segments.
 This geographic proximity of related businesses enables efficient cooperation and knowledge transfer, which has been shown to significantly increase the productivity of all businesses within the cluster \cite{clustersandcomp,gems-model, regionaladv, clustertheory}.
@@
 This process is very labor-intensive, as businesses do not provide specific data on the latter points, but it must be inferred from their product portfolio and websites.
-Additionally, even simpler data like the number of employees is often unavailable or only available inside hard-to-parse company websites, especially for small regional companies.
+Additionally, even basic data like the number of employees is often unavailable or difficult to extract automatically, especially for small regional companies.
 
@@
 The main contribution of this work is an automatic clustering pipeline to effectively identify market segments and business clusters from publicly available information.
-Utilizing those clusters, our system can provide a strategic location, which we will demonstrate by using the German federal state Saarland as an example.
+Utilizing those clusters, our system can provide a strategic location recommendation, which we will demonstrate by using the German federal state Saarland as an example.
 The novelty of our approach is that we rely on language models to process the companies' information.
 
-Our clustering pipeline can be divided into $4$ distinct steps: $1)$ gathering data from the websites of companies in Saarland, $2)$ computing embeddings of the data, $3)$ reducing the embeddings' dimensionality, and $4)$ applying clustering algorithms.
+Our clustering pipeline can be divided into $4$ distinct steps: $1)$ gathering descriptions from the websites of companies, $2)$ computing embeddings of the text data, $3)$ reducing the embeddings' dimensionality, and $4)$ applying clustering algorithms.
 
@@
 
-$4)$ Lastly, we apply well-established clustering algorithms in the low-dimensional feature space to assign each company to a cluster corresponding to a potential market segment.
+$4)$ Lastly, we apply well-established clustering algorithms in the low-dimensional feature space to assign each company to a cluster from which a potential market segment can be inferred.
 
@@
 \section{Related Work}
-In this section, we will examine previous work on business clusters, and recent advances in natural language processing.
+This section will examine previous work on business clusters and recent advances in natural language processing.
 
@@
 Business clusters and their advantages have been studied in many works.
-For example, \cite{regionaladv} examined the well known technology cluster in the Silicon Valley, famous for being the home of many innovative startups even in recent years.
+For example, \cite{regionaladv} examined the well-known technology cluster in Silicon Valley, famous for being the home of many innovative start-ups.
 
-\cite{clustertheory} provides detailed discussion of the cluster phenomenon.
-It discusses preexisting literature on clusters and reviews the two main postivies effects commonly observed in clusters, positive feedback, and productivity \& growth.
-Additionally, it provides examples for well-known clusters.
+\cite{clustertheory} provides a detailed discussion of the cluster phenomenon.
+It discusses preexisting literature on clusters and reviews the two main positive effects commonly observed in clusters, i.e., positive feedback and productivity \& growth.
+Additionally, it provides examples of well-known clusters.
 
-Our region of choice for testing our approach, Saarland, has also been subject of scientific work.
-It should be noted that most of them examine it for its location on the border of France and Luxembourg or because of its mining and steel producing past.
+The region of choice for testing our approach, Saarland, has also been the subject of scientific work.
+It should be noted that most of them examine it for its location on the border of France and Luxembourg or because of its mining and steel-producing past.
 
-These factors are however of no interest to this work.
-For example, \cite{saarlandeco1} has focused on the agglomeration of automotive industry in Saarland and the neighboring regions, but focuses on the challenges that the country borders pose to this industry.
+These factors are, however, of no interest to this work.
+For example, \cite{saarlandeco1} has focused on the agglomeration of the automotive industry in Saarland and the neighboring regions but focuses on the challenges that the country borders pose to this industry.
 
-The paper \cite{saarlandeco2} specifically compares the economic strategies for development of the regions economy and with a focus on how clusters are developed.
-Most importantly, they identify some regional clusters.
-We will revisit these when evaluating our clustering algorithm and compare on the clusters identified by our approach.
-It should be noted however that the paper was published in 2009, therefore the analysis conducted by this paper was based on the economy at least 14 years before this paper.
+The paper \cite{saarlandeco2} specifically compares the economic strategies for developing the region's economy with a focus on how business clusters are developed.
+Most importantly, they identify some business clusters.
+We will revisit these when evaluating our clustering algorithm and compare them to the clusters identified by our approach.
+It should be noted, however, that the paper was published in 2009, therefore the analysis could be outdated.
 
@@
 
-\textit{$1)$ Collect Descriptions:} The traditional approach for building such a dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in Saarland and then store each in a fixed-size vector.
+\textit{$1)$ Collect Descriptions:} The traditional approach for building an economic dataset would be to gather several attributes, like revenue, number of employers, and products, for many companies in Saarland and then store each in a fixed-size vector.
 However, it is generally unclear which are the best attributes for representing companies.
@@
 To address these challenges to dataset construction, we propose representing companies by the description on their websites instead of numerical attributes.
-The benefit of using this data is that, since companies design their website to attract customers and investors, they include detailed information, such as their products, market positioning, and customer base.
-Using the text directly circumvents the problem of creating a targeted aggregator for specific information.
-This makes our approach simpler to implement and a lot more scalable \& automatable for larger target regions.
+The benefit of using this text data is that, since companies design their website to attract customers and investors, they include detailed information, such as their industry, products, market positioning, and customer base.
+Hence, we circumvent the problem of creating a targeted aggregator for specific information.
+This makes our approach simpler to implement and significantly more scalable \& automatable for larger target regions.
 
@@
 Further, clustering data in high-dimensional space prevents the visualization of clustered data points.
-To avoid the course of dimensionality and to enable user-friendly visualization of our results, we will project the embeddings to 2D or 3D space using two dimensionality reduction techniques.
+To avoid the course of dimensionality and to enable user-friendly visualization of our results, we will project the embeddings to 2D or 3D space using two dimensionality reduction techniques:
 
@@
 The advantage of agglomerative clustering over $K$-Means is that it does not require a pre-specified number of clusters and can compute hierarchically structured clusters.
-Once the clustering algorithm converges, we receive cluster labels for each company in our dataset, corresponding to the predicted market segments.
+Once the clustering algorithm converges, we receive cluster labels for each company in our dataset, allowing us to predict market segments.
 
@@
 Further, users can see the location and clustering assignment of all companies in our dataset on a map.
-When hovering the mouse over a company's data point, additional information about the company is shown, and when double clicking the labels on the legend, only the companies of the corresponding cluster are shown.
+When hovering the mouse over a company's data point, additional information about the company is shown, and when double-clicking the labels on the legend, only the companies of the corresponding cluster are shown.
 
@@
 \subsection{Fostering Business Clusters through Location Recommendations}
-We utilize parts of our clustering pipeline to give location recommendations for companies seeking to establish new sites in Saarland.
+We utilize parts of our clustering pipeline for recommending locations for companies seeking to establish new sites in Saarland.
 Given the description of the novel company, we compute an embedding using a sentence transformer and apply KPCA or t-SNE to get a low-dimensional feature vector.
@@
 Thus, the second approach accounts for the possibility that introducing a novel company might change existing market segments, whereas the first approach does not.
-Given the cluster label of the novel company, the location recommendation is to establish the new company site nearby the most similar company within the cluster, meaning we recommend placing the novel site near the most similar company acting in the same market segment.
-Thus, our location recommendations support the geographical concentration of companies acting in the same market segment, which helps to foster business clusters in Saarland.
+Given the cluster label of the novel company, the location recommendation is to establish the new company site nearby the most similar company within the cluster, meaning we recommend placing the novel site near the most similar company acting in the same market segment, which helps to foster business clusters in Saarland.
 
 Our user-interface offers a dedicated tab for location recommendations.
-In figure \ref{fig:location-recommendation-input} we see the text boxes where users can provide their company's name and description.
-Additionally, users can specify their company's industry, products, customer base, market position, and revenue which can be used to support the location recommendations.
+In figure \ref{fig:location-recommendation-input}, we see the text boxes where users can provide their company's name and description.
+Additionally, users can specify their company's industry, products, customer base, market position, and revenue, which can be used in the location recommendations.
 After clicking "Submit", users are shown the output depicted in figure \ref{fig:location-recommendation-output}.
-The table at the top shows the names and features of the companies in the cluster, to which the user's company was assigned.
+The table at the top shows the names and features of the companies in the cluster to which the user's company was assigned.
 The scatter plot at the bottom left shows the clustered data points, where the point of the user's company is highlighted.
 Lastly, the map at the bottom right displays the location of the novel company's cluster members and the distances between them.
-The user can also overlay a heatmap which show the similarity between his company and all other companies in out dataset.
+The user can also overlay a heatmap that shows the similarity between his company and all other companies in our dataset.
 
@@
 To build our dataset of company descriptions, we manually extracted the descriptions of $50$ of the largest companies in Saarland.
-When a description was only available in German, we translated it to English using the online translator DeepL.
+When a description was only available in German, we translated it to English using the online translator DeepL~\cite{deepl}.
 A list of all companies in our dataset can be found in the appendix \ref{sec:appendix-companies}.
 
-For the purpose of the experimental evaluation we conducted the data collection manually.
-As our target region was very narrow this was easily feasible.
-However, in the future we might create a simple HTML scraper to scale our approach to larger regions.
+For the purpose of the experimental evaluation, we conducted the data collection manually.
+As our target region was very narrow, this was easily feasible.
+However, in the future, we might create a simple HTML scraper to scale our approach to larger regions.
 To test our location recommendation feature, we created company descriptions using GPT-4 \cite{chatgpt}.
 
-Additionally, we evaluate the impact of providing additional features to the clustering pipeline, for which also gathered the features industry, products, customer base, market positioning, and revenue of each company.
+Additionally, we evaluate the impact of providing additional features to the clustering pipeline, for which we also gathered the features industry, products, customer base, market positioning, and revenue of each company.
 
@@
 When using additional features, we compute embeddings for each feature and combine them with the description embedding in the same way the individual sentence embeddings were combined.
-Afterward, the embeddings are projected onto 2D or 3D space using KPCA or t-SNE.
+Afterward, the embeddings are projected into 2D or 3D space using KPCA or t-SNE.
 We chose suitable hyperparameters for KPCA by conducting a grid search over the values $\textit{kernel} = \{\textit{radial basis function}, \textit{sigmoid}, \textit{linear}, \textit{polynomial} \}$ and $\textit{gamma} = \{0.03, 0.032, 0.034, \dots, 0.05\}$, where we found the best values to be $\textit{kernel} = \textit{polynomial}$ and $\textit{gamma} = 0.05$.
@@
 We also used the companies' industry as an additional feature.
- We found that this configuration yields the most sensible predictions of market segments and location recommendations.
-Figure \ref{fig:t-sne-agglomerative} displays the resulting clustered data points.
+We found that this configuration yields the most sensible clusters and location recommendations. Figure \ref{fig:t-sne-agglomerative} displays the resulting clustered data points.
 
@@
 \begin{itemize}
-	\item Coal and mining industries: With the decline of coal mining in recent years, there are no more coal mines in Saarland. As the last one closed in 2012, this cluster does not exist anymore. 
-	\item Metal industry: Covered by cluster 1 (light green) and cluster 6 (yellow).
-	\item Automobile industry: Covered by cluster 0 (red).
-	\item Energy sector: Covered by cluster 5 (light blue).
-	\item Information and communication technology: Covered by cluster 3 (beige).
-	\item Biotechnology and nanotechnology: Covered by cluster 2 (dark blue).
+	\item \textit{Coal and mining industries}: With the decline of coal mining in recent years, there are no more coal mines in Saarland.
+As the last one closed in 2012, this cluster does not exist anymore.
+	\item \textit{Metal industry}: Covered by cluster 1 (light green) and cluster 6 (yellow).
+	\item \textit{Automobile industry}: Covered by cluster 0 (red).
+	\item \textit{Energy sector}: Covered by cluster 5 (light blue).
+	\item \textit{Information and communication technology}: Covered by cluster 3 (beige).
+	\item \textit{Biotechnology and nanotechnology}: Covered by cluster 2 (dark blue).
 \end{itemize}
@@
 However, our approach did lead to more fine-grained separation.
-Additionally, we identified sectors not covered in their work, such as cluster 7 which represents the construction work market segment.
-However, these sectors are usually not contributing significantly to the region's economy, which is most probably why they are not mentioned in \cite{saarlandeco2}.
+Additionally, we identified sectors not covered in their work, such as cluster 7, which represents the construction work market segment.
+However, these sectors usually do not contribute significantly to the region's economy, which is probably why they are not mentioned in \cite{saarlandeco2}.
 In summary, the output of our pipeline matches very well with traditionally identified clusters.
@@
 Thus, placing ABC Auto near VOIT would allow ABC Auto to source parts for its hybrid and electric cars from a company nearby, leading to a more robust supply chain.
-For Bratwurst Bliss, the system recommends settling near the meat producer Kunzler, which could lead to knowledge transfer regarding sausage making.
+For Bratwurst Bliss, the system recommends settling near the meat producer Kunzler, which could lead to knowledge transfer regarding sausage-making.
 Lastly, our system recommends placing PanzerTech's new site close to Diehl Defence, corresponding to the only weapons manufacturer in our dataset.
@@
 \section{Conclusion}
-The goal of this project was to collect data on companies in Saarland and apply clustering algorithms such that the results can be used to identify regional clusters and give location recommendations for novel companies such that business clusters are fostered.
+The goal of this project was to collect data on companies in Saarland and apply clustering algorithms such that the results can be used to identify market segments and give location recommendations for novel companies such that business clusters are fostered.
 
@@
 Lastly, we utilized two approaches to project the embeddings into low-dimensional space where clustering can be applied.
-Further, our methods allowed straightforwardly including other standard company attributes, such as industry, customer base, market positioning, and revenue. 
+Our methods allowed straightforwardly including other standard company attributes, such as industry, customer base, market positioning, and revenue. 
 To make location recommendations, we passed the descriptions and features of novel companies to our clustering pipeline and then recommended establishing new sites next to the most similar companies in our dataset.
 
-A qualitative evaluation of our methods has shown that they can reliably cluster similar companies, which allowed us to infer major industry segments in Saarland.
+A qualitative evaluation of our methods has shown that they can reliably cluster similar companies, which allowed us to infer market segments in Saarland.
 Further, our location recommendation system demonstrated its capability of identifying similar companies, given the description of a new company, independently of the total number of similar companies in the dataset.
@@
 Further, fine-tuning our language models using text data from the business sector might lead to more expressive embeddings.
-To achieve this, efficiently, an automated aggregation system could be developed.
-As we utilize publicly available websites, this would be easily possible without relying on 3rd party services.
+To achieve this efficiently, an automated aggregation system could be developed.
+As we rely on publicly available websites, this would be easily possible without relying on 3rd party services.
 To this end, we have demonstrated the feasibility and potential of applying language models to economic analysis.
@@
 \appendix
-\nm{Upload all \LaTeX{} files to overleaf when its done since they want a link! Update readme in repo!}
-\begin{itemize}
-	\item \textbf{Link to Code}: Provide the link to your code repository.
-You can use any service to host your code (Github, gdrive etc.).
-The code should be running, accessible and all of your work must be reproducible.
-In case your code is not accessible or not in a working state, relevant number of points will be deducted.
-	\item \textbf{Link to Overleaf}: Add a link to the Overleaf project which contains all of the LaTex related files for this report.
-	\item \textbf{Additional Figures}: Add any and all additional figures produced during you work with relevant explanations in the appendix.
-\end{itemize}
-
-\subsection{Additional Clustering Results}
-
+\nm{Upload all \LaTeX{} files to overleaf when its done since they want a link!}
 \subsection{Link to Code}

### 2023-07-02 paper/paper.tex
adjustments to paper & report

@@
 
-\include{./wits_template.zex}
+\include{./wits_template.tex}
 
@@
 
-\author{Nicola J. Müller, Robert Leist, Paul Eichler, \\and Tobias Recktenwald}
-\title{Towards Language Model-based Identification of Market Segments and Fostering of Business Clusters}
+\author{\small \href{mailto:s8namuel@stud.uni-saarland.de}{Nicola J.
+Müller}, \href{s8roleis@stud.uni-saarland.de}{Robert Leist}, \href{mailto:s8pleich@uni-saarland.de}{Paul Eichler}, and \href{mailto:s8tsreck@stud.uni-saarland.de}{Tobias Recktenwald}}
+\title{\vspace{-3cm}Towards Language Model-based Identification of Business Clusters}
+\date{}
 
 \begin{document}
+
     \maketitle
+
    \begin{abstract}
-   	Identifying market segments is crucial for effective marketing strategies and well-informed business decisions.
-Further, combining companies' geographical locations with their market segments allows for detecting business clusters.
-However, acquiring and processing the data needed to gain such insights into regional economies is labor-intensive.
 
-   	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform companies' highly informative public text data into low-dimensional vectors and then applying clustering to identify market segments and make location recommendations for novel companies to support business cluster development.
-
-   	A qualitative evaluation of our methods being applied to data from the German municipality Saarland demonstrates that our methods can accurately cluster similar companies and assign novel companies to existing clusters.
+	\textit{\small
+	One of the most important decisions every business has to decide on a physical location.
+Identifying the right location is crucial for effective marketing strategies reaching the intended customer base, it can reduce transportation costs, and locating in a vibrant regional business clusters can have significant positive effects on business development.
+	However, strategically acquiring \& analyzing data on regional economies, the corresponding companies along with their target market segments is very complex and labor-intensive.}
+	\textit{\small
+	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform publicly available company websites, into machine-readable data points and  applying clustering to make location recommendations.
+We demonstrate accuracy of identified clusters by applying our method to data from the German municipality Saarland.
+	}
    \end{abstract}
@@
 Thus, establishing or further developing business clusters is of high interest to companies and local governments.
-Therefore, significant effort is spent identifying clusters and market segments in regional economies.
+Therefore, significant effort is spent identifying clusters in regional economies.
 
-   However, identifying market segments and business clusters requires a significant amount of manual labor.
+   However, them requires a significant amount of manual labor.
 Typically, one must first collect information about companies in the targeted region.
@@
 Additionally, it provides examples of well-known clusters.
-
    The region of choice for testing our approach, Saarland, has also been the subject of scientific work.
@@
 We will revisit these when evaluating our clustering algorithm and compare the clusters and market segments identified by our approach.
-It should be noted, however, that the paper was published in 2009, meaning their analysis could be outdated to some extent.
+It should be noted, however, that the paper was published in 2009, meaning their analysis is outdated to some extent.
 
@@
 Further, our location recommendation system demonstrated its capability of identifying similar companies, given the description of a new company.
-
 To allow end-users to leverage our methods, we implemented a user-friendly interface with many functionalities, such as visualizing the clustered data points, showing the location of companies, and giving detailed and interpretable location recommendations.
@@
 As we rely on public websites, such a system could be easily implemented without relying on 3rd party services.
-
-   To this end, we have demonstrated the feasibility and potential of applying language models to economic analysis.
 

### 2023-07-02 report/report.tex
adjustments to paper & report

@@
 
-\title{Towards Language Model-based Identification of Market Segments and Fostering of Business Clusters}
+\title{Towards Language Model-based Identification of Business Clusters}
 
@@
 \begin{abstract}
-	Identifying market segments is crucial for effective marketing strategies and well-informed business decisions.
-Further, combining companies' geographical locations with their market segments allows for detecting business clusters.
-However, acquiring and processing the data needed to gain such insights into regional economies is labor-intensive.
+	One of the most important decisions every business has to decide on a physical location.
+Identifying the right location is crucial for effective marketing strategies reaching the intended customer base, it can reduce transportation costs, and locating in a vibrant regional business clusters can have significant positive effects on business development.
+	However, strategically acquiring \& analyzing data on regional economies, the corresponding companies along with their target market segments is very complex and labor-intensive.
 
-	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform companies' highly informative public text data into machine-readable data points and then applying clustering to identify market segments and make location recommendations for novel companies to support business cluster development.
+	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform publicly available company websites, into machine-readable data points and  applying clustering to make location recommendations for novel.
 
-	A qualitative evaluation of our methods being applied to data from the German municipality Saarland demonstrates that our methods can accurately cluster similar companies and assign novel companies to clusters.
+	A qualitative evaluation of our methods being applied to data from the German municipality Saarland demonstrates that our methods can accurately cluster related companies and categorize novel companies to a cluster.
 \end{abstract}

### 2023-07-03 report/report.tex
grammarly is your friend

@@
 \begin{abstract}
-	One of the most important decisions every business has to decide on a physical location.
-Identifying the right location is crucial for effective marketing strategies reaching the intended customer base, it can reduce transportation costs, and locating in a vibrant regional business clusters can have significant positive effects on business development.
-	However, strategically acquiring \& analyzing data on regional economies, the corresponding companies along with their target market segments is very complex and labor-intensive.
+	One of the most important decisions every business has to decide on is a physical location.
+Identifying the right location is crucial for effective marketing strategies to reach the intended customer base.
+It can also reduce transportation costs, and locating in a vibrant regional business cluster can significantly positively affect business development.
+	However, strategically acquiring \& analyzing data on regional economies, the affiliated companies, and their target market segments is very complex and labor-intensive.
 
-	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform publicly available company websites, into machine-readable data points and  applying clustering to make location recommendations for novel.
+	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform publicly available company websites into machine-readable data points and applying clustering to make location recommendations for novel companies.
 
-	A qualitative evaluation of our methods being applied to data from the German municipality Saarland demonstrates that our methods can accurately cluster related companies and categorize novel companies to a cluster.
+	A qualitative evaluation of our methods being applied to data from the German municipality Saarland demonstrates that our methods can accurately cluster related companies and categorize novel companies into existing clusters.
 \end{abstract}
@@
 
-$4)$ Lastly, we apply well-established clustering algorithms in the low-dimensional feature space to assign each company to a cluster from which a potential market segment can be inferred.
+$4)$ Lastly, we apply well-established clustering algorithms in the low-dimensional feature space to assign each company to a cluster from which a potential market segments can be inferred.
 

### 2023-07-03 scripts/excel_to_csv.py
refactor: home page as md file, fix paper page

@@ -7,7 +7,3 @@ def xlsx_to_csv(input_file_path, output_file_path):
 
     # Save it as csv file
     xl.to_csv(output_file_path, index=False, encoding='utf-8')
-
-
-# usage
-# xlsx_to_csv('../Book1.xlsx', '../data/economic_data.csv')

### 2023-07-05 paper/paper.tex
fixed link to code in paper
refactor: paper to more detailed template

@@
 \begin{document}
+	\pagestyle{fancy}
 
-    \maketitle
+	\fancyfoot{} % clear all footer fields
+	\fancyfoot[l]{\fontsize{9}{9} \textit{Workshop on Information Technology and Systems, Hyderabad, India 2023}}
+	\fancyfoot[r]{\thepage}
+
+	\renewcommand{\headrulewidth}{0pt}
+	\fancyhead{} % clear all headers
+	\fancyhead[r]{\fontsize{9}{9} \textit{WITS 2023 - Towards Language Model-based Identification of Business Clusters}}
+
+	%custom title
+    \begin{center}
+		{\fontsize{20}{20} \textbf{Towards Language Model-based Identification of Business Clusters}}\\
+		\vspace*{0.2cm}
+		\textit{Submission Type: Research in Progress}
+	\end{center}
 
@@
 
-   \section{Introduction}
+   \section*{Introduction}
    Deciding on the location of a business is a vital strategic decision: First, most businesses must be located close to their customers and suppliers for more effective marketing or reduced transportation costs.
@@
 
-   \section{Related Work}
+   \section*{Related Work}
    This section will examine previous work on business clusters and recent advances in natural language processing.
@@
 
-   \section{Procedure}
+   \section*{Procedure}
    \input{figure}
@@
 
-   \textit{$4)$ Clustering:} We cluster the data using agglomerative clustering, which initially assigns each data point to a separate cluster and then iteratively merges close clusters until all data points are in the same cluster.
+   \textit{$4)$ Clustering:} We cluster the data using agglomerative clustering, which initially assigns each data point to a separate cluster, then iteratively merges close clusters until all are in the same cluster.
 The intermediate clustering that achieves the largest separation between data points is chosen as the final clustering.
-   Once the algorithm converges, we receive cluster labels for each company in our dataset, allowing us to infer market segments.
+Once the algorithm converges, we receive cluster labels for each company in our dataset.
 
-   Although our general pipeline represents companies using their descriptions, we emphasize that our approach can also utilize additional features.
+   Although our general pipeline represents companies using their descriptions, we emphasize that it can also utilize additional features.
 For instance, we can include the companies' products in the encoding by computing the corresponding sentence embeddings and merging them with the description embedding using max pooling.
@@
 
-   %\subsection{Fostering Business Clusters through Location Recommendations}
+   \subsection*{Fostering Business Clusters through Location Recommendations}
    To give location recommendations for companies seeking to establish new sites in the region of interest, we utilize parts of our clustering pipeline.
@@
    Given the novel company's cluster label, the location recommendation is to establish a new site nearby the most similar company within the cluster.
-Thus, our location recommendations support the geographical concentration of companies acting in the same market segment, which helps to foster business clusters.
+Thus, our location recommendations support the geographical concentration of companies acting in the same cluster, encouraging their growth.
 
@@
 
-   \section{Results}
+   \section*{Results}
    To build a dataset of company descriptions, we extracted the descriptions of $50$ of the largest companies in Saarland, which are listed in the appendix \ref{sec:appendix-companies}.
-   For the experimental evaluation, we conducted the data collection manually.
-However, in the future, we aim to create an HTML scraper to scale our approach to larger regions.
+   For the experimental evaluation, the data was collected manually.
+However, in the future, we aim to create an automated scraper to tackle larger regions.
 To test our location recommendation feature, we created company descriptions using GPT-4 \cite{chatgpt}.
@@
    To evaluate  the clustering of our pipeline, we will compare the found clusters to those identified in \cite{saarlandeco2} (Table 4, p. 1226):
-   \textit{Coal and mining industries}: With the decline of coal mining in recent years, there are no more coal mines in Saarland. Accordingly, no such companies are present in our dataset.    
+   \textit{Coal and mining industries}: With the decline of coal mining in recent years, there are no more coal mines in Saarland, therefore no companies are present in our dataset.    
    \textit{Metal industry}: Covered by cluster 1 (light green) and cluster 6 (yellow), which contain steel producers like SaarStahl and Dillinger and companies offering steel products like Hörmann, a producer of various types of doors.
@@
 However, our approach did lead to more fine-grained separation.
-Additionally, we identified sectors not covered in their work, such as cluster 7 (orange), which represents the construction work market segment, and cluster 10 (pink), which represents the food production market segment.
+Additionally, we identified sectors not covered in their work, such as cluster 7 (orange), which represents the construction work market segment, and cluster 10 (pink), which represents the food production market segment, both not as influential in the regions economy.
 
@@
    \textit{PanzerTech}: A weapons manufacturer with a wide spectrum of products, from armored vehicles to cybersecurity solutions.       
-   For FluxAI, our system recommends placing the new site close to CISPA, which is sensible since CISPA is a world leader in information security research, including artificial intelligence, and thus knowledge transfer between both companies could be highly beneficial.
+   For FluxAI, our system recommends placing the new site close to CISPA, which is sensible since CISPA is a leader in information security research, including artificial intelligence, and thus knowledge transfer between both companies could be highly beneficial.
    For ABC Auto, the location recommendation is to establish a new site close to VOIT, which specializes in manufacturing car components with a focus on hybrid and electric cars.
@@
 
-   \section{Conclusion}
+   \section*{Conclusion}
    In this work, we demonstrated how language models and clustering algorithms could be combined to identify market segments and give location recommendations for novel companies such that business clusters are fostered.
@@
    We represented companies by their public descriptions, which allowed us to leverage state-of-the-art language models to transform the highly informative text data into embeddings.
-Further, our methods enabled straightforwardly including other company attributes.
-Given the embeddings, we applied a clustering algorithm to infer potential market segments.
-   To make location recommendations, we passed the descriptions and features of novel companies to our clustering pipeline and recommended establishing new sites next to the most similar companies in our dataset.
+Given the embeddings, we applied a clustering algorithm to infer related companies, which enables us to make location recommendation.
+A qualitative evaluation of our methods has shown that they can reliably cluster similar companies, which allowed us to infer clusters in Saarland.
+Further, our location recommendation system demonstrated its capability of identifying similar companies, given the description of a new company.
+To allow end-users to leverage our methods, we implemented a user-friendly interface with many functionalities, such as visualizing the identified clusters and location recommendations.
 
-   A qualitative evaluation of our methods has shown that they can reliably cluster similar companies, which allowed us to infer market segments in Saarland.
-Further, our location recommendation system demonstrated its capability of identifying similar companies, given the description of a new company.
-To allow end-users to leverage our methods, we implemented a user-friendly interface with many functionalities, such as visualizing the clustered data points, showing the location of companies, and giving detailed and interpretable location recommendations.
+   A promising opportunity for future work would be fine-tuning our language models using text data from particular business sectors.
+To achieve this efficiently, an automated aggregation system could be developed, along with optimizations to the clustering pipeline.
 
-   A promising opportunity for future work would be fine-tuning our language models using text data from the business sector since it might lead to more expressive embeddings.
-To achieve this efficiently, an automated aggregation system could be developed.
-As we rely on public websites, such a system could be easily implemented without relying on 3rd party services.
-
-    \bibliographystyle{IEEEtran}
+    \bibliographystyle{misq}
 	\bibliography{bibliography}
@@
 	\subsection{Link to Code}
-	\url{https://github.com/NicolaMueller42/data_science_project}
+	\url{https://github.com/nicola-mueller/LM-based_Company_Clustering}
 
